\textit{Lugano. Tuesday evening towards 7 o'clock}

The spa, the comfort — Eva feels good and we both love Lugano. I asked the landlord whether we could have a flat for a few days. There is still no seasonal traffic at all, so it was 30 francs per 4 days for us both. I accepted and wrote to the agency in Genoa, they are to telegraph when the \WTF{"Messina"} departs. So, for a few days we are \WTF{train-free} and content.

In the morning, as we got up at 7:30, I arose with the first ray of sunshine over the mountain ridge,mof Mount Generoso I believe. But the mountains are in the fog, and the fog hasn't lifted the whole day. You can even see gold and silver in the clear water, the hotel on Mount Bré and the settlements spread out across its lower part. It was sunny, it was the faintest pre-Spring feeling, otherwise cold and cool. \missing

After breakfast (what did we hear at the next table, when the \WTF{trolley} to the station constantly went by. "\WTF{Eegal} away goes the track!" - What did we hear at another table, when an excursion to Locarno is advertised with a tour of the Sala Stresemann? "We are not for S-Tressmann!" Dresdeners and Deutschnationals support Germany nell'Estero, jic et ubique) — so we went to the station and went under with the Funicolars in the place. On the Treppenstrasse E could go forwards, not backwards. Below, tne beautiful Italianità. Everything was still clear to us. Eva even claimed that the same green trunk as on June 26th was pit up. Narrow streets with heavy stone houses, with passages, summer houses, colorful decorations, colorful clothes. Cheese and wine and sausage stores. \missing
After eating Eva slept and read "The Tunnel", which quite captivated me. Then we went down to the Kursaal cafe in the morning. A large rectangular room, which might hold up to 150people, was almost totally full. But one only hears Swiss German and Italian. \a