Sunday evening.

Thursday we were together with Gusti at Dember's; we are now with the Dembers at Gusti W's. — Yesterday we had the Hirches over. The husband has set himself up here as an "economic adviser". We talked extensively with him, gave him specific goals for earning money. He says that it's not impossible. That is now almost our last hope. Eva has a;ready done the calculations: the house is a question of life and death for us. If the construction isn't finished by next Winter, we're both done for. 

I don't like thinking how boundlessly sad our lifehas been the past year. —

Work: on March 31st the Corneille was ready. End of April, the anthology (which arrived \textit{today}). Then a series of recensions, above all however endless corrections.  Almost all of July and August devoted to the \WTF{Erziehungsreferat}, then studies on the Image of France. October, November three articles on Spain coming out of \WTF{Vossler's Lope}; since then, very tiring, the Image of France. —

Early in the year Felix died, the drive to his funeral my only trip. Lately, much awkwardness around the family via Grete's presence. 

Today, a greeting card from Georg out of Skt Moritz: Discite moniti! Live healthy! Less smoking, get outside more, no worries! Lovely advice.

Our \WTF{little birch tree has died}. Symbolic?

The cats have won such a place in Eva's, and hence my, life, that I must probably also mention them here. No 2, Domenico, came to us in July.

In place of the former visits to the cinema, we now have the colorful (\WTF{notizenlose}) readings. The lending library plays a big role. Before its discovery I had purchased a lot too. We have also filled our holes in modern German lit, after we initially stuck entire;y to American and English. For Christmas, Annemarie sent us "Die Geschwester von Neapel" (Werfel). Started with delight.