\textit{Sunday evening after nine o'clock}

24 hours among people, which we were unaccustomed to. Yesterday evening: Thiemes, Kuwhns, Blumenfelds, Annemarie our guests. Exhausted, nevertheless it was nice, to bed after 1 o'clock. Got up quite smashed at 9 o'clock. Before we could sit down for breakfast, the \textit{Hirsches} appeared. Offering thanks that I spoke with Lerch before the boy's psychological exam. Hans told about this exam in detail, which had lasted all of Thursday and Friday, and was exceptionally hard, thorough and multifaceted. \WTF{Cognitive exams}, technical, \WTF{dexterity}, tests of memory and reflexes. Also observed at lunch; also an hour of instruction for people from the barracks, also written discussion and assessment of a criminal case...I added to what Thieme recounted yesterday: instruction from the Reichswehr to the SW to build a machine for 100,000M. For what purpose, is not said. Only the most particular specialists know. For testing heavy tanks in a \textit{closed} space.  These tanks are banned by the Versailles treaty, there were pictures of our maneuvers in all the newspapers this Summer: operations against cardboard \WTF{Tank-Atrappen}! Which is correct, Th said, one cannot build in \textit{one} place, but rather individual pieces at different places. 
Third, I added to commemt recently made by Greta: Reichswehr, Military, all of that seems so medieval, so totally antiquated. Who could earnestly still think of war!

As the Hirches left at 1 o'clock, we were shivering from cold and \WTF{sobriety} and made ourselves breakfast, or rather brunch. Soon thereafter, the \textit{young Koehlers} appeared, as arranged. They donated the first tree for our poor plot. A birch, more branch than trunk, about a meter high, but with strong roots and lovely \WTF{little branches on the sides}. We left in the car, I took the Dembers, who came with \WTF{Emita} and fertilizer and two spades. The little tree was solemnly planted in a half-way protected corner —- today at 3:30 in the afternoon of November 13th the first tree my ground and soil — everyone did a few sticks, it was consecrated, then we went to the Dembers' for a while, had Schnaps and cookies, everything was very nice. But the sight of the empty places still 	depressed me badly. God knows whether I will experience the new house up there. The sight of Dresden through the light autumn fog was again glorious. Then again in the car, drank coffee with us, at 7 the Koehlers left, and we got ourselves supper at the station.

\missing

I have read Der jüdischen Krieg to its end. Very exciting. Three elements: a) sattre of the present, b) history of the present interpreted psychologically, c) \WTF{Chronik}. Many places reminiscent of Homer. I now want to read the Olewagensaga by Herm Grimm, which Annemarie had given me for my birthday. \missing

We put off our visit for a moment and five minutes before 6 and before the close we voted for the town councillor. The first time in our life that we participated in a city election. Here, where these votes are certainly useless, we both voted Democratic. Recently in the Reichstag election Eva \?{switched to the Centrum}{schwenkte zum Centrum ab}. I had once compared the Democrats to \WTF{Möpsen - pugs?} in a lecture. An animal completely out of fashion, from which however one may obtain some specimens suitable for breeding purposes. This time I waxed, "I will give my pug one more try./But if it still doesn't help, then he will have to die!" It again did not help at all.
(meinem Mops/geht er hops - chance, turn, spin, try, opportunity, go, time, shot, crack, stab)
\missing