m ',Sunday morning.

The "sad month of November". Cold, damp, eternal darkness, struggle with the heater. \missing On Busstag, Nov 16, we were together in the very bad French war-film \textit{Croix de Bois}. Nothing of the significance of the Dorgelès book; without inner development, \?{clunky}{abgeklapperte} war- and horror-scenes, one gets bored with all the cannonfire and gruesome death. Only good at the start, when the \WTF{trench crew hears the mines under the ground} and count the hours until their relief; how then the procession of the explosions are seen behind them.

As we got home, E was already feeling very bad. The next day I had to have \textit{Dr Weymarn}; a case of the flu, fever. It was not very bad and didn't last very long — already on Sunday she was up for a bit; now she only still lays down in the evenings, and this evening  we are going to risk having guests here: 4 Koehlers, 3 Hirches, M Wiechmann, and Annemarie — but it was hell. Or at least limbo. I had the lion's share of the apartment with the heater and cats (\WTF{Frau Lehmann however came alot but not enough}), \WTF{I brought it bad} and E's overwhelming despair and orders and going out of her mind was dreadful. Now again as for days already she has completely taken over the morning routine. (Other than dusting, my department). But it is too much for her, and she is ever more embittered about the \WTF{Wohnungsfeste}. But I cannot change it, I can't. She doesn't want a servant girl, \WTF{since then she wouldn't be able to move enough}; she is firmly convinced that she won't be able to provide anything outside of physical housekeeping. (No lectures, no music, nothing). I can't dissuade her from it.
Also, money for the house construction needs to be saved. And I am still convinced internally that we will never get the house. The financial situation is always worse, no one will lend to me — and \?{why should they?}{worauf auch sollte er?} So it is all very bitter.

For a week I had to leave aside all work, I was hardly able to put my lectures together. Now I have finally started easing into it again — but the 3rd Spanish essay still hasn't been taken back up. God knows when we will get past this rough patch.

On top of the many woes, there is the pin-prick of the Heuber trial. Up to now I have had around 60M in costs, they will increase, and I no longer believe in victory. If I totally followed my feeling, I would have settled with the requested 250M and would have blown off the missing 350. I suppressed it however from duty.

Grete \?{in the small lecture}{im dünnen Colleg}, Grete gossiping between Gusti W and me, Grete as \WTF{family compass}, pointing to Berlin and pointing to death and pointing to the past, Grete getting on my nerves in each and every way, nevertheless she had been living over there for three weeks already.

Little luck with reading aloud. After the extraordinary (if also \WTF{mannered}) Olewagensaga by Grimm, the disagreeable disgustingly petty "Jagd auf Liebe" by H Grimm. We did not get through the boring smutty book (Huysmann's influence and his own filth) — in such a case I would be for censorship — or at least as regards cheaper popular editions (a 2.85M volume!) — \missing.
