Wednesday morning.

The "holiday week" was made more difficult by the excessive swelteringly humid heat. \missing On Monday (whole day, from 6 o'clock in the morning preparing lectures, then lectures). In the evening up with Dember. With Grete, the Blumenfelds, Gusti W, Emita D. Away at 12; it was nice that after eating we could sit in the garden. We also went over "our" terrain. 
\missing On Tuesday a big group at our place. Wieghardts, Dembers, Annemarie, Ruedigerin, Thiemes, Martha Wiechmann.
There were 13 of us. Everything went nice and well, and we were totally dead by the end of the day.
On the 13th I gave Blauert the task of having the terrain actually measured for us etc, although the Thuringia is in the concourse and we probably won't see the 4000 marks paid upfront again.
A more complete and essential bit of madness I am being choked out financially, I am bound for an indeterminate time to unforeseeables, etc  etc. But it is E's desperate wish. And further deliberation: I don't even believe that the fulfillment of Eva's wish will make her any more satisfied. And further: when will her wish be fulfilled. We bought the land today, i.e. I made a 1500M down payment, paid the fees and taxes — y es todo. And Eva speaks of building, a greenhouse, and this and that. And I hardly see myself being capable of putting up the cost of this first step. Getting the capital for building is totally out of the question.  I let myself drift in everything.

Last week was a preliminary discussion with the notary Langenhan. Today we had been in the car with the Blauerts in HD to the local office, then to the plot where the geometer was just active. Everywhere there are new uncertainties, new costs, new difficulties. I understand literally nothing about any of it. I blindly said yes to all of it. I will pay what can be squeezed out of me. In the worst case there is a poimt where I can just no longer pay. In the very worst case one dies or \WTF{helps the dying}. 
A bit awkwardly, a bit ridiculously, I go about this senseless undertaking. But E's condition forces me. It was a sleepless night for her, and so also for me. \textit{That} does not happen often. But the daybreak with despair with hardly-(or not at all)suppressed tears is the usual for E. And always, under everything, trembling reproaches against me, unspoken, and yet horribly clear: we would have been able to get the house long ago if only I hadn't resisted and let the right time pass.

\missing