Yesterday: \WTF{morgens Buch. Uschla.} Cleared up the Schumann and Konopath matter. Blech. The Uschlas sit on their chairs as if we were at peace. Amann: the best and most loyal of all. 60000 Mk net profit from Angriff. Bravo! The Gau gets the lion's share. With that, I cna get out from under the debt. Great! On the 1st of February a new newspaper "N.S. Funk". Was greatly hyped by the Reich propaganda leadership. Completely under my influence. Negotiations from January 1st in Berlin. I got a contract with Amann. Lay out the guidelines and write to a leader weekly. That also fills Magda's coffers. ...Sold a book, "the awakening of Berlin", for 80000 Mk. Will be totally huge. Then I will be out of debt. Great plans become perfect in no time at all. With...can work...everywhere...\missing...Strasser...I get...and popular education. That also belongs in my...Additionally, B shall appear in Berlin entirely according to my instructions. I will seriously unwind there. Discussed fight over Lippe. That must become a prestige-result. Goering was with \WTF{Alten}. The news papers have swindled. Still nothing at all decided. Schleicher wanted to deceive us yet again. In the morning new negotiations with the Alten. At....thought. Fired a third of the personnel. Radio and...cleared up. Engaged Haegert as my chief of staff. Everything perfect. Franke has damaged me very much. Hitler tidies up. Discussions with Ley and \WTF{Funk}. \WTF{Ausmisten!} No...more...fights! Reichsadler. Prepared battle over Lippe. Training with...talked over... He...too much. Finally! A day's work! Seize the power! Talked with Franke. Now he too becomes tearful. \WTF{Das fehlt noch.} I agree with his opinion. Had one yet another chance. Hotel. Everything closed. Thank god! Read. Worked. Departed. Woke up. We just entered Berlin. New work awaits.


 . Franke hat mir sehr geschadet . Hitler räumt auf. Unterredung mit Ley und Funk. Ausmisten! Keine . . . mehr. . . . kämpfen ! Reichsadler. Kampf um Lippe vorbe­ reitet. Schulung mit . . . durchberaten. Er . . . zuviel. Endlich ! Tages­ arbeit! Macht ergreifen! Gespräch mit Franke. Jetzt wird er auch noch weinerlich. Das fehlte noch. Ich geige ihm die Meinung. Hat