Hitler held a three-hour talk with Oberstleutnant Ott: Schleicher will not accept. Show him all of dangers. Reichswehr will be used for that. He is deeply impressed. Hitler gives us a report. But these officers are really political children. Ott telephones with Berlin. Schleicher can no longer turn back. Asks for acquiescence. \WTF{Knif[!]}. In the meantime, we had to go to assemblies. I speak in Arnstadt and Blankenburg. Both overflowing. Mood very good. Back to Weimar. Everyone waiting for me. Still at coffee[!]. Minister Mueller out of Koenigsberg: the East-Prussian Reichswehr will not let itself be driven into chaos. Will defend the borders. Asks for solidarity with the SA. That would be something. But Kube is not the man to handle such a matter. A commissar must be sent there. Late to bed. Slept well.
Friday: late here. Hanke comes from Munich. Had put in much preparatory work. Franke has ruined the whole division. I could slap him. A green boy. Must go! Hanke has handled his affair well. I must now concern myself somewhat more with Munich. Most important: Personal questions. Schleicher is named chancellor. OK then. That is then the last \?{Ausweichmöglichkeit}{option} for the old guard. We will \WTF{gleuch loszetern}, and from the rest, wring out what we can. Goering back to Berlin. He treats with Schleicher. With Hitler for coffee. He is a Mensch here in Weimar. We likes Magda and me very much. Then he travels to an assembly. I am free today. I wait on him and work in the meantime. The sweet Magda sleeps.