Sunday: Work at home. Brandenburg \WTF{Gautag}. Overflowing. The long line made a bad impression. \WTF{Strassermann}. I spoke very well. Sharply against splitters. Big applause. To circle X. Neukoelln to Treptow. Everywhere fantastic mood. Festive atmosphere. Our Berlin stands. I again spoke well. Strasser has lost. At home spoke with Konrad. Things are going very badly with him. I must do something for him.  I gave a notice in the Angriff, in which I again made amends for the tactless remarks of the editors against Strasser. To Munich. With Hanke with Strasser (crossed out). Roehm also there, and Frank. Read a long time. Ruckus in Leipzig. Hitler! He comes from the speaking tour. Very lucky that I am there. I like very much that. Talked about his speeches in Breslau, Dresden, Chemnitz, Leipzig. Smash hit everywhere. Sharp remarks against Strasser, who had already lost the party. Little sleep. Munich. Coffee at the Braune's house. Everything about Hitler. Joy that the Strasser case was so quickly liquidated. That it already was. Imperial eagle. Smoked out the division. Fired a third. \?{Cleared out the upper echelons}{‹berorganisation abgestoﬂen}. Franke is totally astonished. Now the division is again ready for work. Today Strasser's \?{previous possessions -- spoils?}{Konkursmasse} will be distributed. With Hitler and Auwi. Midday. Later coffee. All questions talked through. Evening I am alone with Hitler. The Prussian question. The old will only give us Prussia when we enter into the Reich cabinet. Schleicher's idea. And not Goering as Min.Pres., but rather Strasser. There is the rub. Goering and Kerrl were with Hindenburg. But with little success. Hitler tells of his great youthful love. Touching how he honors the lady. Later Hoffmann's and the H...Hoffmann makes his "p...photopischen experiment". Laughed our heads off. Everyone joined in. Home late. Slept well today. Negotiations the whole day.

