I cannot shake the impression that General Schleicher is only using the negotiations to eventually shut us out. They demand of the fuehrer that \?{before his promotion}{vor seiner Betrauung} he sound out the trustworthiness of the parties, always with the ulterior motive that the Deutschnationals be shut out and thereby make a majority coalition impossible. The fuehrer conferred with us at great length and then came to the decision that further negotiations not be verbal, but rather carried out win writing, so that a new August 13 situation can be avoided at all costs.
Rumor upon rumor circulates. Most are untrue \?{and so they only lie in the air}{ und liegen nur so in der Luft}. \?{All under-bosses hold to the straight and narrow, only Strasser makes his obligatory detours}{nur Strasser macht seine obligatori­ schen Seitensprünge}. In the afternoon, I carried out the swearing-in of the magistrate for East Berlin. Among the people, too, there are unfortunately again all-to-grand illusions. Shall these again be deceived by failure? \WTF{Im Kaiserhof wird weiter beraten}. 
From here on out the fuehrer is playing a game of chess for power. It is a \?{high-stakes}{aufregender} and nerve-wracking struggle, but it also conveys the tingling feeling of a party \?{in which everything is at stake}{bei der es um alles geht}. We must be uncannily vigilant, so that we don't appear weak. Goering accepts delegations from the parties. The Zentrum claim to be in agreement with the fuehrer's chancellorship. The Deutschnatiomals have not responded to our invitation for a meeting. They are always on a high horse. The fuehrer has put to paper an extensive answer to the task of forming a majority coalition. It is gloriously stylized and stated with uncontradictable arguments. In it, the parliamentary solution is rejected as not in line with the situation. The requirement of the \?{presidential character}{Präsidialcharakters} of the coming cabinet is maintained.

Die parlamentarische Lösung wird darin abgelehnt als nicht der Situation entsprechend. Die Forderung des Präsidialcharakters des kommenden Kabinetts wird aufrechterhalten .