Yesterday: the press is swimming in rumors. But the crisis is already over its high point. Strasser stands completely alone. That pleases me. Der Angriff has caused me great shame through its brash commentary. I named Kampmann editor-in-chief. Not an ideal solution, but in any case better than Lippert. Finances with Brinkmann and Fellmer. Which is hopeless. We must introduce very rigorous cost-cutting measures. Discussed the situation with Harpe and Goerlitzer. Mood not good and not bad. Everyone expects that some will happen. Strasser's move has provoked great unrest. To the leaders: I discuss the Strasser case and the situation. \?{Naturally, the gau stays}{Der Gau steht natürlich}. All yet again promise me loyalty to Hitler. Berlin remains firm. Discussion with Schim. Back home. Konrad is there. Hopeless situation with him. I must and will help him. To Goering in the palace. Big group. Balbo, the Italian. Minister of air transport there. A colorful chap. Exudes a lust for life. Banquette. Goering and Balbo have a very friendly talk. Much warmness everywhere [!]. Music, singing, discussions. I speak at length with Ex Cerruti, the Italian ambassador. Clarified the movement for him. He doubts whether we will get the commune at all, let alone become the rulers. The Strasser conflict will \?{generally be written in my account}{allgemein auf mein Konto geschrieben}. Rubbish with sauce! Leni Riefenstahl is also there. And Frau Sonnemann. Extraordinarily sympathetic. Magda and L Riefenstahl flirt with Balbo. He is a filou. But very pleasant. Makes many compliments to us. The whole evening with us. He is very simpatico with me. An artist with the ladies. On top of that a brave and complete man. It went on until 5:00 in the morning. Kube and Kerrl \WTF{honored/devestated}{verheerend}. Beautiful women there. I am totally...And Magda is generally venerated and admired. Slept well. \missing

