 \header{November 4th 1932 (Kaiserhof)}

We have put out our position on the strike once more on large posters. Up there they have \WTF{been fantastically successful}{einen tollen Schiedsspruch gefunden}; \?{consequently}{demzufolge} anyone who does not appear for work is to be fired without notice. Of course, no one comes. In Wedding and Neukolln it has come to terrible street-fighting. The tram is totally shut down. Berlin is the image of a dead city. Of course our people have taken over the leadership of the strike in all parts of the city. That is also good. \WTF{If they're ready, then ready}{Wenn schon, denn schon}! Every hour new, bloody acts of terror occur. There are already four officially dead. A revolutionary mood reigns in Berlin. Our party apparatus is functioning wonderfully. We have started an \?{aid program}{Hilfsaktion} by which we have succeeded in saving the strikers from the worst social damage. With us everything proceeds in the most orderly fashion. Our appeal to the workering class has, in a very few days, splendidly improved. Even if it does not have an effect for this election, this asset has an immeasurable significance for the future. Here one must learn to reckon in longer time-scales; since we will indeed finally conquer Berlin, and since it does not matter whether a more or less meaningless election is lost by a few ten thousand votes, which in the active, revolutiobary struggle has no significance anyway. The streets are full of masses of people. How the gray walls squeeze them into long lines. An undescribable nervousness reigns everywhere. The most insane rumours are circulated. The bourgeois press have invented the lie that I have instigates this strike without the knowledge and will of the fuehrer, in order to lead the party into the bolshevik lane, and so I am in hourly contact with the fuehrer on the telephone. He approves of every facet of my standpoint. If we had not acted as we did, then we would no longer be socialists nor a workers' party. Our press stands bravely and persistently at our side in this action. It is our only weapon aside from our speaking and propagandistic elan. Once again I spoke \WTF{tensely}{in einer Höchstanspannung} in a series of working-class neighborhoods, Wittenau, Schönholz, and Pankow, there alone three times before overflowing halls. It is not difficult to make our view on the strike question clear to the masses, if one sees them face-to-face. I have put out the slogan: "One doesn't need to stab struggling workers in the back to be a nationalist". That is spreading like a wildfire through the whole city. If we had another week's time to push our standpoint throughout the Reich as well, the wouldn't have to worry about the outcome of the election. Finally, I spoke atan over-flowing tennis court. The reactionary press is going even worse than the reds. But I hope that the Volk will understand us. The open sympathy for the strikers is unmistakable; although Berliners have to accept many inconveniences, they are still in solidarity with the workers struggling for their daily bread. In this election, the goats will be separated out from the sheep. It is an election of convictions like none before. The strike proceeds in undiminished ferocity.

% a