The boycott against the worldwide atrocity propaganda has caught fire at full strength in Berlin and in the whole Reich. I drove, to see for myself, over Tauentzienstrasse. All Jewish businesses are closed. SA guards stand at the entrances. The public has declared its solidarity everywhere. An exemplary discipline reigns. An impressive performance! Everything proceeds in complete calm, in the Reich as well. At the office I make a series of personnel changes, above all regarding the radio. Also, the press division is now newly filled-out and ready for action. Only there is now still a more difficult struggle against the bureaucracy ahead of us, which we will probably have to tangle with for a couple of years.  The situation in the Gau is incredibly good. The finances are in great shape. In the afternoon 150000 Berlin workers march in the Lustgarden, joining us in protest against the agitation abroad. An indescribable \WTF{Siedestimming} reigns. In the evening another 100000 Hitler Youth march. I also speak before them for Bismarck remembrance day. From there a wild ride to the Mueggel mountains, where the eyes are treated to a wonderfully romantic image of Bismarckdom. The German student youth declare their vows for the \WTF{Reichsgedanken}. The press is now already working in full unity. The boycott is a great moral victory for Germany. We have shown the foreigners that we can appeal to the whole nation without it coming to chaotic riots. The fuehrer has again done the right thing. In the midnight hour, the boycott will be broken off by our own decision. We now await the reverberations in the foreign press and propaganda.