Kaiserhof

The fuehrer speaks to the German Reichstag. He is in fabulous form. His whole speech is evidence of a thoughtful clever statesman. Many are seeing him for the first time and many are taken by the grandeur of his manner. There was a two hour break to give the parties a chance to \WTF{comment}. The SPD leader Wels can actually be \WTF{driven to an answer}. It is one long whimpering Jeremiad by the latecomer. The Social Democrats wanted all of that too, and now they whine about terror and injustice. As Wels finished, the fuehrer climbed the podium and gave him a ferocious reply. Never before has anyone been tossed to the ground like that. The fuehrer spoke totally freely and was great in form. The house roared with acclaim, laughter, enthusiasm and applause. It will be a success without equal. The Zentrum and all the Staatspartei vote for the Enabling Law. It applies for four years and gives the government a free hand. It is adopted with a 54 majority, only the SPD voting against. Now we are also constitutionally the lords of the Reich. One member of the cabinet, Labor Commissar Gereke, is accused of serious offenses. The cabinet unanimously decides to have him arrested immediately. Only in this manner is it possible to root out corruption. There can be no favoritism, either above or below. 
Friday: In the cabinet, Hugenberg thanks the fuehrer for the wisdom and straightforwardness of his politics, above all for his brilliant handling of the leader of the Marxists, Wels. For my first bill, I bring up the declaration of May 1st as a national holiday of the German Volk and entrust the cabinet with its implementation. We will stage this in the largest scale, amd for the first time the emtire German Volk will be gathered together in a single demonstration. From there then begins the showdown with the unions. We will not get any rest until they are in our hands. The atrocity propaganda abroad is causing is many issues. The many German-emigre Jews are stirring the entire world up against us. Now we are feeling the consequences of the old state having done no preparations in the area of foreign propaganda. Now we are defenseless against the attacks of our opponents. We have already started with the preparations for May 1st. This celebration shall be a showpiece for the organization and its creative power. I write a very matter-of-fact and objective essay against the atrocity propaganda for a big English paper. We do as much as we can. But all of that is only a drop on a hot stone.
