Kaiserhof

The SA marches in a long procession through Berlin. The past preparations for the election have been made. The struggle is at its high point. The whole route to Hamburg is \?{shrouded in fog}{vernebelt}. Hence we couldn't start with the plane, but instead had to go by train. On the way, we counseled and worked. The thing in Hamburg stands on a knife's edge. Right after the vote, drastic measures are to be taken here. The assembly is extraordinarily prepared, and here the fuehrer holds by far his best speech of the campaign. It is a wonder of oratory rhetoric. The masses go wild. The next morning we all fly back to Berlin early, make a stop there and start right again, after the most urgent tasks are dealth with, on a glorious flight to Koenigsberg. The great "Day of the awakening nation" has dawned. At 2 o'clock we land in the \WTF{crown city}. The last preparations for the evening assembly are put in motion. It will go off without a hitch. I have already given in an introductory report a vivid picture of the day and the repercussions to be expected from it. The fuehrer speaks with fire and devotion. When he at last said that he and the Reich President are hand in hand, the one, who freed East Prussia from its enemies as Field Marshall, while the other did his service as a simple grenadier in the West, there was over the whole assembly a solemn stillness, peace and deepest enthrallment. \WTF{In the mighty final chord of the speech, the thank-you from the Netherlands, in the last verse} drowned out by the ringing of the bells in the Koenigsberg Cathedral. This hymn soars through the aether to the whole of Germany over the radio. Forty million people are now on the plazas of the Reich, in the evening streets or sitting in pubs and private flats in front of loudspeakers, feeling the great changes to come. Hundreds of thousands will, in this houe, come to the final decision to stand behind Hitler and to struggle for the revitalization of the nation in his spirit. At the airfield we learn that a night-flight is impossible. The whole route is foggy and hence a landing in Berlin is totally excluded. We had to drive back to the hotel and already find a heap of telegrams from the whole Reich. An indescribable enthusiasm reigns in Berlin. The whole city is up. Singing draws masses of people into the streets. The SA marches \?{noisily}{mit klingindem Spiel} through the Brandenburg Gate. Hundreds of thousands go through the city quarters, in the center as well as the outskirts. Everywhere on the hills of the countryside \?{freedom fires are burning}{burns the fire of freedom}. All of Germany like a single great shining torch. It is indeed what we wanted the "Day of the awakening nation" to be. Dawning of the Volk!
