Kaiserhof

Up here I have talked through the open questions in detail with the fuehrer. We will transform May 1st into a grandiose demonstration of the Volkish Will of the German people. Then on May 2nd the union houses will be occupied. Gleichschaltung in this area as well. There will perhaps be a few days of noise, but then they will be ours. We can no longer give any ground here. We can only be of use to the worker when we have freed him from the parasitic leadership who have only made their life sour up to this point. If the unions are in our hand, then the other parties and organizations will not be able to hold on for much longer. In any case, the decision was made in Obersalzberg yesterday. There is no way back. One must let things run their course. In a year all of Germany will be in our hands. While we reflect and strategize in the lonesome Summer cottage in Obersalzberg, the Volk stand outside undeterred in masses. In ever-repeating chants the crowd calls to the fuehrer until he finally goes down there and shakea hundreds of hands. One can't get enough of this pure and childlike enthusiasm with which the people greet Hitler. Passing Hitler Youth from Braunau are taken home with us. They eat with us at lunch and are totally glad to sit at a table with the fuehrer. The fuehrer must go back to Berlin. It is gripping to drive through the country with the fuehrer. In all the villages the streets are packed full of people. There are ovations and spontaneous outbreaks of enthusiasm. The children bring him flowers up to the car. They approach right up to the door holding them in their \?{little hands}{Patschhändchen}. In Traunstein the masses have blocked the street. A SA leader comes up to the car and asks the fuehrer to make a half-hour stop, an old party comrade is dying in the hospital and has only one wish, to see the fuehrer. The fuehrer immediately turns around, goes to the hospital and shakes his dying party comrade's hand for the last time. A few hours later he died. At a breakneck speed on to Munich. At the last instant I get the night train, which takes me back to Berlin.

