Yesterday: Thick Berlin air. We ride to the Buelowplatz. The streets throb with mob and \?{communists}{Kommune}. Very dangerous to drive through this. But everything is going well. Büelowplatz one...Kommune rage in the side streets. Tanks, machine guns. Schupo is concerned that none of us gets shot from the windows. Hitler arrives at point two. SA marches before the Karl Liebknecht house. Terrific! Frau Wessel lets us wait a half hour. She is unbearable with her arrogance. Our dead belong to the nation. Two clerics speak. Horrible. Worlds away from us. Then Hitler. Very good and touching. H holds one [!] gravesite open for Frau Wessel. Departure. The Janhagel thrashes in an almighty rage. SA marches. Frightful loss of prestige for the KPD. Buelowplatz belongs to us. \?{Something tossed quickly to Kaiserhof}{Kaiserhof schnell etwas gefuttert}. Then with Hitler to the clinic. Magda is already up. I am so lucky that she is so well and I thank god when she will again return to me. It was very earnest. The doctor had already given up the sweet woman. Hitler is touching. Coffee at Kaiserhof. Briefly worked at home. Stadium overflowing since 6:30. \WTF{Hitler besichtigt noch Wesselsturm}. In the stadium, senseless enthusiasm. Frau Wessel unbearable. Hitler spoke briefly. Not in good form. He was too agitated by Frau Wessel. The audience was wild with enthusiasm. Everything went well. Few clashes. We have won one battle. KPD lost badly. And how! Berlin stands again. Farewell from Hitler. Gone. To Munich. Lay awake the whole night. Slept in in Munich. Now Reichsadler. Much, much work.