Yesterday to Rostock. On the way work with Hanke on the book "Berlin Awakening". Hanke does his part well. Talked through school questions with Krueger. Also much to do there. Rostock: Debated with students. Announcement: Schleicher just stepped down. \?{So we should be set}{Den hätten wir also gekippt}! Faster than I thought. Poor Gregor. The great tactician! Papen tapped to sound out the parties. If that doesn't just become a new chancellorship. Then Hitler is again ... Chancellor Papen means revolution. I spoke at 8:00 before an overflowing hall. Many students. Good form. Right back to Berlin. The papers spew out their consternation. Berlin. To Kaiserhof. Hitler has just dealt with Schaeffer of the BVP. He gives me a clarification. Papen will come here. In any case, better than Schleicher. Who the old man, in his famous faithlessness, has let go. That famous old song! Now you also have to feel what German honor is. But Schleicher can't be blamed. Hitler is still very skeptical and suspicious. With good reason. The...a big band of liars! The pack brawls, the pack agrees. Now the tug-of-war between the parties begins. The old main is predictable. Only no illusions. I remain totally calm and don't let myself be taken by surprise. Perhaps it would be best if Papen would come again. Then since the ... is so imminent, that they aren't able to without us anymore. Only Hitler cannot...unless he already has the chancellorship in his pocket. I will take care if that. Hitler is fabulously certain. He was again right in everything. We sit below with Frau von Dirksen. Hitler speaks about Adel and...merry and inerrant. Crushing. Judgment about...1918. These lickspittles. Home late. Still, played with Helga. She is so sweet. Hitler in the middle of the negotiations. What will come of them? In any case, we are rid of Schleicher. The old man tossed him out yesterday. The just punishment for this Fouché. Now, the tug-of-war. But probably not much will be achieved.
