Kaiserhof.

Our published is advancing us a large sum of money for the electoral campaign. With it we can now work in totally grand style. Goering is cleaning the muck out of the bureaucracy. One Öberpräsident after another is tossed out. Names that meant the world yesterday now fade to insignificant nothingness. Admiral Levetzow will be named as Berlin Police Chief. Lutze is Police Chief in Hanover and Scheppmann in Dortmund. That is good. We are already gradually fortifying ourselves in the administration. Ones comes after the other. The temp of the revolution must not be rushed, otherwise the reins will slip from our hands. Now we also have a new weapon against the press, and \?{und nun knallen die Verbote, daß es nur so eine Art hat}{the now ban has gone out, so that there is only one type}. "Vorwarts" and "8-Uhr-Abendblatt", every Jewish organ which has caused us so much trouble and concern, vanish with a blow from the Berlin street. That soothes, and acts as a balm for the soul. I fly to Stuttgart with the fuehrer in the afternoon. Give an introduction to his assembly, then he speaks. He sharply opposes the still-reigning state president Boltz and the slimy intrigues of the Zentrum. One part of the speech could not be transmitted, because as a consequence of the inadequacy of the official preparations \?{a cable had been destroyed by communists}{ein Kabel durch Kommunisten zerstört worden ist}. Since we couldn't fly back that night, I went right to the Herren responsible for the radio in the hotel and gave them a piece of my mind so that they didn't know what hit them. The very next day, two of them are to be laid off via telegram. Now the others will probably lose the desire to disturb us with sabotage. It still doesn't seem to have gotten around in Germany that a revolution is in progress. Some have taken our initial tolerance as weakness and think \?{we can be trifled with}{uns auf der Nase herumtanzen zu können}. They will find themselves to have been most horribly deceived. One day the sword of our wrath will cleave through the bad actors and smash them in their haughty arrogance into the dirt. I sit together with the fuehrer deep into the night talk through the details of my new ministry with him. We will start with it right after the election. The scope has already been precisely marked out. It will be difficult, since I will have to put together a completely new department, on the other hand it will be easy, since I don't have to start with anything already entrenched, and can start fresh. Two hours sleep. Up again at six o'clock. To the airfield by car, and because of a dense snowstorm went climbed right up to almost 6000M. We could all only breath through our oxygen masks. Most of the passengers were green and yellow from lack of oxygen, only the fuehrer remained unperturbed and didn't have to rely on any means of assistance for a single instant. It was a wonder to us all how he overcomes all strain of the body and the soul. One gets the impression that it does not affect him at all. He does not smoke and does not drink, eats only vegetarian meals, lives simply like any of the Volk, has no pleasures and no relaxation other than his work and his calling. When the German Volk has finally recognized him in all his greatness, he will have won them over in all their millions as his unconditional followers. In three hours we have flown from Stuttgart to Berlin. Straight to the bureaus again to serve. The organization of the electoral campaign is complete. Now we dig deep into the work. But if yields a big success, then it will have been worth it.