Kaiserhof

The big day in Potsdam will be unforgettable in historical significance. In the morning I drive with the fuehrer to Luisenstadt cemetary. We don't go the religious service, but rather stand at the graves of our fallen comrades. The drive to Potsdam goes from Berlin through an eternal jubilant mass of people. Potsdam is drowned in flags and green. The path of the cabinet and the members from the Nikolai-on-Garnison church is almost blocked. We are nearly crushed by a mass of people. Hindenburg meets with the fuehrer at the Garnison church. A solemn silence lies over all present. Softly and earnestly the Reich president reads his message to the members of the Reuchstag and to the German Volk. His tone is strong and collected. Right under us stands a man, \WTF{with generations united in him}. Then the fuehrer speaks. He speaks with hard and forceful urgency. At the end, everyone is moved deeply. I sit close to Hindenburg and see how the tears well in his eyes. All rise and pay the gray Field Marshall, \WTF{hand in hand} with the young Chancellor, a jubilant homage. A historic moment. The shield of German honor is again washed clean. The standards with our eagle are raised high. Hindenburg lays a big Royal Prussian laurel wreath at the grave. Outside the cannons thundered. Now the trumpets sound, the Reich president stands on a raised stage, field marshall's staff in hand, and greets the Reichswehr, SA, SS and Stahlhelm, who march past him. He stands and greets. Above all, the eternal sun, and the hand of god stands invisibly blessing the gray Prussian grandeur and duty. The cabinet sits in the inner ministry. The emergency order against the unofficial uniformed paramilitaries, which gives very harsh punishments, is unanimously resolved upon. Then the plenum meets. The burned-out Reichstag offers no accomodations. We move to the Kroll Opera House. A solemn moment, as the fuehrer enters the Kroll Opera. In a half hour all formalities, which otherwise would have taken almost a week, are finished. Goering is again voted president and introduces himself with a firm and manly speech. In the evening one could hardly get through the enormous masses of people who were marching in unending torchlight processions through the lindens. On trams and busses men, women and children stand, singing and cheering. A fantastic, never-before-seen picture. If one was recognized here, he would probably be crushed. At the close of the evening, an intoxicatingly beautiful performance by a "master singer" in the Linden Opera. Everything os drowned in music. Now the brilliant "Wacht Auf!" choir has \WTF{earned its name again}. Late in the evening General von Epp described the happenings in Bavaria to me. It is all happening promptly and precisely. The opposition offered by the kingmakers can only be described as laughable. It was broken on the first onslaught.
Wednesday: Now I finally move into the ministry. My new space coincides with my taste, sun, sky, light, here one can work. In the evening I sit with the builders, all old SA comrades, and celebrate the \WTF{Baufest} with them. They are loud, splendid guys, who naturally enjoyed striking a blow at the bureaucracy with me.

