Kaiserhof

The battle for the Reich election is already liquidated. We have not only lost no money, but even finished with a enormous surplus. How different this time than in the November battle; but since we did nit give up at the time, we are now able harvest the bumper crop. It is always so in life. From nothing comes nothing, and who does not sow can not reap. I have now set up my ministry in the Rohbau. It will be sliced up into five big divisions, for the areas of radio, press, film, propaganda and theater. Those are all the areas that are very close to me personallt, and which for that reason I will devote myself to with total zeal and total inner devotion. The Hitler Youth march under the lindens. One can watch them for hours and not become weary of the joy. The German revolution goes persistently further and does not stop anywhere. On all public building flags the crooked-cross flag is already flying. Here and there there is resistance from a petty official, but a gentle push suffices to bring to their knees. From time to time a group of German-Nationalist \WTF{Kampfringes} pops up somewhere where none of us is around and raises their flag high. The typical \?{oppositionist}{Schlachtenbummler}, who is always to be found when the danger is past. In Baden, Saxony and Wuerttemberg, National Socialist commissars have been installed. Everything is in order, there is no resistance anywhere. In the evening we are all with the fuehrer; there it is resolved that Bavaria should be next. Though some nervous types outside the party still have reservations,  talk of opposition of the Bavarian Volk's Party and the like, but we are convinced that Herr \WTF{Held} is no \WTF{hero}. In carrying out the revolution we can no longer \?{have any qualms}{Rücksicht kennen}; since we do have the power \?{to use them}{um sie zu gebrauchen}. We do not have to fear resistance. Out enemy has been tossed into the dirt, so he no longer dares move a hand.  The destiny of Bavaria now hangs on a silk thread. No other government would be able to do what the fuehrer intends to do. He can do that, since the Bavarian Volk stands at his side.

