\?{Es ist so weit}{So far, so good}. We are sitting in Wilhelmstrasse. Hitler is Reich Chancellor. Like a dream! Yesterday afternoon in Kaiserhof: we all wait. Finally he comes. Result: He Reich Chancellor, Frick Reich interior, Goering Prussian interior. The old man has given up. At the end he was totally moved. So that's good. Now we must totally win him over. We all have tears in our eyes. We all shake Hitler's hand. He has earned it. Great jubilation. Below the people were making an uproar. Right to work. Reichstag will be dissolved. New election in four weeks. I have no office until then. To the bureau. Everything ceremonious. Magda calls on us. She is going to hit the ceiling. Spoke before the editors and \WTF{Kr.Leitern}. Like a church. The first step! Out struggles. Hugenberg...Papen vice chancellor. Seldte labor minister. Those are minor defects. Must be rubbed out. To Kaiserhof. Hitler meets with the new defense minister von Blomberg. He is very satisfied with him. Hitler is fantastic. Totally great. As I have wished for him. To me very...He goes to his cabinet meeting. With Auwi and Hanfst. To Magda. She almost bursts with joy. Tomorrow she will be free. To Kaiserhof. Waiting on the torchlight procession. Questioned by the police. On the Alvenleben matter. He is to be arrested today. This cowardly intriguing. Hammerstein wanted to \?{block}{abfangen} Blomberg. Failed.  The torches arrive. It begins at 7:00. Endless. Until 10:00. To Kaiserhof. Then Reich chancellery. Until 12:00. Unending. A million people on the way. The old man takes in the march. Next door, Hitler. Breakthrough! Spontaneous explosion of the Volk. Indescribable. Ever more masses. Hitler is gone. His people celebrate him. I speak on the radio. over all German transmitters. "We are immeasurably lucky". Kubisch also speaks. Once as a Stahlhelm, once as my chauffeur. \?{The Stahlhelm has dissolved into the mist}{Der Stahlhelmer selbst fällt aus wegen Nebel}. I speak to the masses from the Reich chancellery. After midnight. Heil to Hindenburg and Hitler. Senseless giddiness of enthusiasm. Reflected with Hitler. The Reichstag is to be dissolved today. Tomorrow, proclamation to the people. \?{We will already be up}{Da werden wir schon auf}. To Potsdam for Auwi. Everyone drunk. Home at 3:00. \WTF{Sturmf.} Hahn there. Maikowski shot. A Schutzpolizei too. From the commune. But now, finished! Goering must smoke it out. To bed. Dead tired. I can't any longer. Slept in. Now to work. Prepared for the electoral struggle. The last. We will win it \?{bigly}{haushoch}.
