Yesterday: bad weather in the morning. Overnight, there has been a massive attack in England. But Churchill puts out more lies. He has also lied so fantastically about the attack on Berlin that is is easy to hold him up to the German people ad absurdum. Our Luftwaffe reports conscientiously. I read some daily reports which contain every tiny detail. I have also made the material available to my superiors and the press. Martin gives a report on the military situation. London had nothing to laugh about the previous night either. \WTF{We led the campaign against sleep.} On top of that, still ceaseless bombardments. Wodarg claims that the English flight to Berlin is not an especially heroic act, and \?{backs this up with details}{belegt das im Einzelnen}. We intensify the air defenses and all preparatory measures. By order of the fuehrer, everything must go back into the cellar upon the air raid alarm. And that is just as well. Goering's decree is repealed \WTF{by the Praxis}. The Italians pompously comment on the Viennese negotiations while we, according to the arrangement, keep silent. Again the typical lack of discipline. Discussed a series of art questions with Biebrach. He works well. Midday with the fuehrer. He looks very well and rested and is in the best mood. We were able to talk fir 4 hours and discuss all open issues. Here, briefly, the resumé: the weather prevents still grander aerial operations. As soon as it gets better, it will start in grandest style. England will probably not be able to withstand our aerial attacks for too long. At least that is what we believe and hope. Already today there are very pessimistic voices coming out of London. But naturally one cannot say anything more specific. The English power of resistance is not too well-known. Our prospects are, now as before, very good. We hope to be able to avoid a second Winter of war, but we are preparing for one. Above all, the fuehrer proposes a gasoline reserve. Better safe than sorry. Because of the oil question, he also wants peace in the Balkans. That is why he pushed so hard in Vienna. Though the Hungarians got so much, and the Romanians accepted under protest. But, they did in the end. For that, we and Italy guarantee their borders. Even against Russia. Moscow's appetite there will soon pass. They won't want to get into a quarrel with us, since we are not English or Finns. Romania and Hungary are unhappy with us. But, that is the fate of the arbitrator. Peace in the Balkans. And we get our oil. The fuehrer discusses theatrical questions with me. Above all, the new construction plans for Koenigsberg, Linz and Berlin. Vienna lies very close to his heart. He wants to revive an old plan by Semper for Dresden. The new opera in Berlin is to be a Reich's Opera. The loveliest and the best that it can give. He is not in agreement with the closure of the Western theater ordered by Goering. The relevant decree is repealed. He praised our new film and is constantly enthusiastic about our weekly shows. \missing As regards the stolen artworks, he gives me full power and authority. We will take back everything that the French have stolen from us over the centuries. He strongly praised Reventlow's book "From Potsdam to Doorn". He gave 5000 copies of it to the Wehrmacht. Reventlow got 10000 marks. His work is a biting critique of the Kaiser's Germany. It is very useful for us. The fuehrer explains our new \?{long-distance defenses}{Ferngeschütze} to me, which are a technological marvel. And now there are new night attacks on England, \?{and then soon the devil will really be loose}{und bald ist dann wirklich der Teufel los}. \missing