Yesterday: The fuehrer's speech went over very well here and abroad. It projected an enormous strength. Only London is making foul jokes about it. \?{But that has already passed the plutocracy by.}{Aber das wird der Plutokratie schon vergehen.} The weather is very good. A...three-day undertaking of the most radical type shall now arise. Keyword: \WTF{Loge}. The last night again brought a series of English air raids. We were not quite so active. Our blow must come like a bolt from clear skies. That will strike. America shows more insolence. But by and by the English have been nicely fleeced. Very good results with the U-Boats. The Italians have avoided a sea battle at Malta. But so did the English.  Nobody wants to risk his fleet. In Romania, General Antonescu is appointed. He has stripped almost all power from the king. Not much is left from the \?{monarchy}{Königsstaat}. This \WTF{Carol} will yet reap the fruits of its labors. A first-class \WTF{Dreckstück}! Japan has withdrawn its ultimatum wrt Indochina. US threatened. A confused world! I give instructions to the press. The progress of our "Marion" transporter has now nonetheless come out in the Scandinavian press. We'll see how we get ourselves out of that. Went over new weekly newsreel subjects with Hippler. Hess has also fallen madly for "Jud Suess". It will be a big hit. Von Tiedermann reports on Holland. Mood still tense. No active opposition. But everyone still hopes for England's victory. \WTF{Intelligence at the top.} With Gutterer, discussed the \?{AO}{Auslandsorganization?} question and collaboration with Bohle. Bohle does not want to work with Brauweiler's division. But that he must. The ministry's structure must not be destroyed. But otherwise the AO's work must go on as freely and unimpeded as much as possible. I provide the means for this. And then Gutterer will worry about the supervision. Question of the cultural film fund finally resolved. Which now brings about \WTF{8 Mio} per year. With that, that is already enough to do something. What glorious weather! The air raid \WTF{lockt}. Only a little while longer! Midday with the fuehrer. Air raid in our region took another 15 dead. The fuehrer has had enough of it and now gives London over to total bombardment. It will be loosed tonight. That means the warning shots are over and London is finally, finally going to feel the hardships of war. That is essential. A city of millions \?{cannot be harmed}{kann man...nights anhaben} with mere air raid sirens. Stolen sleep cannot defeat a people. Demoralization only comes after devastation and terror. So, let it loose! Then we shall however \WTF{still get something to feel}{auch noch einiges zu verspüren bekommen}. The effect of the fuehrer's speech is nil in Official England. But, in the English people and the rest of the world, its great effect will be felt. Otherwise, the fuehrer will strike against England when he is ready. Not a day sooner. Discussed the future of Berlin with Speer. Lippert's posts must be filled again as soon as possible. He wants me to take the City President post myself. Because of a lack of time I will not be able to do that. The new construction of our ministry is being prepared in the best and most grand style. Dr Dietrich has arranged the technical outfitting of the DNB and the ministry. Here we will also somewhat stem the AA. Our prisoners get better food and lodging that the German populace. Typically German. With General Jodl it is decided that this is to stop immediately. Our speedboats sink a large portion of a convoy. On top of that, 3 more English destroyers are sunk.  Ratio 57:17. But it must be let loose! Bernard Shaw writes a witty interview against the Ministry of Information. He has now also been muzzled, as he himself has said. Also[!] England already come reports on the devastating effect of our aerial bombardments. And there is more to come!