\letter{703}
\rcpt{Jauch}
\date{September 8, 1944}
\location{Saranac Lake}

Dear Herr Jauch!

Best thanks for your remarks included in Lopes's letter. Your complaint that you'd found no reference in the literature to the Hermitization of interaction operators has unfortunately not taken account of my reference to the paper by Hulme (see my penultimate letter).

Now to the question of the singularity of the $V$-operator. (a) or (b) (c.f. my current letter to Lopes), that is the question! What do you think? But even in the more favorable case (b) (which was the focus of my last letter) taking the recoil into account can \textit{never diminish} the singularity! This probably applies also for Hulth\'en's relativistic correction to the quadropole moment. \?{And the cut-off is hideous!}

This criticism also applies for strong coupling in the pair theory with spin-dependent forces. \?{Indeed, there is the "apocryphal" paper by Oppenheimer and Nelson.} Its result, that the cutoff radius can \textit{not} be set up so that both the range as well as the strength of the force is in harmony with the requirement for strong coupling in the pair theory - this result seems very plausible to me.

I am not \textit{a priori} against the pair theory, but I am very much against strong coupling. My physical feeling is this, that the first approximation (perturbation theory with respect to the coupling parameter) of the present theories have something to do with reality, but the higher approximations (which diverge without cutoffs) in a future, reasonable theory \?{must be much smaller}. -- Now, in Princeton you could tell me more about your project for Blatt.

When is the seminar?

Many greetings,

Your W. Pauli

%eas   Comelyc