\entry{June 29th 1934}

Wednesday: the situation becomes ever more serious. The Fuehrer has to handle it. Otherwise the reaction will drown us. Count Welczek-Madrid. Frightful conditions in Spain. On the eve of Bolshevism? Bank Director Mueller for the consumer cooperatives. \?{Da müssen wir kurz treten, sonst große Pleite}{We must act soon there, otherwise all is lost}. Laubinger is well again. Or does it only seem that way? Still many unsolved theater questions. Mayor Markert-Bremen describes to me the hopeless situation of foreign trade. With the fuehrer: capital of the "K..." with Raeder. Interesting report of the world travels of the ship. We have many enemies. I to Kiel. Linse-Marine friction there. Must be settled. I tried. Linse very nice. Everywhere worries about reaction. Speech before 60,000. Good success. The people are waiting foe us to act. Sour mood in the RW. Wrote Papen's speech on Dr Jung. Dispute about that...At midnight, Berlin again. Hanke brings the latest pastoral letter to the clerics. Sharply against the state. Now however to work. Magda is very dear. Thursday: Berlin work. But ever more depression. Reaction everywhere \?{at the factories}{am Werk}. Out to Cladow. A free afternoon. Ate with the fuehrer. Terboven wedding. Boat ride with Magda and the kids. Then it started. Impertinent Bremen newspapers. Warning. "Old guard" of Hamburg has K.O.'d the Portuguese General counsel. I can't get there. The perpetrators left the hall. Long telephone negotiations. \?{Endlich melden sich 2 Unschuldige}{Finally, 2 found without blame}. Brave spirit! Spandau. Honest and plainspoken. The people understand. Streets packed full of people. Many handshakes. To Cladow. How long? This morning, call from the fuehrer to fly immediately to Godesberg. So it goes. In god's name. Anything is better than this terrible waiting. I am prepared.