\subsection*{72.}

We shall now try to characterize this universe by invariant properties, that is to say properties that are independent of any choice of particular reference system at each point of the universe. We remark first of all that \textit{in this universe the space is metric}: this is our Euclidian space. Thus we have, \textit{among all universes with an Newtonian connection (that is to say with a metric space) and no torsion, characterized that of Newtonian gravitation.}

If with the aid of the formulae (4) we calculate the forms $\Omega_0^i, \Omega_{ij}$ which define the curvature of the universe, we obtain immediately\footnote{The expressions obtained for the $\Omega_0^i$ show that a Newtonian universe whose gravitational field is at each instant uniform has no curvature. The fact that when a material system is immersed in a uniform gravitational field it is impossible for mechanical experiments made on the interior of this system to detect this gravitational field shows indeed that we perceive only the \textit{curvature} of the universe, manifested physically be the \textit{variations} of the gravitational field. \textit{Cf.} Chapter I, p. 335, note (3).}
\nequ{5}{
\Omega_0^1 = -[dXdt], \quad \Omega_0^2 = -[dYdt], \quad \Omega_0^3 = -[dZdt],
}
\nequ{I}{
\Omega_{23} = \Omega_{31} = \Omega_{12} = 0.
}

The law according to which gravity is derived from a potential is expressed by the relation
\nequ{II}{
[\omega_1\Omega_0^1] + [\omega_2\Omega_0^2] + [\omega_3\Omega_0^3] = 0;
}
the Poisson formula is similarly expressed by
\nequ{III}{
[\omega^2 \omega^3 \Omega_0^1] + [\omega^3 \omega^1 \Omega_0^2] + [\omega^1 \omega^2 \Omega_0^3] = 
4\pi f \rho [\omega^1 \omega^2 \omega^3 \omega_0],
}
$f$ designating the coefficient of universal attraction and $\rho$ the density of matter; the second oart of this last equation is, up to a factor of $4\pi f$, the elementary \textit{action} $dmdt$. 

We will show:

\begin{enumerate}
	\item That the relations (I), (II), (III) have an invariant character for all manifolds with a Newtonian connection and zero torsion;
	\item That they characterize the universe of Newtonian gravitation, given zero torsion.
\end{enumerate}