\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}

\newcommand{\WTF}[1]{\textit{???}#1\textit{???}}
\newcommand{\byline}[1]{#1}
\newcommand{\?}[2]{#1}

\begin{document}

\title{Politics and Bohemianism}
\author{From our A.B. comrade}
\byline{Munich, at the start of Februrary [1919]}

\maketitle

\abstract{The Munich riddle. -- the Ur-Bavarians Eisner, Muehsam and Levien. -- The political Bohemia. -- The \WTF{Kommunisten-Gut} with two types of love. -- The effect abroad. -- Eisner's future prospects.}

There is now with Munich politics, as it was with Munich art; one asks himself: \?{Whither}{Wo stecken} the Munichers, the Bavarians? In art, one comes across East-Prussian, Württembergish, all possible names -- and yet it was "Munich" art. And now in politics? It is actually unnecessary to slander the minister-president of Galiziertum under and doubt his German name. He himself has confessed to being a "Preiss" and is now a total Berliner. And his main rival on the left, who in many circles enjoys as high a regard as \textit{Eisner}, since he has regard, even still today, where the votes have somewhat decided against him! -- even his radical opponents are not as Bavarian as he. \textit{Erich Muehsam}, the noble anarchist, whose star rose in the German cafes of the west and for a long time beamed soft literary light in Berlin (despite all noble anarchist light), before he filled himself with more active bloody political red, Muehsam, who by nature was always a lively, helpful, unwarlike creature and about whose revolutionary heroics one would like to laugh about even today, if it was not also \WTF{acting} wildly and dangerousl, , is indeed sufficiently well-known as a Berlin \WTF{W-Pflanze}. i.e., he was first transplanted there. Growing up as a son of a Luebecker pharmacist in the (at the time still so quiet) Hanseatic city.

A newer appearance is the doctor \textit{Levien} -- as reported from Munich, Dr Levien has been arrested in recent days, who played the most serious role here in the \WTF{A.- and S-Rat} and on the Spartakus side, and the government, who naturally does not want to create a martyr, is more than uncomfortable. In order to get it out of the way: the Doctor Levien is not a Russian Jew, he has German blood in his veins, he shakes his blonde locks in mighty gesticulations, blazing blue eyes, he tugs at the button of his field-gray uniform, when he, agitating with raised right hand, defends himself against the charge of being a foreigner, of being able to speak the language. So at least I saw and heard him in an assembly where he thundered against the "reactionary" Eisner. But of course, when he then painted the poor, slandered Bolsheviks in the proper, namely the soft rosy humane colors and now suddenly stood up against another objection, how he knew the Russian condition so well, there he thundered with clearer conviction and clearer gestures how he was before: "I have stood as a German in the field!" this time: "I was born in Russia!" That also did not completely jibe with the Bavarian-ness of this leader of the people.
\end{document}
