\subsection*{49.}

\nc{\opU}{\mathbb{U}}
\nc{\opV}{\mathbb{V}}
\nc{\overu}{\overline{u}}

For this we return to our first point of view. We imagine in the manifold $(V)$ a volume delimited by an infinitely-small closed surface. Associated to each element of this surface enclosing a cergain point $\m$ is the infinitesimal transformation $\Theta$, \?{in symbols}{de symbole}
\uequ{
\Omega_1 X_1 f + \dots + \Omega_r X_r,
}
which we may interpret as defining a \textit{displacement} $S$ in the space $(E)$, defined analytically by using the coordinates adopted by the observer at $\m$. Then let $\xa$ be a fixed point inside the volume under consideration. The \textit{same} displacement of the space $(E)$ may be expressed analytically by means of the coordinates adopted by the obsver $\xa$, \?{since it is known how to pass}{puisqu'on sait passer} from one to the other when the two observers are infinitely close. Let
\uequ{
x_1, \dots, x_n, \textit{ and } \overx_1, \dots, \overx_n,
}
be the coordinates adopted by $\m$ and $\xa$ respectively. The passage from the latter to the former is made via an infinitesimal transformation $\opT$.

Finally we designate by primed letters the coordinates of the point transformed by the displacement $S$. It is immediately seen that the passage from $\overx$ to $\overx'$ will be obtained by applying the transformations $\opT, \Theta, \opT^{-1}$ successively. Put another way, the displacement $S$ will be defined by adopting the coordinates of the fixed observer $\xa$, via the transformation $\opT\Theta\opT^{-1}$.

Then it is easily demonstrated that if $\opU f$ is the symbol of the infinitesimal transformation $\opT$, $\opV f$ that of $\Theta$, the symbol for $\opT\Theta\opT^{-1}$ is
\uequ{
\opV f + (\opU\opV) = \opV f + \opU(\opV f) - \opV(\opU f).
}

If one calls $u_h$ and $\overu_h$ the respective coordinates of $\m$ and $\xa$ on the manifold $(V)$, and putting
\uequ{
\omega_i = \gamma_{ih} du_h,
}
we have
\uequ{
\opU f = \gamma_{ih} (u_h - \overu_h)X_i f,\\
\opV f = \Omega_i X_i f,
}
and, finally.
\uequ{
\opV + (\opU\opV) = \left\{\Omega_s + c_{iks} \left[
\gamma_{ih}(u_h - \overu_h)\Omega_k -
 \gamma_{kh}(u_h - \overu_h)\Omega_i\right]\right\} X_s f.
}
This is the analytic expression for the displacement $S$ when it is related back to the reference system of the point $\xa$.

Taking the \textit{sum} of the components of the displacement, over all the elements of the closed surface under consideration in the manifold $(V)$, it is found, for the $s^\text{th}$ sum,
\uequ{
\Omega_s' + c_{iks} \left([\omega_i \Omega_k] - [\omega_k \Omega_i] \right),
}