\header{July 21st 1924}

Thomas Mann, "Königliche Hoheit". A painful book for the author and for the reader. The conflict is rather \?{garden-variety}{gartenlaubenmäßig}. The style already made rather strong. An artist of the word. A great disappointment over Mann. Strongly recalls his brother Heinrich Mann. \?{On nationalist grounds, the book is absolutely to be rejected}{National ist der Buch unbedingt zu verwerfen}. More from it when I read selectiojs from it. In that way I still have no view over it. I think so uch about Anka Stalherm. She appears to me in dreams with surprising clarity and speaks with me. In it she rather skeptically shuts one of her \WTF{mysterious gray-green eyes}{graugrünen Augenrätsel}. Strange: I live entirely under her spell. Often on her street I think, I must see her. Yesterday Else was at Mörs, and then I had a great desire for the so-long forgotten girl from Recklinghausen. What does destiny have in store for me? Yet not new love-sickness and torment and pain? Since the time that I lost Anka, I could not have back at any price. I believe that I would then have to be destroyed. Would I ache the same way at the loss of Else? No! I probably love her less than Anka Stalherm. \?{In his life one loves just once, if he is lucky, like the gods do}{Man liebt eben, wenn's gut geht, in seinem Leben nur einmal wie die Götter}. I believe that a new encounter with Anka today would frightfully disappoint me. One always idealizes the past. Only the present is gray and hopeless. Konrad 
as moved out with his kith and kin, and now there is a strange silence here in the house. At first it weighed somewhat on my spirit. But now I find it delightful. The whole day one doesn't hear any noise. Only Minka bangs in and then again out. Outside rainy and gray. Up here in my boudoir, cosy spiritual peace. So today I am rather satisfied and happy. Richard died on Saturday, I dreamt the night of Saturday-Sunday about Anka. Did the dead wake up? A warning of the dead to the living? Anka Stalherm, you lovely, good person, I yearn for your sweet conversarion, for your soft hand and your kind mouth. If something is to become of me, then I want to see you once more! Yesterday gone through forests and fields. Innocent Summer Sunday afternoon. Wonderful stroll through god's colorful garden. Politics depressing. In London, rich bankers haggle over Germany's work flrce for 40 years. Not so fast, mein Herren! You are still not at the end. \WTF{The history of the world is the world's judgment}{Die Weltgeschichte ist das Weltgericht}! Olgi wrote me today from Switzerland. Dear girl. If I could only get out of the country! Mother and father are so good to me these days. I do not know what I did to deserve it. And Else loves me a hundred times more than I have ever deserved it. Life bestows its gifts upon me. And I am so poor that I can hardly give anything back.
%