\header{July 4th 1924}

Finishsd Rosa Luxemburg's letters. In the continuing lectures one notes the nonsense [!]. There is no nature in them. Their flower- and animal-love is the yearning for a big-city type for the lost nature. Their literary remarks are often more than primitive. But perhaps I am being unjust, since I am biased. \WTF{Outside of one's skin one cannot be a good person}{Man kann als Mensch so schlecht aus seiner Haut [Haut durchgestrichen] heraus}. And now my skin is a rather one-sided antisemitism. But I will never recognize that Maximilian Harden is no \?{scoundrel}{Lump}. A \?{scoundrel}{Gesinnungslump} par excellence. This infamous person, the greatest warmonger in 1908-1915, yet goes to America and besmirches the land that he earlier called his "Fatherland". These sort of people always remain the same. Our worst enemy in Germany is Jewry and Ultramontanism. How strange that our great Volkish movement has become all at once so superficial and worn out. Are we resting on our electoral laurels? Why are we not working? \?{I would like a victory and doubt a breakthrough}{Ich möchte an Sieg und Durchbruch verzweifeln}. Olgi wrote me a dreamy letter from St Moritz. \WTF{Complaints about the business with the Germans in the Swiss luxury bathrooms}{Klagen über das Treiben der Deutschen in den schweizerischen Luxusbädern}. "They are mostly only Jews." Who suffers under this? Our German children, who the foreigners will no longer help. I read Gustav Noske's "From Kiel to Kapp". What upheavals this social democrat from the glorious revolution shows. What a sum of cowardice, despicableness, \?{empty phrase}{Phrasenbrei} in the time from Kiel to Kapp. We are lacking a strong hand in Germany. Put an end to experiments and phrases. Begin with honesty and work. \?{Kick to the curb}{an die Luft setzen} the pack of Jews that do not want to submit to the \?{responsible idea of the racial community}{verantwortlichen Gedanken der Volksgemeinschaft}. Also kick to the curb \?{the nest of financial speculators}{verhauen. Geldabenteurer}. Gustav Noske had something of a strong hand. If he had only used his instruments of power to battle the Jewish threat! We would be further along today. Germany yearns for the One, the man, like the earth does for rain in the Summer. We are preserved only by the combination of power, enthusiasm, and ceaseless devotion. Those are all indeed wonderful things. But can a wonder save us? Herr, show the German Volk a wonder! One wonder!! A man!!! \WTF{Bismark, sta up!}{???} My brain and heart are as dried-up from despair for myself and my Fatherland. A crushing weight lies over Germany. One must expect the worst. I want to help with the reconstruction. And everywhere I am rejected. The current battlw for the face of Germany is the ancient battle between father and son. Despair! Despair! I can no longer live to see all of that injustice. I must struggle for justice and freedom! Help me, great god! I am at the end of my strength!!!

%{}same.