\header{June 30th 1924}

Yesterday in Elberfeld. So these are the leaders of the Volkish movement in the occupied territory. You Jews and you French and Belgian gentlemen, you have nothing to fear. With them, you are safe. I have rarely taken part in a meeting with so much \?{blathering}{geschwafelt} as the one yesterday. And most of that was against their own comrades. In the unoccupied territories the struggle, which I have long expected between the Volkish Freedom Party and the National Socialist Workers' Party, has already flared up most violently. Indeed the two don't belong together. The first wants Prussian Protestantism (they call it the German Church), the other wants greater-German reconciliation -- though probably with a Catholic element. Munich and Berlin are in conflict. One can also say, Hitler and Ludendorff. Which way I will go, there can hardly be any question. To the youth, which actually wants the new man. The old of the \?{camps of the defense- and defiance-leagues}{Kämpen des Schutz- and Trutz-bundes} want the youth out of the way. Perhaps they are uncomfortable with the successes of the youth. I am for a clean break -- even in the Reichstag. Where they can go together, they can go together, -- where they cannot, they should not feign a dishonest unity. How pitiful yesterday afternoon was. Only \?{busy work}{Kleinarbeit}. Personal quarrels. No magic words, no brilliant thoughts. A mix of cowardice, vulgarity, trying to be a big man, and \WTF{social climbing}{Strebertum}. How embarrassisng was the impression that I brought home. I would much rather gonwith Munich than Berlin. If only Hitler were free! Maximilian Harde, "Trials". What frequent lies, what smugness, \WTF{as if it was written for his own love of noise}{wie für den eigenen lieben Rausch geschrieben}. In it, a surprising flash of inspiration. My Herren Volkishmen, you must be rather more active, be rather more mentally elastic, in order to make this type of writer go kaputt. It will not happen with complaining and \WTF{..ing}{..ung} along. Harden is a man who goes after the whole thing, with focus, \WTF{caustic wit}{Lauge, Witz}, and satire. The typical Jewish manner of struggle. Can the Jew be beaten with his own weapons? I look with great worry to the Volkish future. The idea of the Volkish Greater Germany is good. But it is missing efficient, harf-working, clever and noble leaders. Nothing can be done with good will and noble sentiments. We must all work. Boundless work. Otherwise we are finally lost. Many beautiful hours with Else, and many hopeless, hard, harrowing confrontations. How hard life is. How often the wish and the thought comes to me: away from here with its hustle and bustle, alone, lonesome, a little house in the forest, ... that is enough to get by. And let the world be the world. Elberfeld is a beautiful city with strikingly-many lovely ladies. It must be good living there! Herr Wiegershaus, the Reichstag candidate: Wilhelmian, portly, twisted mustache, \?{body odor}{riecht aus dem Halse}, forthcoming, a good chap, but not a man that can impress the youth. No fuehrer nature. I still don't see any Volkish fuehrer at all. I must find one soon, \WTF{so that I can get some new courage and confidence}{damit ich mir wieder etwas neuen Mut und neues Selbstvertrauen hole}. \WTF{That hasn't happened yet}{So geht's nimmer}. Hope for another one crumbles. \?{I'm running straight into despair}{Ich renne schnurstracks in die Verzweiflung}. Back to work! In the end, one is only what he makes of himself. A person is only worth as much as he would give for himself, if he were not himself. I hate petty politics all the way in my down soul. \WTF{Connections, my Herren, lines, views}{Zusammenhnge, meine Herren, Linien, Aussichten}. They couldn't hold onto the youth for long. Now I wait for the end of the \WTF{credit crisis}{Kreditnot}. I have waited an eternity for position and money. Despair! Skepticism! Breakdown! I no longer know where to turn.