\header{July 17th 1924}

Yesterday evening a delightful auto-tour to Cologne and back. Saw Cologne at night once again. Wonderful to cruise through the evening this way. After a refreshing rain the sky was like balsam. Moths flew against the headlamps. Raindrops dripped from the highway trees like thick gold. One gentleman ran straight towards the car and turned away at the last second. The path goes through small, sleepy villages. Like a stormy wind we drove. Dostoevsky's "Nettchen Neswanow". A charming young girl's face. Again drama interwoven with drama. The love between Katja and Nettchen is a masterpiece of psychological art. The Russians did so easily, like no one since. The psychology is always brilliant in Dostoevsky. Incidentally however "Nettchen" is, in comparison to Dostoevsky's great novels, is more of a \?{casual work}{Gelegenheitsarbeit}. Often it is too small for the great, great Russian. Perhaps he needed money. Or he wanted for once to take a break afer a great novel. I know so little of Dostoevsky's life. \?{And after that I have no desire to learn more}{Ich trage auch kein Verlangen darnach, mehr zu erfahren}. I am so dejected with respect to everyday life. Everything I start goes wrong. I do not emerge from the hole here. As if my wings were clipped. So sapped and powerless. Up to now I still have not found any proper purpose in life. Many times in the morning I wake up in fear from it. Nothing awaits me: no joy, no pain, no task and no purpose. My life is lacking concentration and \WTF{togetherness}{Sammlung}. I wander and rave around through the universe. To an upstanding life belongs above all a fixed purpose and a firm foundation. I am missing that. How often I ask myself now: what am I to do? What to begin? Eternal doubt. Eternal questions. How dried-up my spirit is. Something has put me off. To burn and to not be able to set ablaze! The money, that I do not have, lays me low. Miserable life that must be directed towards the damned money. \WTF{Curses and rottenness around me}{Fluch und Verderben über mich}. I am outraged with the existing order. Now I bear the consequences. Redemption! I stumble from place to place, from blame to blame in the abyss. Unfortunate undoing! \WTF{What good is newspaper chewing!}{Was nützt die Zeitungskauen!} One only becomes dumber and more imbecilic that way. Politics is ruined for me.

% 