\header{June 27th 1924}

May this book contribute to me becoming clearer in mind, simpler in thoughts, greater in love, truer in hope, more glowing in belief, \?{more modest}{bescheidener} in speech! Franz Herwig. "Sankt Sebastian vom Wedding". A Christian novel. I must think more on Jakob Wasserman's "\WTF{Creation of Christian Myths}{Christian Wahnschaffe}". But this Saint Sebastian is purer, more convincing, in a word, more Christlike. Some of the true spirit of Catholicism goes through this little book. Also some of Franz von Assisi. How far the official church is from this spirit! All of these books on the spirit of the original Christendom, that is nothing but the product of a strong yearning for the spirit of Christ. Hauptmann "The Fool in Christ". For now, the only book in the German language with this idea. But how far does the "Fool" stand behind Dostoevsky's "Idiot"! Russia will find the new Christian beliefs with all the youthful fervor and all the childlike beliefs, all the religious torments and fanaticism. These days I often imagine the future of Germany and Europe. What will this part of the world look like in 50 years? Probably totally different. Today we have a new man, or at least the beginnings of one. The human society has remained the same old way. There will not be rest in Europe until this form of human society is broken. The new race will give its new form, suitable to itself. The course of history cannot be held back. The new man has always and everywhere only one desire: a new world. \WTF{Else is good to me like the Summer}{Else ist sommerlich gut zu mir}. I would like to take a wedding trip with her, with lots of money, lots of love, without worries, down to Italy and Greece! i read this morning R Wagner's "The Art of the Conductor". Or the musician, a treasure trove of \WTF{conductor's delicacies}{Dirigentenfeinheiten}. Lecture on Maximilian Harden (alias Isidor Witkowski) "\?{Trials}{Prozesse}": (Köpfe. 3rd part.) What is this damned Jew but a hypocrotical swine. Lumpen, scoundrel, traitor. They suck the blood from our arteries. Vampire! I sit in the newly-installed porch and enjoy the beautiful Summer day. Sunshine! Mild beautiful wind! Scent of flowers! How lovely this world is!!!