\header{July 2nd 1924}

Maximilian Harden, such a lying Polish \?{Jewboy}{Judenlümmel}. \?{How vulgar}{Wie gemein manchmal}. This apparently-patriotic bravery hides hypocrisy. This Jewish sophistry grates on the nerves. \WTF{This loving semitic self-adulation}{Diese liebevolle semitische Selbstberäucherung}. "You can judge me when onlythe nation is saved." How gruesome this \?{Jewish dog}{Judenbengel} is against the men who are in his power! With Harden one can, if one opens one's eyes, study the whole race question. Then the most common things that the goyim in the provinces don't notice. "Your name?" "Ernst, Felix, Maximilian Harden, of the protestant denomination." Haha. An upstanding patriot! A man who loves the truth. I don't get down into the mud. I am not a sensational man. A Maximilian Harden! A writer of rank. Than an artistic impulse. \WTF{The judge pinches the tail}{Der Richter kneuft den Schwanz ein}. (Probably also a Jewish dog, named Lehmann, \WTF{the prosecutor called him Preuss}{der Staatsanwalt heißt Preuß}.) This patriotic \WTF{Gimpfwlfang}{???}. "I have wrestled with myself for seven years." -- But then I have poured it into the German public with gusto. God, what a swindle. Herr Maximilian Harden = Isidor Witkowski, Protestant = Jewish denomination, German = Polish = semitic nationality, you patriot, you brave fighter for truth and justice, you are a lout, a lump, amd the greatest swindler of the 20th century. You have proven this to even the most idiotic after the war with your columns against your German "fatherland". \WTF{There you let down the mask hiding your Jewish character}{Da durften Sie die Maske von Ihrer jüdischen Fratze reißen}. -- And you have done it with gusto. Assez! It is not worth the effort! It it were up to me, then you, along with Heern Warburg, Herrn Louis Hagen, Herrn Nathan, and several other yellow dogs would be shoved over some border in a cattlecart. The spirit is a weapon for us. We must overcome the spirit. The spirit torments us and drives us from catastrophe to catastrophe. Only in the purest heart does the tortured person find a resolution to the pain. \?{Beyond the spirit for pure men!}{Über den Geist hinaus zum reinen Menschen}! Rosa Luxemburg, "Letters from prison to Karl Liebknecht". Perhaps an idealist. Sometimes startling in her intimacy, in the warm, dear tone of friendship. (Incidentally, the letters are directed to Sonja, the Frau Liebknecht, and not to him himself.) In any case Rosa suffered for her ideas, because of them sat for a year in prison and finally -- died for them. That cannot be forgotten with all these trains of thought. But these Jewish ideologies do not take into account the eternal law that has been written in the breast of all occidental people: the love of the fatherland. For that we combat this fantastic, lying -- because it is unnatural -- world of ideas. Thus have probably many idealists on both sides gone into the ground. Whether idealists or not: we do not need to have the love and \WTF{responsible consciousness}{verantwortungsvolle Bewußtsein} with respect to the fatherland be torn from the hearts of the foreign elements. I now sit the whole beautiful Summer day outside on the porch, beset by balmy winds, in the middle of the sunshine. And let my thoughts fly like \?{little flakes}{leichte Flocken}. I am collecting for the Winter. There one must have a stock ready. The dear Olgi from Switzerland sent me a packet filled all the way to the top with wild red Alpine violets, which are on my table and give off a sweet mountain air. The good, dependable friend. I like her very much and sometimes feel a great desire to talk with her once again. She is so to speak the constant connection that always brings me back to Richard. \?{Whoever stands truly close to us in life cannot leave us in death}{Wer uns im Leben wahrhaft nahe stand, kann uns im Tode nicht sterben}. The spirit is not lost in this world, in some form and in some people every word, every thought, every idea keeps acting until the end of time. Richard lives in me, and through me in all people who have \WTF{taken up my ideas}{mein Gedanke aufweckt}. Before my eyes stands a blood-red greeting from the Swiss mountains. Richard and Olgi! How much love and loyalty has been given to me in my life! I am once again \?{on most intimate terms with}{aufs innigste vertragen} Else. A wonderful hour of mutual understanding. I have her again just as in the beginning. She is so sweet and dependable. The sharpest weapon that a woman has against us: a flood of tears. Against it we are powerless. I heard Else giving orders in the neighboring schoolyard. She will definitely be pleased at our rendesvous this afternoon. I am her everything. \?{Why does fate give me so much to love}{Warum gibt das Geschick mir so viel an Liebe}? \?{Why can I give back so much love}{Warum kann ich so viel an Liebe wieder geben}? Am I different from all the others? Born under a lucky star? \WTF{Or might I cost life more with its treasures, since I once had to be cut off from them early}{Oder darf ich das Leben stärker kosten mit seiner Schätzen, weil ich einmal früh davon scheiden muß}? Sometimes I have such feelings! One can be so sentimental! On to the work, my boy! Learn, so that you won't become a windbag! 


% aryan yahoo