Yesterday Strasser's daily paper actually appeared, though in Berlin. And with that, all of our arrangements have been turned on their head. Hitler has openly capitulated to these megalomaniacal and shifty little Lower Bavarians. I thereupon demanded in a forceful letter his public repudiation of this impertinence, in the absence of which I offered my resignation. I spoke yesterday evening with the chief on the telephone, who -- at Wessel's funeral -- \WTF{in Berchtesgaden -- weilte}, drew his attention to the seriousness of the situation, and \WTF{im...gen} that night Goering and Lippert drove to Munich, to have a final discussion with Hitler in the morning. I am very skeptical there, he will as always \?{give in}{ausweichen}, but I am now resolved to never get into a fight against him, but rather to withdraw. Then he can have his marionettes look elsewhere. Funeral in the afternoon. Ceremony at the house. Solemn and earnest. The police closed all streets. The \?{bunting}{Fahnentuch} is taken from the coffin itself. Only ten cars allowed to follow the hearse. I am only allowed to drive in front of it. So, the honor guard goes through the silent greetings of masses of people, densely packed on the sides of the streets, probably 20-30,000. Sometimes, as on Buelowplatz, opposition flares up. The Internationale is sung. At the cemetery, the KPD has painted in big white letters: "To the pimp Wessel, one last Heil Hitler!" I swallow my rage. Be calm! The cemetery overflowing. Shoulder to shoulder. Two students, Breuer and Osaf, and I speak. His song rings out: "Die Fahne hoch!" Makes you want to cry. Farewell, Horst Wessel! Outside, the rabble rages. They rage and we win. Mountains of flowers. Volkish community! The still healthy-feeling workers have recoiled with disgust from these cynical police. Afterwards there are more ambushes and police attacks outside. But otherwise everything goes well. Press trust meeting at auxiliary office. It was a funeral made up of princes all the way down to small folk. The worker gradually finds the way to us. To the Goerings' for the evening. Auwi is also there.  He is a good guy, and I very much like him with his warm naturalness. But the reaction must be driven out of them. At Goering's planned out his travel route for tomorrow. Everything depends on him. More work at night. Went to sleep tired. Sunday today. Film "der heilige Berg". I speak!

