Yesterday: Many visits in the morning. Among others, Schickedanz. He asked whether I had something against him. I came clean with him. He is personally \?{upstanding enough}{wohl anständig}. \WTF{But he has nothing to eat.} And a Baltic! No word from Munich. There the KV merrily continue to publish its appeals. Anarchy in the party. Hitler alone bears the blame, since he doesn't use his authority and decide. Even Schemm, who we were with today, complained a great deal about Munich. Schweitzer is also \WTF{powerfully loaded}. I wait and am on guard against carelessness. Newer plan: a NS funnies page, between Jugend and Simplizissimus. But sharp and audacious. I will pursue the plan further. I have a great desire for it. Worked at home in the afternoon. Evening with Schweitzer to a film. "Die Kampf um die Erde". Soviet film by Eisenstein. Well-made, but way overdone and hence awkward. Less would have been more. Other than that strong \missing \?{element}{Einschläge} "For progress and civilization!" The eternal yesterday, even when dressed up in bolshevistic garb. We cannot be fooled anymore. But nevertheless the film is dangerous, and we should learn from it. If only we had the money. I would write an NS film \WTF{that would blow it away - der sich gewaschen hat}. Argued with Schweitzer at length. After that an hour with Grete Koenig for the birthday. Very instructive, to see the party comrades at home and to hear their little troubles. Today a glorious Sunday. I have very much ahead of me. Nothing but things that make me happy. I don't worry myself any more about Munich. Goetz from Berlichingen. Stoic rest and waiting!

. Dazu starke . . . Einschläge »Für Fortschritt und Zivilisation!« Die ewig Gestrigen, auch wenn sie in bolschewistischem Gewande auftreten. Uns kann man nichts mehr vormachen. Aber trotzdem ist der Film gefährlich, und wir sollen daran lernen. Hätten wir Geld. Ich würde einen n. s. Film schreiben, der sich gewaschen hat. Lange noch mit Schweitzer disputiert. Danach eine Stunde bei Grete König zum Geburtstag. Sehr lehr­ reich, so die Parteigenossen zu Hause zu sehen und ihre kleinen Nöte zu vernehmen. Heute herrlicher Sonntag. Ich habe sehr viel vor. Aber lauter Dinge, die mich erfreuen. Ich ärgere mich nicht mehr über München. Götz von Berlichingen. Stoische Ruhe und abwarten !