Yesterday midday conference with Angriff and the branch office. The Strasser papers getting out of hand, we and the Beobachter are completely up against the wall. Result: Wilke has driven to Munich to negotiate with Hitler and Amann one last time. I don't expect anything to come of it. But I can also make a bad decision, since the whole movement is at risk. Munich, incl the chief, has lost all credit with me. I don't believe in them anymore. Hitler has broken his word to me five times. That is bitter knowledge, and from that I draw my inner conclusions. Hitler hides, makes no decisions, no longer leads, but instead lets things take their own course. I was loyal unto death. But one cannot demand of me that I let my Gau be stolen by Strasser. Waiting. Wilke will at least have clearly recognized the situation tomorrow evening. My people stand strong behind me and are staying sharp. I keep calm and hold back. In the afternoon studied newspapers at home and wrote a terrific essay against "the new course". With a demand for a soft tone (Protection of the Republic law) and clearer \?{rejection of the right}{Absage an rechts}. Distancing from the right. I mean, that must now come soon too. The DNVP can no longer use us, so away with us. We want...to stand on our own feet. In the evening Eckart celebration in the Schwechten hall. Naumannian songs from "Michael", with a string quartet, flutes and clarinets. Wonderful. Then a very beautiful string quartet from our party comrade Gunther. He should get the Beethoven prize this year. Matschuk recites Eckart. Wonderful sculpture of language. Glorious scenes from the "Lorenzaccio". A beautiful, sweet, rounded evening. \WTF{Das können wir also schon}. I have spoken about Eckart. Afterwards, ate with the artist. Good little Volk! Home late and tired. This morning the SA man Behnke died after a two years of pain from head injury. A new victim of the bloody red terror. He cleared the way for us! Outside it has become Winter again. The snow is deep. I stay home. Work, leisure!

