Yesterday midday: For the first time in the "Reich Committee". Everything that I had assumed was confirmed. A committee. Loud rubbish. One eyes the other. The only one who is above average is Hugenberg. He is in fact a clever man, and probably also a man of character. Seldte and Duesterberg politicking reserve officers and old soldiers. A Herr von Rohr and von Kleist still stick out over the dull mediocrity. An appeal will be read out which is so dumb that I dread it. Against that Epp protests my \WTF{...terung hin}. \WTF{We also decide that he will be newly edited}. I get some momentum there. Topic: coming cabinet crisis and eventual [!] red putsch. Everyone worrying about unlaid eggs. We don't take part in the discussion at all. It is too dumb. The committee live out its life as the "Freedom block". I will advise Hitler against it. A difficult hour with Frau Wessel. It is touching, and I cannot comfort her at all. I stand at Horst Wessel's casket and make the obligatory vow. The funeral us forbidden. We can only gather at the cemetery. A brutish vulgarity! In the afternoon, Reichstag. Only boring. The Young Plan and the financial reform will be dealt with behind the scenes. Is it coming to a crisis? I believe so. Red house. The caucus rather \?{agitated}{Dampf gemacht}. They had thought it important again. \WTF{To storm 5}. Wessel's storm. Pure worker. Bold, strong face. I speak only a couple minutes, and the icy silence of pain and rage reigns. That is the counterpart to the committee. Here the new Germany is born. Back home. Wrote a sharp essay against Groener and the Burogeneral. That will again stir up some sensation. It should too. Dead tired in bed. Now the dance continues.

