That was probably the most difficult day yesterday. Woke up with a dull head and then \WTF{hammer away on the job postings}{trommelten die Hiobposten auf mich ein}: Stennes \?{has not given up his affair}{gibt seine zsache nicht verloren}, the main thing he wants to fight against me. That is indeed very nice. Alarm from the Gau, chaos at der Angriff, this is a back and forth, that can cause despair. Only Frau von Dirksen remains like before, sends me oysters and is a touching kindness to me. Auwi comes and fills my head with gossip for three hours. Compared to him, his son Alexander is a true picture of manliness. Auwi always makes, without intending to, a bit of intrigue. But of a good type. He reads too much into things. The Bronnens come and are very nice to me. Olga Bronnen brings me \WTF{flowers}{einen Riesenfliederstrauß}. I work until late in the evening. Listen to the gramophone and am depressed. Magda is in Berlin and does not call. A nonsensical jealousy stirs within me. Ilse Stahl consoles me, without knowing what about. She is very reasonable. A wild night with an excruciating head. I call this morning. Not there. Then finally she calls: the man who she loved before me has \WTF{badly injured her with the ball} in her apartment. Now she is totally \WTF{gone}{dahin}. I hear in her voice that I will probably lose her. I fall into the deepest despair. I see how deeply I love Magda. It will take effort to put myself back in order. Perhaps this loss is necessary, in order to get myself completely \WTf{back into the saddle}{mich wieder...der Sache zurückzugeben}. Who knows! The paths of destiny are unfathomable. I had begun to once again believe in personal happiness. What is probably gone now.  But I don't need that either. I must and should and will remain alone. Now, when everyone has left me, I will again find my old strength. And then go into my work with doubled force. And not think about myself any longer. This poor life! And this heap of muck, called mankind!

