In the first trial 200M penalty, in the second 1500m (!). The first penalty is a perversion of the law. I hurled that into the face of the court and then refused any further explanation for the second. During the reading of the verdict I ostentatiously left the room. Outside stood masses of people who wanted to charge the building. I am cold . I am so tired, so sick, so sore. At the branch office right to work. I hope to have the Gau back in order again in 14 days. Conferences. Ede Weiss comes totally abruptly. This big child trembles and cries and stutteringly declares his submission to me. Stennes has driven these poor people into a true tragedy. It is terrible to have to witness this moral conflict. Slogging away the whole afternoon. I have even gotten der Angriff moving again. I again have some friends in at work. At home read proofs of my Danzig speech, which \WTF{is now to be published}{jetzt bei Eher herauskommen soll}. Money worries everywhere. Above all, personally. In the evening Schweitzer comes. We sit until midnight. He complains a lot about Munich. Wants more Prussian spirit. Munich is so low-energy. We have to learn from the Stennes affair. Become more Prussian, harder, thriftier, more socialistic. No compromise. Otherwise we are done for. Schweitzer stays loyal to the party as always, but he also has many critical reservations. And not unjustly. I \WTF{believe I am ready}{glaube ich gut fertig zu werden}. With Heines too? The revolt itself has been smothered. But it ferments and bubbles further. It will always return if we do not reform the party from top to bottom. I am again the buffer. If my health only returned. I am still very sick. With this infamous press agitation one must indeed nerve in the long run. Forward! \?{Don't dawdle!}{Nicht umschauen!} \WTF{Strich darunter machen!}

