The development is now inevitable: Stennes has already lost. Hitler and I have \WTF{eingeleitet} der Angriff through the press. Sharply against Stennes. Chief worked on it with me. \?{Loyalty rallies}{Treuekundgebung} in all gaus. The Beobachter brings out a big essay against St.'s split! The picture changes from hour to hour. Weissauer has begun an incomprehensible breach of trust against the movement and against me. Who knows what kind of money is behind that. I live in nervous unrest. Goering makes a move against me in the decisive hour, in order to get the aithority that the chief has given me into his hands. The chief beats...off, he does not want me to go back to Berlin and declares a \?{loyalty rally}{Vertrauenskundgebung}\missing...us in a magnificence like I have never yet see. from him. I will never forget that Goering. One despairs of humanity. He is a heap of creamy shit. Weissauer! Horrible disappointment! I only get over it with difficulty. Then, to action. I fire the traitors \WTF{daß es nur so knallt}. An appeal to the Berlin party from me, and one from the chief. Stennes crumbles. Yesterday was his defeat. Revolt finally beaten down. Yesterday evening we sat, Magda and I together with Hitler, and he colorfully recounted his experiences in the Kapp putsch. I terrific guy! Magda is very nice and good to me. I adore her so. That was a dreadful Good Friday yesterday. My critical hour. But I believe that I have overcome it. This morning Amann came back. He reports dreadful things from Der Angriff. Weissauer has lied to me and deceived me. Now it is Easter tomorrow. Outside it is pouring rain. I am now totally wounded and rundown. And dead tired. Magda is good. Only rest. Nothing more heard and nothing more seen. So that is my holiday. Keep quiet, don't think about it, go on! Joyous Easter!


Gestern abend sitzen wir, Magda und ich mit Hitler zu­ sammen, und er erzählt fabelhaft von seinen Erlebnissen im Kapp­ Putsch. Ein knorker Kerl! Magda ist sehr lieb und gut zu mir. Ich verehre sie sehr. Das war gestern ein schauriger Karfreitag. Meine