Yesterday for the first time out of her. I reach Magda on the telephone and then drive with her to a secluded cottage in Pichelsdorf. She is totally desperate, but so full of love and goodness for me, that she totally moves me. \WTF{She got dreadful things from her relatives and had endured a wild lover.} But she has stayed brave. I am rather unjust to her. But she also had to come to me, since I was sick. She breaks down in tears. This evening we will see each other again. Branch office. For the first time. Difficult trip. Everything sparkles. The SA stands at attention. So much has changed. My heart aches. Right to work. 1st conference with Hinkel. The Angriff situation is not so desperate as I had believed. We will get through it. Little \?{paring down}{Umfangverringerung}. Now I only have the editorship, and Amann/Hinkel take over the total responsibility for the business. That is fine with me. 2nd conference: Meinshausen/Drege. It will be mucked out further. I am already getting things in order. Goering has not always proven to be a friend. 3rd Lippert/Schultze. The editorship is re-established. But I have managed that already. Until Thursday. In the cafe with Schulz. He is loyal and submissive to me. \WTF{And set up the SA anew, and totally around me}{Und stellt die SA neu auf und ganz auf mich ein}. Magda comes home to me. We make up.  She is totally good and happy. Late to Clou. The people almost tear me to shreds. My popularity is only increasing. But now it tastes stale. Home late and dead tired. This morning two trials. And there I am still very sick.
