Yesterday a day of meetings: midday Schulz, then the whole district office and finally the editorial board. Cleaned up, exhorted, pointed the way everywhere. District office is now in again in our possession except for a few posts. Dr Meinshausen is doing well for himself. Editorial board: I have provisionally taken Dr von Leers for the editorship and provisionally released Krause. But took them both sharply to task. \WTF{Mal...}. Now Lippert must however must \WTF{actually be made chief}{in der Tar den Chef machen}, otherwise things will go sideways. Work in abundance. \WTF{I am again getting on well with Hinkel}{Mit Hinkel komme ich wieder Erwarten gut aus}. In the afternoon Magda comes. Something unnameable stands between us. I believe it's the other man, her former lover. She disputes that. Our clashes are getting worse. At the end I make the condition that on Sunday she does not say goodbye there, but rather is with me. She does not accept, and with that, it is out. She leaves crying. My heart is so heavy. I love her immeasurably. But I cannot trust her. So then farewell. Frightful torment! I am in total despair! But it must be! The general appeal to the Berlin SA in the Sportspalast. 4000 men with SS. Schulz hands over the SA who are loyal to Hitler. Much crying. It is a great hour. Stennes is finished. March with band playing. Berlin SA stands. The flags glow, the standards stand. I am immeasurably lucky. Now no devil will take this youth from me again. To the PO evening. 2000 functionaries. Jubilant reception. I speak briefly. About the crisis. Everything is fine. Berlin gau in order. What happens now is the affair of the organization. We will soon master that. Together with Willikens and Dr von Rinteln. Everywhere complaints about Munich. It is terrible. Tired, home sick. Today up with a heavy head. \WTF{Straight to court}{Gleich Prozess}. This evening speech in Chemnitz. Rest day Sunday morning. I am still very sick. Grief about Magda. But that must be struggled through. Either way! I now notice for the first time how very much I love this woman.
