Now the unholy mess is upon us. But I will recount it chronologically: Tuesday, call from Munich: I am to go to Hitler in Weimar. I first travel through Dresden, speak with good results in two overflowing halls, drive right from there in the night to Weimar with the car, where I arrived at 5:00 in the morning. Right to bed. No idea!
Wednesday: I meet the chief in the corridor. He is very serious. Roehm gives me information. Stannes is dismissed, he has openly rebelled, his position with respect to Munich has become untenable. Apparently the dismissal went to the press too early. Now the dance begins. There is nothing else left for me \WTF{besides the tried and tested methods}{als mich den Tatsachen zu beugen}. Telephone from Berlin: der Angriff and the extension office occupied by the SA. Weissauer is openly sympathizing with Stennes and publishes an impossible declaration from him in der Angriff. Berlin is an anthill. For me there is no longer any question: I remain true to Hitler. Even with all the criticism. I do not want a \WTF{mainline}. The movement above all. The SA must yield. Stennes will however not fit in. Good. Then there must be a struggle, and if that last a half a year. I remain with Hitler. Meanwhile Frick will collapse. Lucky enough. Schimmelmann, Meinshausen and Duerr come. Weissauer telephones \WTF{a flurry of reports}{Schauerberichte} and wants to set conditions in the name of the SA. That is now past. Weissauer plays a very ambiguous role. I order him to be fired immediately. Meinshausen gets full authority from me. Then the phone rings. The empty rumors hound us ever more dreadfully. Stennes is working: Gau and Der Angriff are occupied. Keep calm, that is all \WTF{Chamade}. I am wanted in Berlin. I don't think about it. I will drive with Hitler to Munich and there prepare my countermeasures in peace. Dalague is in Weimar. Stramm for the chief. The reports topple one upon the other. Meanwhile I speak \WTF{eine Nase lang} with Anka. \WTF{Das ist längst aus}{That is finally done with}. In Berlin Erhardt appears to work. A large-scale intrigue. We will get our SA behind us! The biggest, but perhaps also the last crisis for the party. Which we must get through. In the evening Hitler speaks. Then me. Unending jubilation! I come out for the fuehrer openly and without qualifications. Torchlight procession. Poor SA! What a \WTF{wicked}{frevles} game! Departed late. Car to Jena. The lovely Easter celebrations are there. Once again. In god's name! One is torn between his requirements for happiness. Sad drive. Hitler is sorry for me. He is thin and pale. We talk at length, but the mood is not very good. Hitler feigns courage,but he is totally broken. I sleep with him in a compartment. A heavy, weary sleep. Munich! Sunshine! In the morning the press shireks about our dangerousness. Should I participate? This betrayal to our affairs, sanctified by blood and death? Never, never! Magda has come from Berlin and awaits me in the hotel. I enjoy myself madly, but what a reunion? She is totally shaken. \WTF{Gut so!} She stands by me, faithfully and firm. I don't want to hear any more announcements. The chief is still at work. I stay in Munich. The picture is becoming more favorable for us by the hour. But what an innumerable number of nerves will it cost?
