In chronological order: on Easter Monday in a great cavalcade to Tegernsee in the country house \WTF{of the printer Mueller}. Rather relaxing. Magda is there too. She is fusses over me a great deal. I also visit Herr Amann briefly in his neighboring wigwam. He is from Berlin and tells me wild things about Weissauer's mismanagement. Though I believe that he excessively exaggerates for reasons of rivalry, but even what remains is enough to finish Weissauer. This man is one of the worst disappointments of my life. Another long chat with Mueller. Then a gray drive home in rain. Munich. Wrote and worked until 1:00 in the morning. Chief is up top. If only he always kept such a close watch! Then another hour with him in an awful cafe. Poor Hitler!
Tuesday: \WTF{Packing} the whole day. Parted with Magda. She stood loyally at my side during the difficult days: I will never forget that. With Amann to the notary. Weissauer dismissed. I am sick. Have a high fever. In the evening I speak with the chief again in the overflowing circus. \?{Wild celebrations at the end}{Ende toll gefeiert}. But that tastes so sour. Then with Amann to Berlin. \WTF{At night, wild fantasies}{Nachts tolle Phantasien}. Berlin. I must get right to bed. 40C fever. ... That now breaks everything out. Nevertheless I keep my meetings. First Amann, Hinkel, the new signatory, Schultze, the printer, and Dr Lippert. The situation at der Angriff is hopeless. Weissauer has acted link a berzerker there. That all only serves to strengthen Amann's power. He wants to hire the entire \WTF{Provinzversand} for der Angriff. Weissauer's "work". This dog writes me yet another letter in which he affirms his loyalty to me. Then Schulz, the \WTF{Femerichter}, new SA Eastern fuehrer. He is the man who sought to understand the Berlin revolt psychologically as well. So many upstanding people have gone: Hess, Muencker, Starvard, Weiss, Wagner. That is what innerly destroys me most. Munich has made so many errors, and we in Berlin bust now atone for it. Schultz perceives that all. He is very reasonable, estimates Stennes's followers at 35\% of the Berlin SA. But that is probably too grim. Schultz wants to act politically. With that my situation in Berlin would become wonderful and clear. We'll have to wait. Even I have made mistakes. I was too trusting, I believed too strongly \?{in humanity}{in den Menschen}, left over from the gray conflict a great \WTF{Protion} for skepticism and contempt for mankind. In the evening, the five district fuehrers arrive. Not one political functionary has \WTF{abgesprungen}. The party is unshaken. So I have also expected that. Difficult night. Today the fever has diminished. But so low that I can hardly speak. The shivers were too great. This morning telephone call with Hitler. I give him an extensive situational report. He is very satisfied. In Thuringia the burgers are crawling back to us. But they will tossed out. Magda calls from Severin. She is very concerned about me. I myself am around despair. That is probably the primary cause of the sickness. Head high, my boy! Now I must dictate the whole afternoon.