\header{November 11th 1932}

I received a report on the financial situation of the Berlin organization today. This is entirely hopeless. Only \WTF{???}{Ebbe}, obligations and liabilities, and on top of that, the total impossibility of somehow raising money on a large scale after this defeat. In Schöneberg we buried the SA man Reppich, who was shot during the strike. Forty thousand people sent him off. He was laid to rest like a prince. Over the cemetary circled airplanes with swastika pennants, as they wanted to give the dead the last farewell. The SA people are deeply moved. From an intermediary to the government I learned that in the cabinet they are beginning to  crack. The opposition to Papen has become very strong. We are advised to remain strong and to not enter into any kind of negotiations. This advice is superfluous, since we hadn't imagined doing otherwise for even a second. Our attacks against the KPD must now be carried forward with greater ferocity. During the strike, we were stuck with them in an uncomfortable but unavoidable \?{bond}{Tuchfühlung}. Now we must keep our distance again. It is also important that we ourselves have no illusions and that we under no circumstances stumble into a second August 13th. We must above all no longer enter into oral negotiations. \?{You can take to the bank only what you get in black and white}{Was man schwarz auf weiß besitzt, kann man getrost nach Hause tragen}. But the fuehrer is so certain in his tactics that no one needs to worry about anything. Every day, I write an essay against the cabinet. Constant drips wear away the stone. Though it is not immediately apparent that these attacks are having any results, they cannot remain completely without effect in the long run.
% a few is twenty-thirty