\header{November 15th 1932 (Kaiserhof)}

A government middle-man brings us a new little sensation: \WTF{Wilhelmstrasse is hatching their eggs}{die Wilhelmstrasse brütet ihre Windeier aus}. A fantastic plan has been drawn up, in which the goal is always in the background to trip us up. We listen in silence and imagine our part. Only it us sad what figures the Wilhelmstrasse has sought out as middlemen. ?{One cannot too frequently try to remain strong and un-embittered}{Man kann sich nicht oft genug zum Vorsatz machen, start und unerbittlich zu bleiben}. Hard situations in politics are always decides by character, not reason. I am warned about Strasser from all sides. It is claimed that he has already come to an agreement with the government. That would however be the most serious danger. Otherwise everyone is against everyone in Wilhelmstrasse. One tries to cheat he other. That is also totally natural in a dubious situation. If we operate skillfully now, then we will crown the next phase of the battle with a victory. If it doesn't happen this time, then it shall probably come to a military dictatorship. That would not be very pleasant, although it is to be expected that this experiment would only last a very short time. I gave our press a new direction: sharply against the KPD, otherwise splendid isolation. From January 1st, the "Volkische Beobachter" will appear in Berlin as a morning paper; thus is one of the most pressing inner-party questions solved. We can protect ourselves with one morning and one  evening paper. I learned from my lawyer that my trial for high treason, which has been hanging over my head for three years, is now finally being going forward. Hopefully the \?{men in robes}{Talarträger} will not come too late and I am not a minister when the court date comes around. The mood is again better, but \?{something has to happen}{es muß irgendetwas geschehen}. The decision can only fall between Hindenburg and Hitler. I laid that out in my very carefully-written essay under the title "What must happen now!". Papen will not be able to hold on much longer. The opposition in his own cabinet is too strong. Everything is in the process of resolving in Wilhelmstrasse. The SPD has also given the government a sharp refusal. The reich chancellor no longer has the possibility to negotiate with the parties. Today is \?{the day of repentance}{Bußtag}. Exactly 6 years ago to the hour I founded the party in Berlin as a young Gauleiter with three hundred people. How many successes and defeats lay in between! But we have nevertheless \WTF{stayed strong}{uns...gut gehalten}, and we will also do that in the future.
% 