\header{November 9th, 1932}

Yesterday: long session with Hitler. He is completely set on battle. No reconciliation. \?{Out!}{Drauf!} Papen must go! There is no compromise. The reaction is baffled. We don't take half-measures. Reports from Berlin: Papen wants to make concessions. Poor lunatic! To Hitler's place. He is \?{enraged with}{wütend auf} Strasser. I can see that. Strasser is always sabotaging us. Saukel arrived. Southern German states are rebelling against Papen. Caution! Only not to let Braun be roped in. Drawing up plans for the next campaign. \?{That is coming along}{Da geht's heran}. Sharpest concentration. No distractions! Cafe Heck. Herr Schnee came. And is as uplifting as ever. Hitker must still have a meeting and we discuss with Schaub. Film: "Wie sage ich's meinem Mann?" Dreadful kitsch,\WTF{in which one can only feel sorry for Maria Müller}{bei dem einen nur die Maria Müller leid tut}. With Hitler in the apartment. He philosophizes. About the \?{right of might}{das Recht des Stärkeren}. All very good and very well thought-through. A legend-worthy man! For him I would \?{let myself be drawn and quartered}{lasse ich mich vierteilen}. He reads much and knows much. An eminent head. At the end, I read aloud one of his letters from the field. Fantastic. The Hitler of today. Almkst unchanged. The first National Socialist. The Hoffmanns were also there. He is very witty. Went home late. Dead-tired. Little sleep. Greeted Litzmann at the hotel. He was very happy. \?{To Braun's house}{Zum Braunen Haus}. November 9th. \?{Day of the dead!}{Totentag!} Large rally before the standards. Major Hühnlein spoke. Gloomy. That must not happen. Spoke with Schwarz. Wilke has now also started to become a problem. And in Berlin, another new case of misappropriation. Yes, the money, the cursed money. \WTF{Imperial eagle.}{Reichsadler.} \WTF{The examiner was dealt with in advance}{Referenten vorgeknöpft}. Arranged next propaganda action. It begins the day after the truce. We will toss Papen out. Telephoned Magda. She is sweet. At noon, Hitler. Alvensleben was there. Papen in...We remain strong. If only the fat Strasser didn't commit idiocies. He is so disloyal. Reichsadler. Got everything ready. \WTF{Schwarz at Braun's house}{Braunes Haus Schwarz}. I warn about Strasser. He is of my opinion. Carlton-Diele. With Hoffmann, Schwarz and later Hitler. Discussed radio and film plans. Much delight there. Hotel. Rested some. Spoke again to Franke. Now to Berlin. I am already happy. Berlin remains Berlin.

% Arschkissen