Wilhelmstrasse's answer still has not arrived. But the fuehrer and all of us are in a peaceful and calm mood, since we are clear that a rejection is unavoidable. At three o'clock the answer arrives. It is just as we had expected: rejection! The fuehrer ends the discussion with a brief final letter. With that, the negotiations have been broken off without success. The revolution again stands before closed doors. The fuehrer's answer is strong and manly.
In order to be certain that a renewal of the August 13th affair is to be avoided under all circumstances, our Reich press chief Dr Dietrich immediately summons the Berlin press and makes the whole exchange of letters public. The brave Julius Schaub has, in his wisdom, already prepared the writing bureau with the removal of the whole material days before. He knows the operation and beats the opposition through swiftness. Thus we come to Williamstrasse an hour early and have an unbeatable head start. All documents are published, and and now the people themselves have the possibility to decide who is in the right and who is in the wrong. Now, since the negotiations are at an end, the fuehrer is holding a meating with Hugenberg. It remains without direct results. In the meantime I publish an in-depth presentation of the whole negotiations through the national socialist press. The fuehrer addresses the party in a firm and unflinching appeal. The debate is over; now the struggle begins anew. Rest and relaxation have returned to our ranks. We will certainly pass the coming test. They will soon have to come crawling back to us, since there is no other solution to this crisis.