Tuesday: Office completed in haste. All kinds of trouble as always. Money worries, personally and for the Gau. Also difficulties at the Rei.Prop. Midday on with Tonak. To Weimar. Glorious drive. Lectures on the way. Weimar: Magda awaiting me. She looks splendid. Immediately continued on. Drive through the fog. Eisenach overflowing. I spoke well. Through the fog to Apolda. Also overflowing. \WTF{Ich groß in Fahrt}. 
Weimar: Telegram from Hitler. He did not get to Berlin. Let Schleicher wait. Bravo! Comes straight to Berlin. Late to bed. Wednesday had a good rest. Press out of the house.\?{Schleicher cannot come to power}{Schleicher kann nicht zu Stuhle kommen}. Wants our acquiescence. Conditions for and against. Spoke the matter over with Hitler. Goering, Strasser and Frick came. Conference. Strasser is for cooperation. Malt otherwise black in black. Hitler sharply against him. Remains consistent. Bravo! Goering and I remain firm. Strasser gives in. Hitler correctly understood the situation. Also warned Schacht. Frick totally insignificant. Meissner's invitation to the chief \?{to come to Alten took place here}{, zum Alten zu kommen, platzt herein}. Question back over the phone: wants to discuss the matter with him. Saw through Schleicher's and Alvensleben's dark game: thus as already planned on August 13th. Resolution: Hitler will not go. Very friendly letter of refusal to Meissner. Visit also impractical. Letter was very carefully stylized. Schleicher's blow is parried. Now he becomes flakey. Goering tries to reach him by phone, to send an officer as an intermediary. He goes to it immediately. Hitler has again retained the right. Greatest confusion in Berlin. Letter to Meissner goes out. Now he even asks for everything to be kept secret. Trapped in his own sling. Only keep your nerves! The crisis waxes. Schleicher the favorite. Wildest rumors bandied about. We sit on the longer leg of the see-saw. Press howls with curiosity. Strasser also suddenly withdraws. In the evening, great company. Then with Hitler, long into the deep night...coffee. He is very nice to Magda and me. Says good things about us and Goering and Roehm. Negative about Strasser. Today, Thursday: \WTF{great press combinations}. In Berlin still no decision. Everything waits on Hitler's decision. Oberstleutnant Otte enters Schleicher's negotiator. Chief deals directly with him. Adjournment of the Reichstag until January. \?{For them, amnesty and streets free, and martial law}{Dafür Amnestie und Straße frei und Notwehrrecht}. Otherwise, struggle. In Berlin, highest confusion. Our seed bears fruit. Hitler's hour comes. If we remain firm. I am for the most ruthless attitude. No reconciliation with the reactionaries. The crisis will lift us up. Strasser is wrong. Hitler is the great, outstanding strategy. After him! Then we will be victorious.
