Yesterday: Read and chatted the whole day. Hitler is very nice. The Mutschmanns like it up here. Ley comes with a man from Cologne: Feder now with Schleicher. He will pay for that, this noble, stuck-up nincompoop. Hitler dictates his new year appeal. We go to the Moritz and play. Glorious weather. Press up in arms against "lynching" in Dresden. Awkward affair. There seems to have been a hairy stupidity again on our part. Report from home: things are not going at all well with Magda. I have so much anxiety about her. Want to depart immediately. But Maria calls later, says that it has become much better. I shudder when I think that something could have happened. Miscarriage. Magda is so brave and so good. I cannot imagine life without her at all anymore. The whole evening I am totally beaten down. Hitler talked about the Strasser case: very sharp. Mutschmann is totally perplexed. The Strassers have brought us great shame. Above all Otto, who is just a nihilist. That is in the blood. And so that makes me suspicious. Alvensleben and Papen want to speak to Hitler. Flirting? Now the battle. Today slept a long time. Hitler already dictated his address the whole morning. The voice drifts up to us. Is good. Hopefully good news from Magda.

Wir gehen in die Moritz und spie­ len. Herrliches Wetter. Presse hetzt wegen »Fememord« in Dres­ den. Peinliche Sache. Da scheinen die Unsern wieder eine haarige Dummheit gemacht zu haben. Nachricht von Hause: mit Magda steht es garnicht gut. Ich habe so Angst um sie. Will gleich abfahren. Aber Maria ruft später an, daß es viel besser geworden ist. Ich zit­tere, wenn ich daran denke, daß da etwas passieren könnte. Fehlge­burt. Magda ist so tapfer und so gut. Ohne sie kann ich mir das Leben garnicht mehr vorstellen. Den Abend über bin ich ganz nie