Yesterday: A colorful throng at the Reichstag. Wild rumors. Strasser the topic of the day. He is getting good press from the Jews. He has earned it. Conflict over the emergency order and amnesty. Depressed mood among us. I listen everywhere. \WTF{Einige Mieﬂ[!]macher}. Koch and Brueckner. But Strasser has already lost. Feder takes a leap, asks for a leave if absence with a stupid letter, which...to Hitler, goes to the press. That is what got everyone riled up. I go to Kaiserhof. Hitlet's report given. It is good. Strasser to Munich. But without any entourage. He is completely lost. I plead for the exclusion of Feder. Radio is also a Canaille. And you, Satan, lie. Schulz. Reichstag: Mood much better. Feder has drawn in the line. Before the vote, he had completely cowardly surrendered. But it will go to shit. Amnesty approved. Constitutional amendment approved. \WTF{Sozialpol}. Part of the emergency order kept. Reichstag adjourned. Kaiserhof. The rumors subside. Palace revolution failed. And so...Feder is politically dead. \WTF{O I fliegt auf.} The ballast is broken down. To Goering. Hitler first speaks before the gauleieters and inspectors, then before all members. Fantastically certain. Annihilates Strasser, and even stronger against Feder. The people howl from rage and pain. All Hitler's great success. At the conclusion, a spontaneous loyalty oath. Everyone gives Hitler the hand. Strasser is isolated. Dead man! I have fought 6 years for that. And now the fulfillment. I sit for a while with Hitler. He is totally content. Now he has also overcome Strasser on the inside. Now all that he has suffered comes out. Adieu! He goes to Breslau today. Home late. Magda somewhat sick. Slept well. Jewish press today very small. Schleicher's coup has not come off. We are no DNP and also have no Treviranus.

