A couple of \WTF{Oberschlaue} types from the Christian Union pay me a visit to negotiate the participation of their members in the new state. I got rid of them quickly. They will not be able to speak of their members any more. Amazing that everything is not put at the disposal of the new state. But caution is called for here in every regard. Those who just adorn themselves with crooked-crosses and set about among the people as \WTF{fresh-baked} party comrades. The Potsdam celebration shall be held in the National Socialist style for the first time. Radios are switched on for the whole of Germany. The nation must take part in this day. I work on the project until deep into the night in all details, call in a brief appeal to the nation to participate, and do everything to imprint this solemn act of state indelibly in the thoughts of the living generation. In the radio we now have now carried through the unification that is so essential for all cultural areas. It is exclusively in the hands of the Reich. The eternal \?{back and forth}{Zwischenschaltung} is finished; so, we are guaranteed a clear \?{path forward}{Führung}. I carry out a series of sackings, to at least clean up the personnel at the top. All important positions are filled with unobjectionable National Socialists. Now it only comes down to training them in the difficult material. I would not have thought it possible that a new ministry could make so much work. One can hardly see over the mountain of decrees. And nothing is more repugnant to me than puttering around with files. But I shall soon discover new methods of working with which I will come to a fruitful activity. 

