Kaiserhof

Before we depart from Koenigsberg, we satisfy our duty to vote in a small polling place on the way. The election monitor was astonished when the fuehrer suddenly entered his polling place, and like anyone else tossed his ballot into the urn. Beneath us the fog and rainclouds, the motors thundering their jubilant song. High above us, the sun. Wednesday at 1 o'clock we plowed through the fog and take a short glide down onto the Tempelhof airfield. All of Berlin is immersed in a sea of flags. It will be a totally huge victory. In the afternoon we all sit in the Reich Chancellery and wait tensely on the first results. The fuehrer is calm and composed as always; this time it should go off without a hitch. In the evening we listen to "Valkyrie" at the State Opera. It Wagner's captivating, beautiful music, \?{one hears from outside}{klingen von drauﬂen} the marching rhythms of the passing Stahlhelm columns, who had their big day in Berlin. Then come the first results. Victory upon victory, fantastic and incredible. As we came back to the Reich Chancellery after the performance, \?{we rang in the glorious triumph}{ist der gloriose Triumph errungen}. It is more overwhelming in its scale than ant of us had dared to hope. But what do numbers mean now? We are the lords in the Reich and in Prussia; all others are beaten into the ground. A long work is crowned with final success. Germany has awakened! Above all, Southern Germany has placed itself at the center of the whole electoral success. That is all the more pleasing, as we now have the possibility to radically bring to heel the separatists and federalists.
Berlin has \?{registered}{verzeichnen} over a million votes. Incredible numbers; we all feel drunk. Every hour brings a new, improbable surprise. The fuehrer is totally touched from joy. Outside on the Wilhelmplatz a colorful wave of tens of thousands of people calling out their well-wishes to the fuehrer. \WTF{Nun sind wir also so weit.} Now the construction of the German revolution can begin. I sink into bed, tired and delighted, at 4 o'clock in the morning. Now we have done it.

