Yesterday: Gau made brief arrangements. Installed financial control. It had to be done. Little dispute with Meinshausen, who was too weak and too petty bourgeois. To the clinic. Magda is doing better. I speak with Stoeckel, who gave me great hopes. He is very concerned with her. A fine man. And then, politics. Parted from Magda. I always dislike going away from her. On the way to Lippe with Kube. Chatted. About Strasser. Everyone against Gregor. Sits between all the chairs. In Munich Tonal sees us off. Through dirt and rain. I spoke three times: in Alverdissen, Luedenhausen and Almena. All overflowing. Only farmers and smallfolk. But that is very nice. and most were very convinced. Again amongst the people. Rest in Bielefeld. Left in the night. Great company. Hitler with the whole staff, Kube and all the people. Hitler reports to me. Papen sharply against Scheicher. Wants him out and totally sidelined. Still has the ear of the Alten. Also loves by him. Prepared the arrangement with us. Either the chancellorship or the \WTF{Ministerien der Macht}, defense and interior. \.{We'll see}{Dies läßt sich hören}. Schleicher does not have a dissolution order. Going downhill. Very suspicious. Now very dependent upon Lippe. So much work. Hitler is very nice and so concerned about Magda. A real friend! Today he will give me more news. We all sleep. Only two hours left. Berlin: straight to bed. Exhausted. More discussion with Hitler. Then clinic with Magda. Fever sank to 36.5. Thank god! To Lippe again in the afternoon. Now I stay until Sunday. And then the success must follow.

