Yesterday: Weimar trip. Everyone enthusiastic about Lippe. Kube is there. Bureau comrades. Gauleiter day. Ley gives a talk on the Strasser case. They are shaken. Then discussion. Frightful accusations against Gregor. His best friends have abandoned him. Mutschmann calls him a Jew. Judas would be better. Lohse, Brueckner, all anti. Kube is set. He will remain with us. I trust him...with Hitler: Prussian question will be decided today. Strasser is excluded as soon as he gets cheeky. Otherwise dilatory. Hitler is determined on everything. Hitler speaks before the Gauleiters. Three hours. The basics. Rigid intransigence. So that is correct. No compromise. And then the drawn-out Strasser affair, the old details. The peoples' eyes are opened. \WTF{Feder bekommt auch sein Fett}. At the end everyone was agitated. Hitler has won a full victory. The Strasser affair is through. \WTF{Knif[!]}. Poor Gregor! His best friends will slaughter him. I prepare a big propaganda action with Muchow and Haegert. Farmers and workers. Back to Berlin. Our people behave like...peasants. Impossible line. With...Freyberg. Clever man. Has his money troubles. Berlin: straight to the clinic. Magda already asleep. The sweet thing! I still chatted with her. Press at home. Everyone is deserting Strasser. No more \?{inquiries}{Nachfrage}. Thus I am rid of this bad penny. He will end as a nobody, just as he deserves. Today slept in. Afterwards Hitler came. Today Harzburger Front discussions. Winter outside. Things are doing well for us again.
