Yesterday: work at home. Essay: "Finally a clean slate". Clinic. Magda very good and cheerful and kind. Thank god. Kaiserhof: Goering reports that everything is perfect: Hitler chancellor, Papen vice, Frick Reich interior, Goering Prussian interior, Hugenberg...etc. I still decline, to carry out the electoral battle. Reichstag to be dissolved. The last time. We are going to do it. Hitler to the old man today. Still don't dare to believe it. Is Papen trustworthy? Who knows? I go straight home. Hitler calls me right back: in Frick's presence solemnly explained that my ministry was secure, only with a front man as a placeholder for now. That is good enough for me. So, to the election! \WTF{Wol­len zum Reittournier}. Hitler cancelled at the last moment. Good. Then Alvensleben comes with wild tales. Hindenburg will today imstall a Papen-Minderheit cabinet. Reichswehr will not be pleased. Hindenburg is blind and unfit. His son is to be arrested in the morning. Still tonight a telegram to the...Hindenburg transported to Neudeck. Today at 10:45...So, coup d'etat. Threat, serious, childishness? I immediately inform Hitler and Goering, who was waiting in the next room. Goering immediately notified Meissner and Papen. Who the... . Goering handles the affair without fantasy, does not bring Papen around, otherwise we would have made the break here. We consider at length. Hitler in a great trip. Helldorff appointed. He makes arrangements with Pol.Maj. \WTF{Wecke}. But I don't believe that Schleicher has the courage. \WTF{Hammerstein schon.} \?{Who had also telephoned Hitler}{Auch der hat am Te­ lephon vor Hitler gedreht}. So we wait. We sat until 5:00. It didn't happen. Now it is 11:00. Chief goes right to the old man. Is the great hour actually upon us? I still dare not believe it.
