Monday: \WTF{Kr.Leiter} and editorial staff \WTF{aufgewienert}. Electoral campaign huge in preparation. Only money is missing. Hitler in Munich. I hold many conferences. Am very tired and exhausted. Landtag dissolved. Braun finally dismissed. So that is good. The jews are quiet. The wave of terror recedes further. Laying in bed. In the evening spoke before the functionaries in the overflowing tennis hall. Last reserves of energy are running out. Then out. Flu. Keeled over. In bed. 39C fever. Hard night. Tuesday: \?{hallucinated}{phantasiert} the whole day. Conference towards evening. Which agitated me very much and the fever climbed to 40C. Hitler called. Had already spoken \WTF{with Funk} "because of my ministry"...demoralizing. So I am very curt. The sickness lets me overcome all these trivialities. Magda is sweet. Little Helga is also getting the flu. Wednesday: laid down \WTF{delerious} the whole day. Wild hallucinations. Now Magda is getting the flu too. A sickhouse. I work with the men as much as I can. But only annoyances. No money for the campaign. \WTF{Satiresturm der...}. How small that all looks from the sickbed. Weary and painful night. I live through bitter hours. I feel abandoned by everything.
Thursday: I must immediately relieve Kubisch, since he has shamed me with \WTF{black rides} with dubious girls.  Also, he is sexually ill. \WTF{Ein Blender!} I don't like it. But it can't go otherwise. I fell better and am already working again. But Magda s very sick. What beautiful weeks! So thus begins the Third Reich for me. The men sit with me for an hour and give council. No money for the campaign there. \WTF{No Blacks trouble themselves about that}. The Goerings reign. Out of bed. I must get to work...and then dictate from bed into the night. Hitler calls [!] Very kind! The crown prince writes a friendly letter. \WTF{Ein Anschmeiﬂer!} Nauseating!
Friday:  Dictated signs since midday. Worked. \?{In the saddle again}{Wieder im Geschirr}. Just stood up for the first time. Still very worn out. Magda still in bed. Conference for the Gau and Reich Prop Division. This evening stadium. Hitler on all German transmitters. Totally huge event. Beforehand I did a half hour's reportage. And then tomorrow the great work shall begin again.

