Kaiserhof

I have an exchange of letters with General Music Director Dr Furtwaengler about the principles of forming German art. His appearance excites some sensation. I attempt, in my reply to Furtwaengler, to lay out the essence of the national art concept. Up to now we had never thought it possible that we would think about it at all. The agitation of the Jewish press still continues. They see us as good politicians, but bad friends of art. The future will prove how fundamentally they have erred there. I receive the deputies of the Christian unions who, in clumsy confidence \WTF{ask for good weather} and promise in return that their members will march with us on May 1st. Harmless naive children! As if we had to rely in the Christian unions for our appeal to the German Volk. They still seem to have no conception of what has actually happened. Not six months \WTF{Nicht ein halbes Hahr wird mehr ins Land gehen}, and they are completely booted out and without influence. So this is what has been governing Germany for 14 long years! It is almost Easter already.
Goering named Prussian Minister-President. With this, a clearer and sharper national-socialist course for this largest state is guaranteed. Epp named as first Reichsstatthalter in Bavaria. Now further appointments will follow one by one. One \?{leadership role}{Spitze} after another will go to our people. Last year we were in the middle of the heaviest struggles to maintain our party's position. Who would have predicted then that in a year we would have already be in power.