Yesterday: Bureau in the afternoon. Conferences. Haas, the foreign policy diplomat. Does not make a pleasant impression. A squirrelly windbag. Frau Moesmer from the RWM. Recounts a wild slanderous story about me. One must have thick skin. I should write mottos. Garbage! But RWM. Yes, Schleicher! Advises against Buelowplatz. \?{Great state action}{Ganz groﬂe Staatsaktion}. Schleicher wants to ban it. But RW remains firm. KPD demonstrations totally forbidden. We do not give in. Jewish press agitates for a ban, but the police remain strong. Thus today comes down to a test of strength. Work, annoyances. Hitler should not go there. Foolish cowardice. Must, must! Even he himself explains that he never even imagined staying away. Clinic: Magda stood up for the first time. What a joy! She is too sweet. Kaiserhof. Chatted with Hitler. Strasser was with Goering. \?{Very little news}{Gana klein beigegeben}. So that is good. Tuesday with Hitler in Munich. He must lay low for two years. We will no longer get power, he has nothing left in his future. The agrarians want Hindenburg. He should take Hitler. Frau von Dirksen works forcefully. I don't believe in the results. \WTF{Man will parlam}. Solution. But I think that we must fight once again. Corrected Hitler's speech with him for a long time. Discussed Gauleiter questions. Count Solms must soon take over Hessen. I will have Brandenburg from Schlange. So that will also come. Later ate with Dr Wagener and wife at Hitler's. Chief does not feel well at all. He sleeps and eats too little. Home early. Still working until 3 in the morning. Slept in. Today spent entirely on Horst Wessel. Police with machine guns and tanks. \?{That was splendid}{Das gibt tollen Zauber}. KPD will suffer a heavy loss of prestige. Shame that we still don't have the police. Otherwose today the KPD would have suffered....with their... Hitler is in Frankfurt etc. He is expected at the Friedhof at 2:00. Everything is again in motion. Schleicher is doing very poorly. When will he fall?


