\entry{January 3rd 1934}

Yesterday, \?{wide awake in the morning}{morgens ausgeschafen}. Ate at Braun's house. Large group...is very nice. Strong moods against Goering. Visit with Esser. Radio, press, tourism. He waffles a lot. Everywhere anxiety about the Reichsreform. Also at Siebert's. He spoke of the Lutze case. A corruption affair, in which even Darre is not entirely clean. Siebert is a painfully rigid official. Good finance man.  Wagner, who I then visited, is in full force. But nothing behind him. With Epp: who has become old, only somewhat senile. But charm and style. He is delightful. I stayed with him for tea. Totally in the clutches of the Blacks, who work ingeniously. With Hitler for coffee [!]. He is touchingly nice to me. At Mercedes, new Rennwagens on display. A marvelous piece of work. First class! German theater is crap, but Grock had made us laugh for an hour. A comic genius. \?{Er kommt in der Pause}{He came by in the break}. Also, still yet a child! Food at Osteria. And then home. Laid awake a long time. Overslept this morning. At Heidi Braun's haus. Hess met with the Reichleitern. Small questions, particularly about the danger of the clerics. I let loose a storm. Then the regional inspector. Totally small...boring crap. A also touched on the woman question. "The German woman does not smoke." Bloody nonsense and quackery! With Hitler. Hoffmann's wedding with Erna Groepke. Very nice. Frau Raubal. Now hotel. With fresh questions to the Rei.Prop.Leitung. Darre spills idiocy upon idiocy. A dud. Now still much work. French memorandum unacceptable in its proposals, if still nice in form. A whole mountain. This evening back with Hitler.