\entry{July 1st 1934}

Friday: Call from Essen to go immediately to Godesberg. So it goes. Still brief work in Berlin. Then back. Hangelar. Received by Grohe. It had to be done. Fuehrer comes at 4:00. He is very earnest. Gives me a quite extensive report: Saturday, he handled it. Against Roehm and his rebellion. With blood. Should know that mutiny will cost your head. I agree. \?{Reckless}{Wenn schon, dann rücksichtlos}. Proof that Roehm conspired with Francois-Poncet, Schleicher and Strasser. So, action! The fuehrer is very calm after his decision. We spend the day is negotiations. \?{No one can remember anything}{Keiner darf etwas merken}. Conversation with Lutze, the new chief of staff. He is good. \WTF{Zapfenstreich des AD}. Fuehrer tense, but totally solid. Silence between us. Telephone from Berlin: the rebels are arming. So, no time to lose. Magda went with the children from Cladow to Berlin. Police protection. Then, Hangelar-Munich flight. Arrival at 4:00 in the morning. Serious situation. Saturday: right after arrival, ministry of the interior. Wagner rejoined Schneidhuber and Schmid. The fuehrer demoted them himself. Then off to Wiessee. Chronology: Wiessee arrest. Leadership very brave. Chief brilliant. Heines missrable. With a catamite. Roehm keeps up his attitude. Everything smooth-going. Back to Munich. On the way, SA Fuehrer. \?{Inside Munich}{München Innen}. Alarming reports. But everything calm. Fuehrer with Killinger. Went smoothly. Speech before the SA fuehrers. \missing Colorful impression. Some food. Then, appeal to the people. Not a minute of sleep. From Berlin: Strasser dead, Schleicher dead, Bose dead, Clausener dead. In Munich, 7 SA leaders shot. Among them Ernst, who died in Berlin. Criminal court. \missing