\entry{January 2nd 1934}

Yesterday: received the Reich president. Outside masses of people. I walked on the steps before the whole diplomatic corps and had to greet them all individually. The Austrians stuttered a few phrases about peace etc. I was completely cool. Above, festive reception. The old gentleman is fresh. \?{He powerfully struck Hitler}{Er streicht Hitler mächtig heraus}. He spoke particularly kind words to me. I should not take my health for granted and not overdo it with work. Very nice of him. The reception had dignity and style. \?{Congratulations}{Gratulationsarbeit} at home. Magda greeted me in a negligé. About that there was a frightful racket. She berated me fearsomely and intolerably. That was it. I don't take part anymore, don't go to Hitler until she gives in and sees that she was wrong. One must be rather lenient with her. In this circumstance, she deserves it. We made up, then to Munich. Parted at the station. Great crowd of people. In the train, Chief Roehm and I discussed the foreign political situation. Francois-Poncet was with him in the afternoon. Presented his aide-memoire. Gracious in form, but in substance rather uncompromising. \?{Now nerves are flaring}{Jetzt Nerven be­halten. Und drauf ankommen lassen.} And be ready for the worst. Hitler sees perfectly clearly. He is a logical thinker. I have a little rivalry with Hess. He acts like an unbearable type of schoolmaster. 
Munich. Chief has sent me a very warm letter for the new year, in which he ascribed to me the conquest of Berlin and all of the service of NS propaganda. I am very happy about that. Besides that, got letters from Hess, Amann, Roehm, Schwarz, Himmler and Rosenberg. They are in the press this morning. And Goering? Not a word from him. Out with him! Breakfast at the Braun house. All kinds of questions. Read Hamsun. Unsurpassable. And then sleep. I did not get a wink of sleep on the train.