Wednesday: everything revolves around the politics abroad. Funk to Stuttgart to give a report to the fuehrer. I have a whole list of worries. Long debate over Pygmalion, Rab\missing and Jews in film. I \missing up. Short chat at home. Everyone is already working on the move. On Monday it is to start with the new construction. Tea at the ministry. Talked Tschammer-Osten. Olympiad. A tense atmosphere. Cerutti acts as if it was nothing. Me too. I am grilled by foreign journalists for hours. Goering backs me up, and so we slog our way through the prickly questions. I assert myself well. In the evening a little drive. Film behind Staaken. Very lovely. At home some chatting. Then dead tired in bed.
Thursday: protest notes from Paris and Rome. We know from experience that they will protest what is achieved. Flandin's provocative speech against Germany. Rekindling the war-guilt lies. Incomprehensible. \WTF{The rage of the cheated tanners}. They will complain that we are re-arming. Funk reports briefly on a visit with the fuehrer. Then I fly off to Wiesbaden. But I have a bad cold and hence totally unsociable. Wiesbaden at 2:00. Glorious Spring. The fuehrer already waiting for me. Discussion about foreign politics. He is totally calm. Ribbentrop has turned him somewhat against the English. visit. Guileless characteristic of Simon. I check that. Otherwise Paris and London shall protest. We negotiate and nothing comes of it. Sunday the English visitors arrive. The fuehrer must apply all conversational arts. There I trust totally trust his magical power. Wiesenbad inspection...Somewhat overloaded. But warm and comfortable. Still always better than the modern only-utilitarian buildings. Drive to Neuberg. Early Summer! Glorious sun! And me with my nauseating cold, which has absolutely handicapped me. Hour of sleep in the hotel. Then a concert in the Kurhaus. Beethoven and Wagner. Very lovely. Only in Germany is there such an orchestra in the provinces! Afterwards a long talk with the fuehrer. \WTF{Er läßt sich von mir eingehende Charakteristik Simons ge­ben.} During which I noted his impartiality, which Ra\missing such \missing. Afterwards chat about all possibilities. I have to go to bed. High fever. Sweat cure. And then deep sleep. This morning I am completely \WTf{under it}{herunter}. Afternoon flight to Hannover and \missing. God knows how I am to endure that!