Tuesday: fixed on the work. Election work, which has a claim on much time. Glorious signs. Up to today everything has gone well. Arranged the last two days before the vote. It is totally huge. Midday with the fuehrer. He is still enthused from Frankfurt. Discussed electoral questions. Also light relaxation in London. Fuehrer told me of the measures taken so far. Then Neurath comes with a telegram from London: Eden has promised that the English government is doing everything it can to discuss the German proposals. Further invitation to come. Which can no longer be evaded. Ribbentrop is also to fly. All good wished with him. True we are morally condemned, but practically there must be another decision. And then a longer peace shall dawn. We could then no longer provide \WTF{a fait d'accompli}{Neue fertige Tatsachen}. The Reich is free and sovereign. 
Afternoon home and much work. With the children in the garden. Spring is here. Done at 7 in the evening. 6 meetings. Pharus hall, Pankow, Friedenshain, Neue Welt, Bock brewery and Sportspalast. Everywhere an indescribable mood. Tens of thousands of people on the streets. We must win this election. Touching signs of the love and devotion of the people. That is so good. Wistful recollections. Dead tired at midnight at home. Still working on the signs. The fuehrer calls me and is glad of my success. Fell into bed.
Wednesday: early to work. Campaign, campaign. Propaganda office. \?{Quarreled with}{herumgezankt} Dr von Leers. He did not make a good impression. Jack of all trades. And so puffed up. I have some good press from the night before. New Chinese ambassador. A young, sympathetic person. But rather colorless. Worked. Afternoon flight to Leipzig. Had it out with Mutschmann. Worked. Good impression from Ribbentrop's dispatch in London. Paris peeved. The crisis has relaxed significantly. Hopefully it stops. 
The fuehrer speaks in Koenigsberg. I, in the evening, in Leipzig. Mess hall. A huge overflow. To the 100000 people on their feet. The masses are in a great mood. I speak in absolutely top form. The streams of applause ring through the hall for minutes at a time. At the end I am happy and tired. Ate together for a long time with the Saxon \WTF{Pgn.}. Von Eberstein told me about the Peoples' Court. Much still must be changed there. In bed and slept in today. In London Eden has indeed \WTF{arranged} the German \WTF{Vertragsbruch}, but serious measures are not necessary. A further relaxation of tensions. Ribbentrop speaks today. He will defend our standpoint. Glorious Spring outside. The people uninterruptedly call out to me from the hotel. Right to the airplane to Breslau.