Friday: slept in. Right to work. Three years in office. Many flowers and well-wishes. A singular feeling, to administer a ministry for so long. I have worked much and learned much. Very unpleasant reports from London: there the situation has deteriorated. Full-scale attack on our nerves. But it must be withstood. The fuehrer remains firm. Hoesch lost his head and caused a panic in London. The three military attaches have all been infected by him. But the fuehrer remains firm. He also rejects every gesture. His offer is clear. \WTF{Er läßt sich auf keine Winkel­züge mehr ein.}  When the others want to provoke conflict with violence, they no longer have a weak government to work with. The fuehrer is remarkable. Goering firmly supports, even Neurath and Ribbentrop remain strong, but the military and diplomats fail. Above all the AA and London. A true barrage of rumors comes down on us. But that is useless now. I get a new crash every half hour. But I don't make a sound [!]. Midday with Kaufmann for lunch.  Joked, played with the children, talked. Diversion. Then to the hotel and nice coffee. Lectures, work on the electoral campaign until the fog recedes. Evening, car to Kiel. In Neumuenster the whole city was out on the streets. Unending jubilation. On to Kiel. Brief visit with Lohse. Then an overflowing assembly. I am not in good form. \WTF{The whole time the faint-hearted are passing by me.} A frightful atmosphere reigns. But I still push through it. After the assembly I was suddenly seized by disquiet. In the plane and back to Berlin. Arrival at 2:00 at night. Panic in the press as well. I put the brakes on that immediately. I will help these \WTF{Mießmachern}[!]. At 5:00 at night everything is again in balance. And I go happily to sleep for a few hours. Saturday: bureau work. With the fuehrer. He is steely calm. Attolico was with me; Italy will no longer take part in financial, nor economic nor moralistic sanctions. The atmosphere is clearing. The English and French press are starting to give in. Thus as suspected the day before everything was whipping up emotions and panic. The fuehrer recounts the whole day to me. He has not wavered for one moment. But he looks completely pale. You have to love him. Ward Price was with him and demanded a gesture, symbolic \WTF{Räumung} and similar rubbish. All refused point blank. And now they are giving in over there. I discuss the electoral campaign with the fuehrer. Up to now everything [!] going well. Only the press is here and there being unfaithful. Will keep a look out. Hitler wants to send Pfeffer to Anhalt as governor. Good decision. Will speak witn Amann because of the purchase of our house in Cladow. And then improve my \WTF{salary}. Then we can again breath freely. And Magda again sees clearly. We have so many other worries that we couldn't bear another such money worry. That robs us of time and the ability to work. The other is cheaper. Stoeckel is 65 years old. I give him another 3 years service with the fuehrer. Prepared a big reception of the Rheinisch \WTF{Stände} for March 24th. Fuehrer flies to Munich. All my good wishes go with him. In the ministry for work. Propaganda committee meets. Everything goes in order. Good posters, special editions, fliers. I work through a mountain of decrees. Work at home. Magda enjoys herself like a child about our increase in salary. In the evening comes the report: Germany invited to London. On Monday. Air cleared. Now to keep our nerve. And smash the defeatists. I am completely happy. Played with the children. They are so sweet. And worked with relish. In the evening to the destruction of the film "An impossible woman", with Dorothea Wieck. Good discussion. "Paul and Pauline", with Lommel. Rubbish. Not worth talking about. Early to bed and slept well. Today I speak in Potsdam.
"

