Friday: Expected in Breslau. Jubilant send-off in Leipzig. Ribbentrop's speech in London. \WTF{Gutt [!]} and hard-hitting. Plane to Breslau. Stormy reception. The whole city on their feet. Flags upon flags! I also converse at length with party comrade Prof Raabe there. Overflowing rally in the evening. I speak in top form. Stormy ovation. In London we have been so to say \WTF{roundly rejected}{einstimmig verknackt}. That was to be expected. What comes next is decisive. Plane back to Berlin. Arrival at 12 midnight. Worked with Hanke until 2:00. And then I drop. Short sleep.
Friday: brief sleep. Right to work. A glorious spring! \WTF{Funk krank.} Mountains of work piled up. Right to it. Long conversation about the election. Everything has gone well up to now. Our people work like horses. Tug-of-war in London. Ribbentrop works well. But still no results and little oversight. We are still far from the goal. Midday, fuehrer. He is optimistic. It will go well. One must now have some patience and prepare oneself with strength. Hess and Neurath also there. I am so tired from the campaign. And such glorious weather outside. Afternoon I work at home. Fuehrer to Hamburg. I fall asleep from weariness. In the evening, "Rheingold". Reception and food for the 400 oldest workers in Berlin. That brings joy and is very satisfying. It is a wonderful evening. The people enjoy themselves very much and are very warm and friendly to me. I give a short speech, then eating, toasts, dancing and humorous skits. Until 12 at night. A wonderful celebration! I go through the lukewarm evening with Lippert and Duerr. Memorandum of the Locarno powers: Germany shall recognize a judgment from the Hague and allow allied troops in a 20km zone [!]. They have become quite mad. Antzmann has given flat commentary to the press. At Neurath's request. We could still stop that. Fuehrer refuses the demands in a Hamburg speech. That would be giving up. So that cannot happen. Only on the grounds of equal treatment. Otherwise not.  But one must remain firm and be careful that the others don't become weak. To bed late at night. Dead tired. Today glorious Saturday. 

