\entry{June 5th 1938}

Yesterday: the weather has become better. The fuehrer has departed for Obersalzberg. Three whole days vacation! Still, some work. I whipped up the Prague question once more in the press...we publicly arm ourselves with everything...\?{against the possibility of a Nationality issue here}{dagegen, daß hier ein Nationalitätenrecht vorliege}. The Czechs only say that to deceive the world.  New incidents in Sudeten Germany. A number of conference days in the summer. From vacation, no speeches can be given. Now the broadcast report times, which have been changed against my will, have again been set for the 20th and 22nd, as before. I agreed and prohibited any further change in the future. An Oberschlauberger has found out that Johan Strauss is an eighth Jewish. I forbade that coming out into the public. Since, first, it is not yet proven, and second, I have no desire to let the entire cultural heritage be by and by so worn down. In the end, all that remains of our history is Widukind, Heinrich der Lowe and Rosenberg. That is a bit paltry. Mussolini proceeds here very shrewdly. He occupies in himself the whole history of Rome, beginning from earliest antiquity. By comparison, we are parvenus. I do what I can in that regard. That is also the will of the fuehrer. The law about degenerate are is now published in the legal gazette. Now it goes to work. This question must be resolved and closed as quickly as possible. In the afternoon spoke at length with Harald. He is already an upright big youth, very nice and very intelligent. His father has remarried. Old buck! Press still full the Czech business. Now the Slovaks are also making noises under Father Hlinka. That is very good. Prague expresses its regret to the German protest. In the afternoon, guests: Ello, Hoehn, the Helldorffs and Arents. We took a boat ride to Funk's. We are living very well in Potsdam. I riled Funk up, saying that Germany should no longer pay Dawes and Youngzinsen. He was very attuned to my argument. In the evening yet more long discussion. Today Pentecost, the lovely feast.