Yesterday: long sleep. Outside Winter again, snow, cold. Midday inspected the preparations for the reception of the fuehrer. Everything is perfectly laid out. The audience in a perfectly fantastic mood. Dictated essay "One-on-one with the democracies". A sharp break with the English and their hypocrisy. I believe that will land a blow. Discussion with the three production chiefs of our film firm. I develop my ideas for a new direction in film. Above all, care for the human resources. The discussion is very fruitful and I believe it will have good results. Still all kinds of work. Outside on the Wilhelmplatz the audience is already gathered in the snow and cold. At 19:00 in the evening, to Goerlitzer station. All of Berlin on their feet despite the wild weather. Goering has already \WTF{divvied up} Slovakia. He is magnificent. We must at least have a monetary union with them....protectorate? I think not. The fuehrer enters. It is indescribable. We are all deeply moved. Goering speaks. With tears in the eyes. Then entry to Berlin. That all is grandiose and still never \WTF{dagewesen}. Millions on their feet. Light, spotlights, fireworks. And on top of this masses of people as far as the eye can see. Wilhelmplatz overflowing. From the balcony, an enchanting image. The fuehrer speaks. His trip to Prague was a right \missing. At the castle district there were literally no people when he arrived. The population of Prague has acted completely neutral. One can hardly demand more at the moment. The fuehrer justifiably doesn't take the protests in Paris and London seriously at all. That is only a false alarm. Daladier has gotten his authority. He will use it to intensify the rearmament. Chamberlain has probably also \missing. The posture has stiffened somewhat in Paris and above all in London over the course of Sunday. But that is all just theater. We must be calm and need \missing nothing to us. That is at the moment the best medicine. I again discuss the question of an SA newspaper with Amann and Lutze. We will now come to the edge there as well. \WTF{With Ley the question of the 8th chamber is perfect.} And then I go to sleep. I am so tired. Today again comes another difficult day of action. One must be on guard.

Ganz Berlin trotz des tollen Wetters auf den Beinen. Göring teilt schon die Slowakei auf. Er ist prachtvoll. Wir müssen mindestens Wäh­rungsunion mit ihr haben . . . . Protektorat ? Ich glaube nein . Führer trifft ein. Es ist unbeschreiblich. Wir sind alle aufs Tiefste ergriffen. Göring spricht. Mit Tränen in den Augen. Dann Einfahrt nach Ber­ lin. Das alles ist grandios und noch nie dagewesen. Millionen auf den Beinen. Licht, Scheinwerfer, Feuerwerk. Und dazu diese un­ übersehbaren Menschenmassen. Wilhelmplatz überfüllt. Vom Bal­ kon aus ein bezauberndes Bild. Der Führer erzählt. Seine Fahrt nach Prag war ein richtiger . . . . Auf dem Hradschin war buchstäb­ lich kein Mensch, als er ankam. Die Prager Bevölkerung hat sich ganz neutral verhalten. Mehr kann man ja auch im Augenblick kaum verlangen. Der Führer nimmt die Proteste in Paris und Lon­ don mit Recht garnicht ernst. Das ist nur blinder Alarm. Daladier hat seine Vollmachten bekommen. Er wird sie zu intensiverer Auf­ rüstung benutzen . Chamberlain hat wohl auch . . . vor. Die Haltung