Day before yesterday: long struggle over the cabaret. \?{I press Schaeffer to the right}{Ich stauche Schäffers zurecht}. He whines to me. But I stick to my standpoint. \WTf{Political humor is eradicated}. Indeed, root and branch. Hanke introduced as president of the advertising council. I talk briefly about it. Cleansing of the advertising council. A very extensive and profitable undertaking. Lunch with the fuehrer. The fuehrer now speaks almost entirely about foreign policy. He is always mulling over new plans. A Napoleanic nature! Talked through the question of the book proofs with Bouhler. We are almost suffocating here in the upper organization. Bouhler is doing there as well \WTF{rather too much of the good}.  He must fundamentally dismantle his apparatus and restrict himself to the examination of the pure NS literature. But there as well he comes into conflict with Rosenberg. In the afternoon work. In the evening supper with the fuehrer. Discussed our new house with prof Baumgarten. And some plans for building the theater, above all that in Linz. \?{That is the main thing for the fuehrer}{Den macht in der Hauptsache der Fuehrer}. He is very much interested in theater questions. That is one of his passions. To the riding and auto event. The fuehrer is celebrated. Lively jumping events. And then very lovely \WTF{Schaubilder}. Until well after midnight. The fuehrer drives to the mountain, I to Schwanenburger. Chatted a long time with Magda. Helga is now going to school. The sweet little thing!
Yesterday: slept in some. To Berlin. Discussed reconstruction plans for Lanke with Hanke. Which \WTF{is now coming together well}{bekommen jetzt Hand und Fuss}.  Decree about the cabaret signed. Now that is also ready. It will make a tempest in a teapot. Midday and afternoon work. Roosevelt has given an impudent speech. Now according to him America's borders are in France as well. But he is mistaken if he believes that it will go again as it did in the world war. This time [!] are more prepared. Militarily and also spiritually. Examined films. "Effi Briest". Gruendgen's direction with Hoppe, Diehl, Hartmann. A very moody film, sober and outstandingly well-made, full of wistful nostalgia and restraint. I am very happy with it. In the evening some more chatting. Then tired to bed.