\letter{613}
\rcpt{Weisskopf}
\date{December 6, 1940}
\location{Princeton}

Dear Herr Weisskopf!

Thanks for your letter. I don't know what will happen in April, perhaps I shall be called somewhere else and hence it would be better if you came at the end of January. (You shouldn't take the article on nuclear forces too seriously -- \?{why say at the moment, "but say, you are so beautiful"? And even less delivery dates}.) Also: please, think it over again.

Two days ago I saw Rabi at that remarkable museum in Philadelphia called the Benjamin Franklin Institute, and about that not much more can be said than that it is over 100 years old. I had a very informative conversation with him about the MIT problem, national defense, physics; but it is preferable to discuss this with you face to face. However, I would like to report to you one bit of wickedness from Rabi (please spread!): He said: "Bohr is the Stalin of physics and Einstein isthe Trotsky!" (The former alludes to certain despotic characteristics in Bohr, the latter naturally to Einstein's stance toward modern physics.)

Now the spiral orbit in the Coulomb field: these were, at least for attraction, extensively studied by Sommerfeld (c.f. the paper Annalen der Physic 51, \textbf{1}, 1916, specifically p. 49, ยง3; further the earlier editions of Atombau und Spektrallinien.) The \?{limit momentum} $p_0 = \mathbf{Z}e^2/c$ plays a great role here; namely, he has long tried to quantize the angular momentum according to $p_\varphi = p_0 + kh/2\pi$ (instead of $p_\varphi = kh/2\pi$), which naturally leads to nonsense. \?{Perhaps you can check this with Sommerfeld}. -- \?{Did} you know that there is a certain analog to the spiral orbit in the Dirac theory when $Ze^2/\hbar c \gg 1$?

Then, instead of the $K$-shell, there is a continuous eigenvalue spectrum! \?{Check out the formulae some time}!

With the positron theory, it seems a bit as if I am to jump into cold water. But when you're in it, it's even quite pleasant. I have just jumped into the concept. (Incidentally Rabi has also strongly advocated for it!) When you come at the end of January, I hope to already know much about it and it would be a great help to me to be able to be able to discuss it with you extenstively and continuously! (Eisenbud has held a very good presentation on the work of Wentzel.) By the way: The Ithacians haven't sent me any check. I had understood from you that they would also do so (not only Rochester).

So, hopefully we will see eachother at the end of January. Many greetings to you and your wife from Franca and your old

W. Pauli

I will be at the Philadelphia meeting. Max Delbr\"uck wrote that he also would resp. should come.

% spirakHaemster