\documentclass{article}
\usepackage[utf8]{inputenc}
\renewcommand*\rmdefault{ppl}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{marginnote}
\newcommand{\nf}[2]{
\newcommand{#1}[1]{#2}
}
\newcommand{\nff}[2]{
\newcommand{#1}[2]{#2}
}
\newcommand{\rf}[2]{
\renewcommand{#1}[1]{#2}
}
\newcommand{\rff}[2]{
\renewcommand{#1}[2]{#2}
}

\newcommand{\nc}[2]{
  \newcommand{#1}{#2}
}
\newcommand{\rc}[2]{
  \renewcommand{#1}{#2}
}

\nff{\WTF}{#1 (\textit{#2})}

\nf{\translator}{\footnote{\textbf{Translator note:}#1}}
\nc{\sic}{{}^\text{(\textit{sic})}}

\newcommand{\nequ}[2]{
\begin{align*}
#1
\tag{#2}
\end{align*}
}

\newcommand{\uequ}[1]{
\begin{align*}
#1
\end{align*}
}

\nf{\sskip}{...\{#1\}...}
\nff{\iffy}{#2}
\nf{\?}{#1}
\nf{\tags}{#1}

\nf{\limX}{\underset{#1}{\lim}}
\newcommand{\sumXY}[2]{\underset{#1}{\overset{#2}{\sum}}}
\newcommand{\sumX}[1]{\underset{#1}{\sum}}
%\newcommand{\intXY}[2]{\int_{#1}^{#2}}
\nff{\intXY}{\underset{#1}{\overset{#2}{\int}}}

\nc{\fluc}{\overline{\delta_s^2}}

\rf{\exp}{e^{#1}}

\nc{\grad}{\operatorfont{grad}}
\rc{\div}{\operatorfont{div}}

\nf{\pddt}{\frac{\partial{#1}}{\partial t}}
\nf{\ddt}{\frac{d{#1}}{dt}}

\nf{\inv}{\frac{1}{#1}}
\nf{\Nth}{{#1}^\text{th}}
\nff{\pddX}{\frac{\partial{#1}}{\partial{#2}}}
\nf{\rot}{\operatorfont{rot}{#1}}
\nf{\spur}{\operatorfont{spur\,}{#1}}

\nc{\lap}{\Delta}
\nc{\e}{\varepsilon}
\nc{\R}{\mathfrak{r}}

\nff{\Elt}{\operatorfont{#1}_{#2}}

\nff{\MF}{\nc{#1}{\mathfrak{#2}}}

\nc{\Y}{\psi}
\nc{\y}{\varphi}

\nf{\from}{From: #1}
\nf{\rcpt}{To: #1}
\rf{\date}{Date: #1}
\nf{\letter}{\section{Letter #1}}
\nf{\location}{}

\title{Pauli - 1936 - May}

\begin{document}

\letter{429}
\from{Heisenberg}
\date{May 26, 1936}
\location{Leipzig}
\tags{showers}

\MF{\fU}{U}
\MF{\fE}{E}

Dear Pauli!

Since my last letter, in which there indeed wasn't much, I have stumbled into a very remarkable connection which I, according to old habit, write to you for criticism.

I begin with a typical \?{variation} of quantum mechanics from the Fermi $\beta$-decay theory. If, by tossing out unnecessary dimensions, a field function is introduced whose commutation relations give only the $\delta$-function, then instead of $\fU$ and $\fE\y = \fU/\sqrt{\hbar c}$ and $\pi=\fE/\sqrt{\hbar c}$, and further instead of the energy $\epsilon = E/\hbar c$, $\epsilon$ gets the dimensions $\text{cm}^{-1}$ and the Hamiltonian function of quantum electrodynamics becomes roughly
\uequ{
\epsilon = \int\left(
\Y^* \alpha^i \pddX{}{x_i}\Y + \frac{mc}{\hbar}\Y^*\beta\Y + 
\sqrt{\frac{e^2}{\hbar c}}\Y^* \alpha_i \Y \y_i + \inv{2}(\pi^2 + \y^2)
\right){dV}.\\
[\pi_p\, \y_{p'}]_- = \delta_{pp'}; \quad
[\Y^*_p \, \Y_{p'}] = \delta_{pp'}.
}
In such a theory, one can also set $m=0$ without difficulty \?{if interested in large energies}. A perturbation procedure always remains an expansion in $e^2/\hbar c$. That corresponds to the fact that e.g. in the theory of pair-production, the probability for the production of $n$ pairs is always less probable by a factor of $(e^2/\hbar c)^{-1}$ than that for a single pair. This applies independently of the energy of the particle.

It is entirely different in the Fermi $\beta$-theory. If, after the fashion of Uhlenbeck-Konopinski, it is assumed that
\uequ{
\epsilon = \int\left(\Y^* \alpha_i \pddX{}{x_i} \Y + \dots + 
\frac{g}{\hbar c}\Y^*_\text{proton}\Y_\text{neutron}\Y^*_\text{electron}\pddX{}{x}\Y_\text{neutrino}
\right){dV},
}
then the constant $g'=g/\hbar c$ retains the dimension $\text{cm}^3$. At large energies, where the rest masses of the particles can be ignores, this means: any perturbation procedure is an expansion in $g'/\lambda^3$, where $\lambda$ denotes the wavelengths of the particles involved. Now from this it follows: for large energies the interaction part becomes \textit{critical}; in particular, in processes where very many particles are emitted at once become no much more improbable than processes where only one or two particles ar emitted; thus from wavelengths $\sqrt[3]{\lambda}$ down, "showers" of particles are to be expected.
\sskip{More shower speculation}

\include{subfiles/454}

\include{subfiles/455}

\include{subfiles/459}

\include{subfiles/460}

\include{subfiles/461}

\include{subfiles/462}

\end{document}
