\header{Sunday morning 8/12 18 Leipzig.}

Got up early Sunday, since Eva went to Church. Beforehand I helped her peel potatoes, since today we shall eat at home -- some of the Vilna bacon. --

\missing

I feel entirely differently towards the coming \textit{lectures} than towards previous ones. I am not especially prepared, only put together a framework in the last 14 days beforehand and otherwise prepare hour by hour. I know that I know nothing, but I also know that quickly familiarize myself in any literary-hiatorical theme, that I can quickly parrot anything -- even if it was Chinese literature! -- \WTF{that is in the specialty works}{was in den Specialwerken steht}. And that is indeed the essence of the \WTF{lectures}{Collegien}. Only no overestimation of the \?{business}{Betriebs}! --

Today there seem to be signs of a formal battle in Berlin. I read it in the morning with calm ?{naturalness}{Selbstverständlichkeit}.

Teeth-grinding letter from \textit{Ella Doehring} from Posen. She is confidently conservative in her opinions, her hate is still always towards England; aside from that, the Jews seem to her to be particularly guilty.

I am beautifies by a badly-swollen jaw. The bad tooth however is at least causing no pain today. --

I brought Eva a pound of miserable apples; they now cost 2.25M and a little \?{rabbit sausage}{Kaninchenwürstchen}, a meager quarter-pound: 2.75M. They were "\?{atonement gifts}{Sühnegaben}" for some particular nastiness. In the Merkur we now pay on average for two days of coffee \textit{senza niente} 7-8M, (2x2 glasses each), in Thuringer Hof for the simplest meal 6-10M. The monthly expenditure reaches all in all 1000M (Eva's study costs 100M of that), our reserves are running out, and I only have 2000M for the quarter. At this point I also survive \?{in total apathy}{ganz stumpfsinnig}. \WTF{What will be will be}{Irgendwie wird es werden}. Perhaps in Munich we will come upon a different financial base.

% eine dick verschwollene