\header{Friday evening after 8, Leipzig 22/XI 18}

Now as before the weight on the heart that the spiritual communion between E and me \WTF{is broken and for all our love is no longer present}{...daß die geistige Gemeinschaft zwischen E und mir unterbrochen und bei aller Liebe nicht megr herzustellen}. \WTF{On top of that, the worsening financial troubles}{Dazu in verstärktem Maße die Finanzsorge}. In January the last of our reserves are gone, and then we will be \?{missing} 300M a month. On top of that, a feeling of joylessness and \WTF{lack of success}{Erfolglosigkeit} at work...Eva reproaches me for my sullenness, \WTF{to some extent the ingratitude of my position with respect to my freedom from the slavery of war -- the three names factors depress me all too much.}{gewissermaßen Undankbarkeit meiner Lage, meiner Befreiung aus der Kriegssklaverei gegenüber - die drei genannten Faktoren bedrücken mich allzusehr.} --

Yesterday afternoon at Scherner's; at eight coffee and music, all too much music, \WTF{which made me feel my superfluity}{die mich meine Überflüssigkeit fühlen läßt}. \missing

The \textit{Spartakus group} met yesterday in a rather miserable \WTF{pub at Brühl, in the back room (Coburger halls)}{Lokal am Brühl, im Hinterhaus (Coburger Hallen)}. A long, smoke-filled room, judging by the photos (among which Wilhelm II \?{was not absent}) a \WTF{union hall}{Verbandszimmer} of a locomotive engineers association. At two long tables and along the wall, 200-250 people quietly having beer, mostly young, but neither mean-looking nor \WTF{looking for trouble}{radaulustig}, some women, many soldiers among them. The whole time we were there, a \WTF{stuttering but thoughtful}{stockender, aber bedächtig wägender} chairman spoke, a \?{lecturing}{referierender} Pole or Polish Jew with \WTF{audaciously cheeky speed}{kaltschnäuzig frecher Geschwindigkeit}, a collar-less gray-haired worker, fluent, calm, intelligent, like a good lecturer, a non-commissioned officier of about 30 years, with a hard East-Prussian accent in the most passionate, fanatical, \WTF{convinced gradually weighted cross-preacher}{überzeugtestem, langsam wichtendem Kreuzpredigerton}. Everyone, each in his own way, said exactly the same thing, with a childlike naive shamelessness: against the national assembly and against freedom of the press. We are in the minority, the national assembly would \?{overwhelm}{besiegen} us, the press \?{antagonizes}{bekämpft} us. Ergo \?{suppression}{Verhinderung} of the national assembly, forcible seizure of the press for our extreme \?{tendency}{Richtung}! The \textit{general} freedom means absolutely noting to them, but \textit{their} liberation, or rather \textit{their} domination. With the fanatical NCO, who flatly demanded civil war -- “we have bled so long for capitalism (betrayed by the government socialists) that we can now \WTF{quietly}{ruhig} also bleed for the cause of the proletariat. Today the \?{cultural elite}{Gebeldeten} rule -- but we are excluded from the culture because we are too poor to afford it. The press belongs to the \?{possessing class}{Besitzenden} - we are too poor. So violence! Violence against parliament, any national assembly, the press! Violence and dictatorship of the proletarian minority, until we are in possession of the culture, \WTF{until we have achieved englightenment}{bis wir aufklärend gewirkt haben}! The bourgeois revolution did not help the excluded at all! Violence, until the nationalization of all businesses, all property is carried out!" Remarkable how peaceful the assembly was, in how calm a tone civil war against the present reactionary government of the socialists (the \WTF{warmongers}{Kriegsverlängerer} and traitors) was demanded!

% Gewalt, bis die Crashbug gefixt ist!