\header{Sunday evening, towards 8:00, 23/XI 18}

\WTF{Eva at the Con}{Eva im Con}. Where she was yesterday as well. I met her midday in the \textit{Motette}, where the famous Straube played a fugue and the \WTF{St. Thomas choir}{die Thomaner} sang many of Schreck's compositions in memoriam. I was \WTF{knackered}{gerädert} -- I don't understand that. I \WTF{abandoned Eva at the cafe}{Im Cafehaus lief ich vor Eva fort}, since she was talking shop with Hempel. And so it went the whole day, that I stood spiritually aside from Eva. \WTF{How does her tenderness help me}{Was hilft mir ihre Zärtlichkeit}? -- We got up late. \WTF{Thüringer Hof, withdrew money, directions on the bulletin board, when Becker read}{Thüringer Hof, Geldabheben, Orientierung am schwarzen Brett, wann Becker liest} -- aside from that, many hours of \textit{Astrée}, which I have been again familiarizing myself, and which I hope to be done with by Christmas.

Yesterday evening a long time with Harms and Kopke at the Merkur. \WTF{I will leave the pharmacist association this evening}{Die Apothekerversammlung heute abend will ich lassen}. --

Regarding the revolution: there were \WTF{flags out}{Flaggenschmuck draußen} in honor of the expected return of the regiments from the front; vanishingly few red flags, mostly old German and \?{Federal}{bundesstaatliche} flags. But a huge handcart full of red \?{scarves}{Tücher} passed by the cafe. Probably for the Volkshaus or the station... It is the \?{most catchphrase-less}{phrasenloseste} revolution ever: everything \?{revolves around}{geht um} economics, everything is organized around professional classes -- nobody brags about ideas, freedom songs, etc...yesterday in the Merkur \?{philistines clapped their skatcards on the table}, as in the happiest days. That was the great lesson for me: that in the wildest times of world history \WTF{the ordinary life nevertheless \?{continues}{fortläuft} and so to say fills the whole of space}{der Alltag doch fortläuft und sozusagen die Breite des Raumes einnimmt}. The poet who would have it otherwise is lying. But perhaps he would be no poet, and would be quite boring, if he did not lie. Or of course perhaps not. I am reminded of Anatole France: "Can you recall the lunatic Jesus of Nazareth? -- No, there are so many lunatics in Juda!"

The newspapers now bring twice daily so much shame, misfortune, decay, apparently impossible things that I, over-saturated, \WTF{dully accepting it}{ganz stumpf hinnehme}, hardly read it anymore. \?{Whatever happens, happens}{Mag werden was will} -- I am tired of the whole business. My own misfortune, my lonesomeness occupies me more. Only, I escape it all by the most extraordinary concentration on Astrée.

% I fled from Eva