\header{Friday evening after 6:00 29 November. Leipzig}

Astrée filled my whole day, and I am finding my peace again in this concentrated work. Everything around me is productively active: Eva composes, Kopke is writing a drama in which Merlin is pitted against Parzifal, Harms churns out article after article, Dr Luther, who yesterday sat with us in the cafe, is the author of a lovely verse translation of one of A. Tolstoy's novels -- I myself can think of nothing but literary history. That is precious little, but it is at least something. I feel that I can liberate the old life that sleeps in the petrified forms of Astrée. Of course I myself am constantly struggling with sleep in this work.

Apart from that, just the commonplaces of mealtimes and cafe-visits and \?{picking up from the con.}{Abholens aus dem Con}. We have a standing plan that I should read something aloud in the evening, but I am always too tired, indeed it is always late when we get home, since I \?{usually only fetch E from the con. at 8}{zumeist erst um 8}. Then we eat, and it is after 9 when we begin our visit to the Merkur. The evening before last, too exhausted for lectures and still not entirely ready for bed, we played -- once again after a month! -- a nerve-soothing game "66".

Yesterday evening at 8 we went to a political meeting. \textit{Lipinsk}, the independent, who recently spoke to the Berlin Reich's Conference ("Ersatz Bundesrat" say the N.N.) against the national assembly, gave a speech in front of his party in the great hall of the Zoological Garden. One was only admitted with a membership card; I said I would join right now, and went in with Eva. Giant hall with a gallery running around it, and a platform (for the committee). There were probably several thousand people present, few women, no rowdys, but \?{humble people}{kleines Volk}. Complete silence reigned. We found a place in the gallery. So far as I could see from that distance, Lipinski is a small man that looks like a manual laborer. He spoke, or rather cried, in \?{choppy}{abgehackten} words with an over-strained \WTF{tailor's voice}. Speech was entirely matter-of-fact, entirely banal, entirely insignificant, entirely monotonic, very boring. Indeed in a people's assembly one can only ever repeat \?{hackneyed sayings}{inhaltlich nur das Abgedroschene}; there only the how, the form and the temprement matter. Both were completely lacking with L. He \?{railed against}{wandte sich gegen} the treasonous \?{dependent}{anhängige} Social Democrats, \?{who no longer demand, as the National Liberals would also do}{die nicht mehr verlange, als die Nationalliberalen auch täten}, advocated for the dictatorship of the proletariat, defended -- \WTF{it was not quite clear how or by what right}{man sah nicht recht womit und quo iure} -- the Independents against the accusation of Bolshevism and the terror. We left terribly bored after a half hour.

I have the impression (conversation with Frau Streller and with a Monteur at the con) that the people here don't at all know the gaping difference between the Independents and the government socialists...I look upon the ever-more chaotic developments with dull curiosity. \?{That filled the only breaks}{Mir füllt das nur noch die Pausen} in the Astrée and the lecture. --

\missing


% the Merkur-sitting