\header{Monday afternoon, 30/XII 18.}

Yesterday evening at dinner I had to \?{get up and leave}{das Besteck hinlegen und aufhören}, since my hands were too jittery and my stomach was turning; I was so very annoyed by \?{the guy across from me}{mein Gegenüber}, a bald-headed master-craftsman, who drank his expensive flask of red wine and explained that blood would have to flow, revenge was coming, the sailors would settle accounts with everyone who had deceived us, "from the coal-barons to the majority socialists". I.e. the old man stupidly spread the incitements of the Leipzig Volkszeitung. I told him that he should be ashamed of himself...

Also, our Frau Streller is pleasant. \?{The Bavarians may let it slide}{mag der Bayerin hingehen} that she always praised noble Bavaria and senselessly ranted against the Prussians. But first she was blood-red, then moved away from the Spartacists -- and now the Jews in Berlin are to blame for everything... \?{I have such contempt for the Volk, such disgust for the Volk above all}{Ich habe eine solche Verachtung des Volkes in mir, einen solchen Ekel vor allem Volk überhaupt}. Democracy in any form is much \?{more idiotic}{blöder} than despotism. \?{Idiotic}{Blöder} is not the right word: mendacious, common, dumb, senseless, \?{illegitimate}{unberechtigter}...yesterday we couldn't any longer \?{get to the newsstand}{gingen...zur Redaction}, and since the raging Frau Streller didn't bring a newspaper with her this morning, I still don't know about the events in Berlin yesterday. But if they were bloody or important, the landlady probably would have already blabbed about it.

\missing