\header{Thursday morning, December 5 18 Leipzig}

In my absence, \textit{Becker} brought an \?{invitation}{Karte...zu} to a French lecture which he held last evening in the \?{new-philology}{neuphilologischen} club, in the Romance seminar, Universitätstrasse. I went reluctantly, but I had to go. At 7:30 I found numerous military patrols on the Univ. street. On the steps of the seminar a student asked me whether I was from the soldiers' council. "No, thank god!" He spoke excitedly: \?{the lecture had been blocked on suspicion of being political}{Man hatte in Vermutung eines politischen Vortrages gesperrt} (freedom of the press and speech! Battle over the red flag over the university, resignation of the rector!), \?{"all the old ladies" would have stood helpless beneath}{unten hätten "all die alten Damen" hilflos gestanden}, \WTF{the seminar committee only had to negotiate}{der Seminarvorstand habe erst verhandeln müsse}! \WTF{What was happening above, touching enough and impossible in France, did not fit well with this revolutionary scene}{Zu dieser Revolutionsscene paßte schlecht, was oben, rührend genug und in Frankreich unmöglich, vor sich ging}. About 30 people in the audience, of which about 16 were women, among them Becker's wife and two of his sons, the elder in uniform, just back from Belgium. Becker, in a black robe, explained in very fluent but simple French three of V. Hugo's symbolic poems, which were distributed \?{like a well-printed concert text}{wie Conzerttexte gut gedruckt}. With joy I said to myself that I probably would have also \?{come up with}{zu Wege gebracht} the same French and the same explanation. Only the personal parts (\?{Dating}{Datierung}, the reasons underlying love affairs and the like) were of course alien to me. I have added the program and a few notes on it to my bundle of papers on Hugo. At the close, Becker recounted how he got there. In Dresden he replaced professor Heyss (?), who was sent to Dorpat, and who assigned these three poems for the holidsy course, the ministry let him print them, and now he, Becker, \WTF{is trying to learn about them}{sich da hineinzufinden gesucht}. The public remarks after the lecture were very miserable. The chair, Anglist, \?{spouted that death also occurred in a poem by Mrs Brown, but one need not think of any connections}{salbaderte, in einem Gedichte der Mrs Brown trete auch der Tod auf, aber man brauche keine Beziehungen zu denken}, an old weak-minded \?{teacher}{Studienrat} stammered something about Shakespeare's lyrics, \?{perhaps since he had understood Shakespeare, when Becker said "Chenier"}{vielleicht weil er Shakespeare verstanden hatte, als Becker "Chenier" hatte}...then there was a collection for a hospital - I gave 3 Pfennige "on the sly", I am poor-enough myself. Beaming, Becker said to me afterwards: "As Vossler's student, you will find that I am \?{looking to do justice}{gerecht zu werden suche} to his idea of the personality of the poet." That B actually did -- \WTF{???}{Eigenes war aber diesmal kaum dabei, ließ sich auch wohl nicht mehr geben}.

At 9:30 I landed at the Merkur, thus following the usual track of my life. We found in the cafe our nightly acquaintences and sat for a long time. Yesterday inter alia Harms, who according to custom we accompanied back to their Grassistrasse at midnight.

\missing Yesterday afternoon I read Astrée under aggravating circumstances: behind me Eva and Kopke were performing the current Bruckner symphony \WTF{four-footed}{vierpfotig}. When Eva alone learned her Organist's Talmud, i.e. practiced Bach, I no longer heard it.

My mood alternates: joy with work, contentment with Thuringer Hof and Merkur; but money worries, jealousy of the music and of the productive and artistic creativity of most of the people who I know here, and especially of Eva...calm observation of the political process.

\?{Popular education}{Volkserziehung}: my red, red barber raged yesterday against the Socis, "who have betrayed us". He had received a letter from the Workers' and Soldiers' Council to immediately fire his help and to hire a more expensive journeyman in their place, wage and working hours pre-determined! \?{That's right}{Recht so}! \WTF{They may only make themselves popular}{Sie mögen sich nur beliebt machen}!

\missing

It is bitter to have to say with all this humiliation: like is repaid with like: in Aachen (or in Jülich) the Belgian commandant ordered: under penalty of being shot, civillians greet our officers by yielding the sidewalk and removing their hat. It is similar in the East, as Beyerlein told me of Romania and yesterday Kopke told me of Poland. --

\missing

I \?{asked}{ließ mir von...geben} Sch. to give me a three-mark piece with Wilhelm II from 1914. Collector's value! One hardly sees silver any longer. \missing. Every second new paper notes \?{turn up}{tauchen...auf}. All states, all cities give it out. And in Berlin, the Workers' and Soldiers' Council has given out 800 million marks in 14 days, which is many times more than the old government gave out. And in the Rheinland, the enemies contribute. We shall soon become acquainted with bankruptcy as well. Ever more energetic \?{object lessons}{Anschauungsunterricht} in history. --



% stone is the colour of your true love's eyes