\letter{555}
\rcpt{Kemmer}
\date{May 5, 1939}
\location{Zurich}

Dear Herr Kemmer!

Thanks for your letter of the 2nd. -- So now everything is settled. The problem of a reasonable notation of equations for higher half-integral spin (without spinor calculus) still remains.

I have now undertaken a brief supplementary report for the Solvay Congress on "Relativistic wave equations of force-free particles and their quantization". There I'll have to deal with de Broglie. So a quick question: de Broglie's theory demands, in addition to the equation
\nequ{
\inv{2}(\gamma_\mu I' + I\gamma_\mu')\pddX{}{x^\mu}\Y + \kappa\Y = 0
}{I}
the auxilliary condition
\nequ{
\inv{2}(\gamma_4\gamma_\mu I' - I\gamma'_4\gamma_\mu')\pddX{}{x^\mu}\Y
+ \kappa(\gamma_4 I' - I\gamma'_4)\Y = 0
}{II}
\nequ{
\left\{\text{N.B. De Broglie writes instead of (I)}
\phantom{\sumXY{x=1}{3}}
\right.\\
\left.
I\,I' \pddX{}{x^4}\Y = \inv{2}\sumXY{k=1}{3}(\gamma_4\gamma_k I' + I\gamma'_4\gamma)
+ \kappa(\gamma_4 I' + I\gamma'_4)\Y = 0.\right\}
}{Ia}
Could you be so good as to briefly tell me whether the auxilliary condition (II) also follows from
\nequ{
\partial_\mu \beta_\mu \Y + \kappa\Y = 0
}{III}
when $\inv{2}(\gamma_\mu I' + \gamma'_\mu I)$ specifically is substituted for $\beta_\mu$?\footnote{I suspect: \textit{yes}. But you could tell me right away with certainty, so that I needn't plague myself with it any longer. -- How do I write (Ia) with the $\beta_\mu$?} Further: \textit{What is the fastest way to solve (III) \?{for} $\partial\Y/\partial t$}, with regard for the fact that $\beta_4$ has no reciprocal? -- Finally, could you also explicitly write out the 5-rowed and 10-rowed representations for the $\beta$? I would like to make use of them in my report. Many thanks in advance!

They've done something rather dumb in Bern: Herr A. Mercier (who we in Zurich believe understands nothing at all!) has received an Extraordinariat there. There has of course been some kind of local protection influence there.

Many greetings, 

Always your W. Pauli
% zwang