\header{Wednesday evening 7:30 15 January 19.}

\missing

Yesterday there was a disturbance from which my heart is heavy today. In the evening Harms brought the corrections of my little Praecieus article with him to the cafe. \?{I had only put "V." under it}{Ich hatte nur "V." darunter gesetzt}. Instead he brought it up to the head: "by Dr. Victor Klemperer, Privatdozent at the University of Munich". I refused to give my approval to it. Under his laughing expression, Harms was apparently rather wounded. \?{As if I scoffed at his work}{Als wenn ich seinen Beruf verachtete}. \WTF{I saw my chances at being a political correspondent swimming away}{Ich sah meine Felle im Punkt des politischen Correspondierens fortschwimmen}. I explained that \?{not everyone who mocks their chains are free}{es seien nicht all frei, die ihrer Ketten spotteten}, \?{I would have to get a professorship}{ich müte zur Professur}; after that I only chose this path once, I exaggerates the warnings of the ordinarii against journalistic activity, said that I would gladly give up the university career track if I could only get a fixed post in the press, if I could be sent to Paris or Rome. Then, strangely, Harms went lively and earnestly into just this point. After the peace is concluded, new people will be needed to be sent to France, people who understand something about it. In the cafe and on the way back, one thing led to another, and when we parted ways at 11 in front of Harms' door from them and Dr. Luther (who \?{had lent me the lyrics for the little article}{die mir die Lyriker für daskleine Feuilleton geliehen}), I had the fixed idea that in the coming days the publisher of the Leipziger N.N. will make me an enticing offer. We both went walking quite excitedly for a while in the moon shine, along the elegant Tauchnitzstrasse, along the frosted Wiesenplatz, through the silver fog. We spoke of Paris, of daydreams for my life, considered whether I should accept or reject, were in a similar mood as the time we got caught up in the Neapolitan affair in Paris...It would be a bigger decision this time than it was then. We got home excited, sat without light in the moonshine, went to bed and didn't fall asleep for a long time...None of that remains today but a deep depression, hangover and uncertainty, what to do with the article. I still haven't sent it back. Eva, who I will pick up from the con. straightaway, has had a visit from Frau Harms there today. Perhaps I will hear news there. --

% Cruzin to the Caucasus