\header{Friday evening after 7 -- the 3rd of January 19}

On the 1st of January I felt so to say de droit unable to work and read only a few pages of Lotheissen. I was happy when we met Scherner in the cafe. We denounced the cold gathering at Harms' and decided \?{to make ourselves comfortable at home}{es uns bei uns zu Haus] gemütlich zu machen}. In was arranged to meet the Harms in the cafe that evening: Scherner and I \?{went out to tell him to call it off}{zogen aus, ihm abzusagen}. Eva's bile, which really was very bad, meanwhile got better remarkably fast, served as a pretext. On the way we met Harms, who just went put for a walk. We had to accompany him back to his house, where he gave us the photograph from New Year's evening, which turned out well; then he escorted us back, and against all expectations came up to us. So there we sat in an improvised gathering, against our wishes, hungry, for over an hour, with the same people as the prior evening at Harms' -- and it was warm and amicable, and the conversation didn't skip a beat for an instant, went around philosophy, politics, philology, etc...why was it more comfortable here than at H's? We have asked ourselves afterwards without result. \?{Really only at the actual table and smaller room}{Wirklich nur am vorhandenen Tisch und kleinerem Zimmer}?... \missing

I will vote for the Democrats. Harms and Kopke are for the Majority Socialists, say thatbthe liberals wouldn't be able to govern at all. \?{That is my argument}{Dem setze ich entgegen}. A Liberal cannot govern. Since he represents the individuals and governing means thinking in masses. \?{But I won't give up}{Aber ich mag mich nicht aufgeben}. The proletarians feel themselves as part of the masses, the Social Democrats represent him. I feel myself as an individual. The Liberals will not come into the government, but they will argue moderately here and there for the individuals, \?{where the governing parties balance the masses}{wo der Regierende die Massen balanciert}...the Liberals are the yeast in the cake.

% dubito