\header{Sunday evening towards 7:00. 24/XI 18}

Yesterday brought rest. Today the whole day Astrée, 80 pages read and annotated. Only briefly at Thuringer Hof and Merkur. Eva at church concerts morning and afternoon, now on the klavier, and a long discussion with hee on my jealousy over her new work, which achieved nothing. I am certainly in the wrong, totally egotistical. However, I am very sad and very lonesome. On top of that, the frightful financial situation. --

We \?{went}{wollen} again to the Thuringer Hof and then to Harms.

At noon had our lunch with both a master craftsman and a train official. They very energetically \WTF{cursed}{schimpften unterdrückt} the impossible chaotic business of the soldiers' councils. After everythung I've seen and heard, I am of the opinion that all of Germany is going to the devil if these soldiers' and workers' \?{\textit{un-councils}}{Unrat}, these dictatorships of senselessness and ignorance, are not soon swept away. I'm hoping for some general of the returning field army. \WTF{Incidentally in this request, there is obviously much anxiety}{In der Aufforderung, es würdig zu empfangen, steckt übrigens offenbar viel Angst}. Whether these troops are going to put up with disarmament and \WTF{putting aside of titles}{Ablegung der Abzeichen}?? -- The most miserable thing of recent days seems to me to be the request of the German \?{Ladies' League}{Frauenbundes} to the French and the haughty Pharisean rejection. Of everyone, the French! How can only such a base, lowly people have brought forth such glorious literature?!
\missing

% gravelly loam