\header{Monday evening after 7:00. Leipzig, 9 December 18.}

Yesterday evening the two of us alone went to see Harms. Chatted at length. He had the definite report from Stresemann that already o June 2 1918 Ludendorf had telegraphed the government:
 make peace, renouncing claims in the West. The U-boats have not been able to hinder American transport, we are at the peak of our offensive -- further success is doubtful! Thus his "collapse" did not suddenly happen in October, but rather he already knew, as we were \?{rushing}{zustrebten} into the Marne, that the game was lost! Also much conversation with H about medicine. \?{He says he has}{Er nennt sich} "intestinal troubles" and \?{it originates from cancer in his family}{stammt aus krebskranker Familie}. He is a kind little guy, with a big bald skull and s
all very bright blue eyes. \?{He is full of images of peace}{Auf Friedensbildern ist er dick.} --

Tonight at 12 I go \textit{alone} to \textit{Munich}. Eva is plagued by coughing attacks, the trip and days in Munich would be excessively exhausting for her -- it would also be very costly. I will try my luck at finding an apartment to rent alone. Additionally, I want to discuss my lectures with Vossler \WTF{and finally finish my dismissal}{endlich meine Entlassung betreiben}. Hopefully everything goes smoothly. I hope to be back on Friday -- but who knows how it will go. \WTF{Perhaps I will experience a counterpart to Vilnius}{Vielleicht erlebe ich gar noch ein Gegenstück zu Wilna}. At least this trip will be interesting -- in the Eisner Bavarian Republic. --

\missing

Now I fetch Eva from the con, where she will play for me. Heynsen had specifically praised her in class today and strongly urged her to further training. Am I wrong to uproot her to Munich? But yet we cannot just give up on our relationship without further ado. And finally there must nevertheless be possible to study the organ in M.

\missing

Munich trip 10-14 December 1918

% Can I interest you in ... decline?