\header{Tuesday afternoon, 1:30. 26/Nov. 18. Leipzig.}

Since yesterday, I feel much happier. \textit{Vossler} wrote that in February a course for war veterans will be held and that I can be a part of it. As soon as I see a task before me and return to my profession, I will get my \?{self-confidence}{Selbstgefühl} back, and 

will be able to live more peacefully with Eva. I have resolved to move to Munich in January together with Eva, who shall study further there, and until then spend all my time here on the Astrée. -- \WTF{During the hour Eva was playing the organ}{währens E in der Orgelstunde war} I went to see Becker, but only saw his wife. In the middle of the conversation she started speaking French, she could not express that in German -- mais c'est un effondrement! She is Alsatian, and \?{regards herself}{fühlt sich} as French. She spoke about Max von Baden, he had been betrothed to one of her students, he was no genius, but thoroughly honest, good and pious...Becker himself came to see me in the afternoon in his friendly manner. He now holds besides the Leipzig lectureship, that of the Dresden high school as a substitute and goes over there twice weekly, he reads Spanish there. He offered to read the Diana de Montemayor with me. In the morning I want to go to his old-French seminar, professedly to sse how he teaches, but in truth to \?{get a handle on the old-French pronunciation}{um hinter die Aussprach zu kommen}.
\missing

It almost seems as if our life may yet \?{come together}{zurecht ziehen} once again. We both work diligently, and often find in ourselves much tenderness, and a passion which is hardly seemly to name for such an old couple. --

The letters which E wrote to me in Vilnius are gradually returning. They all set out her hope in our living together in work -- only now  henceforth separate work. --

Today the valuable bacon-fat and butter package, which I sent shortly before my departure, also arrived. A \?{field-post parcel}{Feldpostpäckchen} with bonbons however seems to have been lost.

\missing

Berthold informed me of the birth of a son (Georg Wilhelm) on November 18 with a printed announcement; I replied via visiting card. --

The money troubles remain present for the next quarter as for the last.

%us Crumpus room