July 15, 1919
Tuesday evening towards 12:00

Two extensive letters from E, things are apparently good with her. -- In the morning, interesting \?{course at the library}{Bibliothekscolleg} about cataloguing and the like. Then spent the morning preparing my lecture. Finished with the dramatists up through Ruy Blas. My lectures are good, at least I can tell myself that. Wrote to E. Very tired after the lecture. A first little bit of preparation for the scholarship exam, since my course on the 17th century has somewhat slipped from my mind; read a few pages in Morf's Overview...After supper to Meyerhof's, very boring tiresome people there, Hamburg Jews, who of course know my local relations -- awkward! Afterwards however very lively alone with M and the decent (naturally also \WTF{pushy}{schiebenden}\WTF{???}{langen}Hemecher. After a while -- Elena had made us coffee -- there appeared a young fresh handsome man of perhaps 20 years in an officer's uniform without epaulettes, with\WTF{EKII, Saxon August band}{mit EKII, sächsischem Augustband} wounnded- and aviator-badges. Many types of business came into the discussion: stockings, suspenders, soap, cigarettes, of a trip to Darmstadt and Frankfurt. Best behavior, confidence-inspiring. Which troop did he belong to, I asked. "None at all" was the calm response, even though the wearing of uniforms is forbidden. A moment later I heard that the youth was also credentialed by Noske (I looked at the papers once more later. "8th Hussar regiment. Holder is a member of the Freikorps. Government troops, Berlin. Signed Noske. He may carry weapons. All authorities are requested not to hinder him...and to support him." Three stamps. Space for signature and photograph.) With that, one could move freely in all of Germany, can travel to Berlin via military car (and thus for 4 or 5M), is allowed in arracks and can eat there. Good for trading and agitation. The 80M certainly be made up after just a couple of trips. There is no high treason in it. Incidentally there are already leave passes for 25M. Perhaps Hans M can get me one for Driburg. As the youth left, he said that he was one of a company of 20, behind which stood Berlin donors; they bought contraband in large quantities for Berlin! \missing Nowhere have I seen so deeply into the complete uprooting of our public life, into its boundless Russification, as with Hans. With respect to the state we have all become amoral. Indeed there is no state any more. Went home through incessant and mightily pouring rain.