\header{Munich 3 July 1919. Thursday morning. Berg Pension, Schellingstrasse 7.}

The great \?{room}{Vorderzimmer} with the little bedroom only belongs to us until Monday. Then the piano goes back to Wetsch and Eva travels to Driburg, and I the little corner room that was Frau Sobat's, who has gone to a painting school in Ammersee. I will be very alone and will work very much; so I have mixed feelings with regards to the coming weeks. For Eva, I hope for recuperation of her nerves and fulfillment. Air, land, a little church organ, mudbaths for the again-awakening rheumatism and above all, absence drom Munich...In my quarters, I am paying -- after energetic negotiation -- a daily price of 8.50, light and service included. E is to pay Frl Mueller 9.50 in Driburg; \?{it will sometimes be more, but far over the 3000, the sum we are already accustomed to, it will probably not rise in these quarters}{es wird mancherlei hinzukommen, aber weit über 3000, die nun schon gewohnte Summe, steigen wir wohl in diesem Quartal auch nicht}. We already had 20M here a day in rent and such high side-expenses that she \?{could not go higher In Driburg}{nicht mehr höher sein können}. I was pleasantly surprised that this quarter is taken care of without getting into the Sebba reserves.

\missing

Because of the war-relief I was with the current dean \textit{Frhrn von Bissing}, who as an all-German is well-known and much-hated, who during the bad hostage days kept himself hidden; a small, skinny, elegant gentleman with blond mustache, blue eyes, nervously rolling his head and neck back and forth. I had never personally spoken to him, knew him only from faculty meetings (in later times he had indeed always been represented by Rehm). Waiting outside, I asked a younger lecturer, the religious history lecturer Heiler, whether one said "Herr Dean" or "Herr Professor". "He likes best to hear 'Herr Baron', but I say 'Herr Professor'!"
I used 'Herr Baron's much and often, and we understood eachother very well. Even politically. Event university politics, where I was against hasty reforms and \?{demagoguery}{Futterneid}, and was pleased with the uncommon character, which in these times don't grow on trees. I played a role, but it wasn't difficult for me, because I stand a bit closer to the right than the extreme left. Bissing showed me a dented bullet, which had flown into his dean's office on May 1, and as the only bullet in the university certainly was intended for him personally, he named it "Tell's shot". He mentioned his father in Brussels (the late Gouverneur), he stressed that he lectured unpaid - I don't know why - in Munich, that he maintained his conservative opinions without personal gain. We understood eachother very well and I shared my [concerns]. That I need to have the title of professor, and would like to have it quickly. On this he (who incidentally wore a medal in his buttonhole) said: he had processed my Genter affair, knew my merits(!) and my particular bad luck, he would ask that I as soon as possible would become professor. On Friday there would be a faculty meeting. "Have Vossler give me the outline and give me as supporting documentation a private letter in which you summarize your history and inquire whether you don't have some right to a title from your previous appointment in Gent and Munich." (This is of course a summarized - \WTF{livianische}{???} speech). On the same evening (Tuesday, July 1) I wrote to Bissing as arranged and yesterdqy afternoon instructed Vossler. He will do everything for me, but is skepitcal as to the swiftness of the appointment. Bissing was a passionate nature and doesn't come through. If I was put forward, a series of Ordinarien would push their protoges through immediately, and I alone and outside of the set wouldn't have a chance...So that is again delayed, and meanwhile ministries, states and all of our \?{bourgeois establishment}{Bourgeoisieeinrichtungen} are crashing together...I no longer believe in the continued existence of the present state of affairs, I now expect the worst coup and breakdown in the very near future. I would have very much liked a title, an outside position secured in this chaos. But I have no hope.

This week I was totally satisfied with and very pleased with my lectures. They went over especially well, even yesterday's \?{seminar exercise}{Seminarübung}, which was indeed new to me -- the first time there I had no coherent presentation -- and I felt that my calling was the professorship. If I could only get one actual and nourishing post, and not in Munich! And the classes always give me stimulation for writing. I will still make a study of Romanticism (the \textit{German Rom. Monthly} is now appearing again, Winter wrote me, he could probably bring out a contribution from me in 1920<!> after catching up on old material), I am planning an essay on les Misérables or perhaps V Hugo's novels, since I have to be very brief in class, in the seminar I elaborated a study on Montesquieu's style, I will draw on the significance of individual words -- so yesterday I spoke about \textit{sensibilité}, which I took as a Rococo word between raison and sentiment...Kaeser said to me: with all the others one hears linguistics, with me, philosophy, cultural and literary history. That did me some good, although that is indeed precisely why I will never bloom into an Ordinariat.

On Friday I will go with Eva to \textit{Lerch's}, on Sunday to Vossler's. In a strange manner \textit{Jordan} invited us via a postcard to this or the next Friday, after he hasn't cared about us up until now, nevertheless we already saw him once at the start of February. He wrote that he had not yet been able to repay our visit, since his wife was still was, and will be for a long time to come, in a sanitorium, but he hoped that she will be able to be able to come home on the Friday evening of our choice. \WTF{It will go like Schwabing, but it will nonetheless be a "treat"}{Es werde Schwabingisch zugehen, aber doch einen Imbiß geben}. What strangeness! How can he assume that we wouls know about his wife's sickness. And now too much intimacy and friendliness after increasingly-awkward brusqueness. Jordan must have been present at by habilitation speech; but I would not recognize him on the street. He is probably an \?{out-classed, over-aged professor in title only}{deklassiert, überalterer Titularprofessor}. But financially well-off due to the business school. Falling out with Vossler. He is suposed to have begrudged me Gent, he said to Lerch: "For Romance languages we onky have two philologists here." I 

{te: Eva is away, I would gladly come alone next Friday. --
I've read a lot of Zola these days. Eva feels sick, I had to read \textit{Bonheur des Dames} to the finish. Also I have been glad to be together with her a lot these last days. I will certainly find enough time for work alone in the coming weeks. --

This evening at eight o'clock I finally hold the \textit{Lecture on the French university} which I have been working on for several weeks. \?{It is eluding me and I have to look at it more closely}{Er ist mir entfallen, und ich muß ihn mir genau ansehen}. I am skeptical as regards its quality. -- \missing the evening we we tont Stephanie. P several timesontius was there, yesterday Meyerhof too - but the main thing blewas the ak timnewspapersthe conclusion of the peace of Saturday {leves} oe dull and nearly without words. First, the ceremony was only worth silence; today a B.P. article by Paul Fock is, who was present in Versailles, circulating, {he general feeling is basically: {wounspokentortion and disarmament, so that there is much anxiety and distraction about the domestic situation. We are probably close to a new explosion.


%