\header{Thursday evening before supper und later. 10 July 19.}

\missing

Eva only left yesterday at noon. \missing. She is supposed to have been in Frankfurt yesterday evening, and she is supposed to have been able to get on a fast westbound train there this morning. Who knows when I will learn where she had landed. Luckily I can rely on her independence. But she limps with such effort on her rheumatic knee. She had a second-class ticket, I have provided her with plentiful money -- \?{which was difficult to do}{was war mehr zu tun}. I think the stay will do her good, it will get her away from Munich and speed my recovery. \missing

This morning at the dentist. In the afternoon with \textit{Muncker}, told him what Vossler had advised me to do. He said that Vossler had also urged him to direct me towards linguistic work. Muncker seems to be of my opinion regarding literary history, and has remained true to it; we came to the idea that literary history was as intellectual as philology (which of course sounded a bit comical in M's mouth). Only M advised me of the possibility of perhaps at some point putting out a brief language essay or holding a linguistic lecture. I had the impression that he wished me well and did not doubt in my future. But it will still last "a couple of years". They all torment me with the "couple of years". \?{I am so bad at waiting}{Ich kann so schlecht noch warten}...Tomorrow the faculty shall advise on the Extraordinariat, where I shall also be. Vossler has called it "childish" that I just want the title for a book...\missing