\header{Friday morning, after 9 o'clock. 18 July.}

I stopped with my notes yesterday and slept until 8:30 today, non sine immortalitate.

As Kollwey \WTF{visited me}{mich...abfaßte} yesterday I came right from Hans M's. He had had to have the young "officer" with the Noske passes, who he himself had hoped to do business with, arrested, since he turned out to have been \WTF{???}{zum Glück noch bei Zeiten als Hôteldieb} a serious swindler. Hans said to the police: he wanted to have the man arrested, he himself was a black marketeer, but honest! Also, H's big cigar business seems again to have come to nothing -- he was to earn 60,000M for four million stubs, his companion Hamecher just as much -- and H said wistfully to me: You didn't even come to Dresden, "you are from the same family as I!" Today he stands trial; because of some forbidden business (all of his business is forbidden, since he is not registered) he has been fined 3000M by the police; he has filed an appeal and will certainly have to lay at least that much...Hence he is an honorable \WTF{Haut}{Haut}. \?{I only wish that he was in Palmero}{Ich wünschte, er wäre erst in Palmero}. --

Towards evening I wrote to Eva, then after eating \textit{Kaeser} picked me up and poured his heart out to me. About his future. Remarkable what trust the proud and guarded man has for me. I akwsys try to strengthen the self-confidence that he earned through the course of the war and \?{big changes since}{Umsatteln ins Wanken}; he will certainly at some point become a \?{leading light at a university Romance Languages department}{romantische Universitätsleuchte}. We took a long walk through the English gardens; dark passages, foggy meadows, and above all, totally unexpected on my part, fireflies. A bit of nature and Summer, I know nothing at all about either these days. It was very pretty. We then sat down for coffee at the Stephanie, and finally promenaded back home around midnight like two young men. Future, prospects on the university track, Lerch, Vossler, I...Once he also got into females, seeking connection, fearing \?{maidens}{Dirnen}; there I just warned about the \?{dirtiness}{Verseuchtheir} here (Ritter said that syphilis is especially bad here) and then demured, that did not fall into my Romance-philological wheelhouse. But naturally the conversation torments me in my loneliness. --

Still to be completed by Vossler: \textit{Croce} had sent him a suo libro Goethe. In the accompanying letter he also greeted me, "although I paid him no farwell visit and although I had written indiscretely about him during the war". (By which he means the Süddeutschen Monatshefte, which indeed -- see the Wilna letter! -- Manacorda is to have answered so wildly.) Vossler replied that I had not paid him a farewell visit since it would have been painful and awkward for me, and as to the indiscretion of my publications he knew nothing. We should however forgive eachother everything said during the war; have also written Croce of the Germans: che popolo di pensatori grossolani! And V beamed about the successful counter-blow.

I have particular luck with \textit{barbers}. In Leipzig I had an epileptic. Recently a new youth shaved me. Very fast but good. He is trusting and told of serious nerve issues in the field. Now yet again come the seizures. "If I shave fast \?{it works}{geht es}, \?{when I go slow the knife slips and I cut}{bei langsamen Führen fliegt mir die Messer und ich schneide}." \WTF{And so he set to work on my neck}{Und dabei saß er mir an der Kehle}! As I was telling that to Vossler he burst out laughing: "You can only save yourself in two ways: write a linguistic paper and learn to shave yourself!" 
Yesterday I told the master about his student.)

\missing

%