\header{Friday night 25/July. 1 o'clock}

\missing Tired this morning. Ordered V. Hugoniana at the library, read Ventre de Paris for a good while at home before I was able to drag myself to work. Prepared for the \?{morning course that takes place every other day}{halme morgige Colleg} -- Notre Dame. I will read from 3-5 tomorrow in order to be finished through mid-August. \missing After that, to 28 Liebigstrasse. To Kraus, Paul's beardless still-youthful successor, on the first floor. He must have heard many good things about us from Muncker, since he received me \WTF{orientiert}{???} and very, very charmingly. "Are you coming to say goodbye, are you going to Dresden?" I responded wistfully in the negative. He consoled me with strange proverbs about possible failure; \WTF{for the most part only the unlucky are nominated}{man kandidiere meist erst unglücklich}: "The first three cats are drowned." I had to smoke a cigartte, tell about my work. D'Urfé, Argenis, Becker. What did \WTF{I think of his dating of Marot's poetry}{von seiner Datierung der Matot'schen Dichtung hielte}? I said with an iron brow that I was not fully convinced, there was no mathematical proof, Hugo had e.g. intentionally falsified dates of poems, if he was \WTF{trying to emulate the mood of earlier epochs}{stimmungsmäßig in frühere Epochen sei} or if he wanted to conceal himself. I knew that directly from Becker (from the lecture in the Leipzig Philological Society), and I have not read Becker's Marot at all. But the answer made a good impression. I also claimed that the D'Urfé plan was all mine, only the Argenis was Becker's. He thought that D'Urfé was also important for Germany. He advised me to remain peacefully with the literary history and to not switch over to grammatics. He seems to be well-instructed in \?{the university's relationship with the Romance languages}{dir romanistischen Universitätsverhältnisse}, knew about Lommatzsch's reply. --

Then I went up to tea at \textit{Muncker's}. I was deathly bored from 6:30-7:45. As I was leaving, Muncker told me in the corridor that he had written Walzel in detail and that my prospects looked very good. -- 

\missing

%