\header{Sunday afternoon 13 July 19. 4:45.}

Already the $o\epsilon\xi o\nu\epsilon\lambda\lambda\epsilon$ torments me and since I don't want it to overtake me and since I have 7 weeks of lonesomeness before me, I need to quickly create relief for myself. As regards health, I am doing poorly. I probably have a cold, and again have the old \?{headaches}{Schmerzen in der Stirngegend}. --

To the reading room yesterday. I began the \textit{Comprehensive overview} of Romance literature, which \textit{Morf} gave in Teubner's \?{Contemporary Culture}{Kultur der Gegenwart}, which was highlighted in Vossler's research reporg "French Philology". It is a very good summary. But such reading is so infinitely sour for me; I am always falling asleep over it, and that depresses me so. After eating I went to the Propylaea, which are flanked right and left by temples. The new \textit{State's gallery} is now housed on the left -- I do not know what was there before. Modern paintings from the New Pinakothek, lavishly hung; Marées had for example a whole magnificient room for himself, where the paintings are recessed into the wall. I saw familiar names and even familiar paintings: Stuck ("War" and "Sin"), Hodler (War volunteers of 1813, \?{putting on their uniforms}{den Rock anziehend}), Liebl, Thoma, Liebermann, etc. Totally modern: Cézanne, Gogh... I understood all too little of it, and went home very tired. \missing Up until today I have \?{carefully used my time}{nutzte ich bisher meine Zeit sehr aus}. In the morning I read a very lovely Latin and Italian Petrarca letter \missing and \WTF{have now determined that the letters went through Fracassetti's hand}{beschloß nun doch die Briefe an der Hand Fracassettis durchzugehen}. It will certainly be an improvement. Then I wrote a \?{long}{ausgewachsenen} letter to Ella \textit{Doehring} until around 11 and from 2-4 in the afternoon wrote similarly to Scherner and \textit{the elder Meyerhofs}, with which all of my \?{letter-debt is paid}{Briefschulden...getilgt sind} for a while. Now all that remains is the \?{daily letter}{Tagesbrief} to Eva...At 11 I left for planned visits with the good hat that Hans M sold me for 15M for the Berlin trip, and which of course promptly got wet. We have had uninterrupted heavy rain since 11:30. I first visited the Glyptothek. Even here, and here for the first time, I was struck by the statiousness of the high halls, such that I was not cramped as usual by the fact that it was overflowing. There was actually nothing there that I hadn't known for a long time through many illustrations. The Egyptians now stand closer to me with their \WTF{connected stylizations}{gebundenen Stilisierung} \WTF{???}{und erklären mir Allerjüngstes, sind aber klarer als dies Allerjüngste}. I find the early Greeks, with the enormous bodies and childish faces, faintly comic, the later 
 
 
lready very fine, but do not move my heart. The \WTF{battle scebe}{Schlachtaufbau} on the temple's pediments is very \?{livelt}{lebendig}. The dead fighers lying in a later room, \WTF{the head very low}{das Haupt ganz tief}, the arm in front of it, the chest heaving, the sunken stomach, is probably the finest piece in the otherwise not very rich collection. I did not bother with the ceiling paintings...At 12 I began a trip through the city, up to the foamy gray-green Isar with its beautiful green construction. I made three visits in the very elegant, villa-like Mauerkircherstrasse: left cards for Mareks and Berneker, was warmly received by Vollmer. Latin with a full gray beard, his wife in the countryside. He was gracious and said some kind words about my lecture (French university) which he recently attended.

Hans M wants to show me a \?{Noske identity card}{Noskeausweis} this evening, signed by N, applicable for travel throughout all of Germany, to be had for 80M!

\missing

%