\header{Sunday morning 6 July 19.}

The whole day yesterday constantly on the way somewhere, in connection with Eva's trip. The rail strike in Frankfurt seems to be finished, she can probably go tomorrow. \missing

In the evening we had to go to Vossler's, and there I had a bitter experience \?{which I saw approaching slowly}{das ich langsam habe herankommen sehen}. Vossler, who brought me to Romance literary history himself, now says that I should turn back, I should hold put on the publisher, I must work on monographs. The Astrée. But above all, scientific linguistic work. Sensibilité, gloire? No, that is cultural-historical Horribile dictu! But the development of the qualitative gentives! I said to him: you give an idea, and I am to spend months adding to it, not genuinely reading, but rather taking samples, and thus arise books on the future tense and thus one gets a professorship. I.e. -- I was not so blunt, but yet my opinion was de facto made clear. And Vossler extolled Lerch and this type of work and said: one cannot always do mental work and must also "collect", and other times, this was mental work, and he only wanted to discourage my contempt of linguistics. And he constantly stressed that this was the only way to get a professorship and that I in those days would have \?{certainly gotten a post}{bestimmt Posen bekommen} if I had only filled out my habilitation a bit. But yet in this speech was contained \WTF{what an intellectual needed to do}{was an Gedanklichem zu geben war}. Do nothing -- collect, document, \WTF{trace}{bewurzeln} -- with a word: \WTF{laboring}{breittrten}, being apathetic, lying. A shoemaker does honest manual work. And \WTF{mental workers}{geistigeres}...In the garderobe Vossler told me yet again: "One need not read everything. One take samples. He who searches intelligently finds!" I have watched Lerch's \WTF{hunting and begging for the future}{Futurjadd und -Betterlei}. Catching fleas is mental work. It is clear from the foregoing that \WTF{Vossler is tired of my work}{Vossler meiner müde ist}. I \.{shamed him}{compromittiere ihn} with "Psychology and culutual history". Lerch, the philologist with the \?{philologist wife}{Philologengattin}, is his pride, his support. An Ordinariat for Lerch. With Lerch also a \WTF{firm friendship of science and the heart}{feste wissenschaftliche und Herzenfreundschaft}. Weekly. Sonja Rabinowitsch joins in. And according to the prior enrollment I need to come once every two weeks. -- The Lehmanns were also there. While theybhad at first wantes to invite us, they are now very cool towards us. The malicious little blond, who I never quite trusted, had probably learned of my secret \?{Jewish taint}{Judenmakel}. \?{I am very bitter}; my plans have fallen through and I don't have any others...From the start Vossler spoke about the opportunity for a professor-title very coolly, the faculty have been occupied with it and would bring the whole class of 1914 into the rolls; how long that lasts is besides the point, one shoudn't put a title on a book any way. (But the publisher has that expressly in the contract!) He spoke \WTF{tactfully unkindly}{menschlich ungut} about Bissing, he was an incoherent fool who had committed stupidity upon stupidity as "Crown Prince of Belgium" and elsewhere. Independent of his nerves, but not \WTF{moody}{Stimmungsmensch} -- "on top of that, he is too unartistic." -- 
Eva came home with a sore knee and frayed nerves, I was just as broken on the inside. Regarding my university presentation, Vossler sounded annoyed: "I have already told you \WTF{it had fallen very badly}{er hat allen sehr gefallen}!" (Unspoken addition: Bad enough for a philologist!)...\missing

In the previous German preparatory course I had a student who was a year older than I, a big blond man woth \WTF{dem St der Küste}{???}! the Bremenser Kolwey. He had a directorship in India, 16000M salary, horses, dogs -- his fortune was for the most part in England. For a little while he was on the Eastern front, he studied nationak economics, wanted to take a doctorate then try to get back to England; he spoke 7 languages. So he sat calmly, intently, enthusiastically on the bench with the abitur students. I met him again yesterday; he wore a common uniform of the guard regiment, partly out of conviction, partly for pay. We became friends, he will visit me when \?{Eva is away}{ich Strohwitwer bin}. I also want to read \WTF{his essay}{seinen sauber in ein Heft geachriebenen Aufsatz} "Freiheit die ich meine". The calm way he bore the u-turn in his position struck me: student, common soldier, probably also impoverished. But he is unmarried and has not permanently failed in his calling; he even apoke very optimistically about our trade relations with foreign countries.

\missing

% came 