\header{4 July, Friday morning.}

\missing

The \textit{lecture} was a small triumph for me, and might benefit me some way or another. I spoke remarkably clearly and freely, I was another person when I was standing at the lectern and listened to myself. I was able to read out the statistical material yet stay away from the manuscript and to keep my speech free and lively, resolve the abbreviations in the material and underline the essential spirit. I had complete attention, applause, and honest thanks. About 50 attendees, among them about a dozen and a half professors, Frau M端ller, the prorector and valiant medics, Bissing the dean, Vossler, Muncker, Berneker, Maurenbrecher, Frankl, among others. M端ller and Bissing participated in the question and comment portion with much interest, Bissing with the greatest kindness towards me, a bit talkative about his own experiences in Gent (he was probably with his father in Brussels), M端ller was grumpily matter-of-fact as always, impatiently puffing on an unlit cigar which was laying before him for a while. I gave all of the information with a cool head: whether French students were tested on specific textbooks in their exams, whether a professor might apply for a position -- \WTF{here I pulled something about the brigue out of thin air}{hier sog ich mir etwas 端ber die brigue aus den Fingern} -- etc etc. I knew everything, yes indeed! Of course in truth without having any inkling. Intuition lives! \missing It was a success. Yesterday evening at 8. And this afternoon my professorship is to come up for discussion in the faculty meeting. -- I asked the Frankfurter Zeitung whether they want to print my talk.

\missing