\header{Monday morning 7:45 21 July 19.}

Yesterday after eating a telegram from Eva, she had been three days without news and requested a telegram. The post functions very badly; I have written her daily. I will now include some greeting cards among them. Of which I just wrote the first...At about 3, somewhat earlier, I gave a reply at the post office, later reproaching myself that I had not "\?{urgently}{dringend}" telegraphed back. But that costs triple, and I still think that she will meanwhile have gotten one of my many letters. E's dispatch has not taken a full 24 hours; it is however not said that mine will be just as "fast".

\?{I got a sudden desire to have fun}{ich gab mir einen vergnügungssüchtigen Ruck} and went on from the Telegraph office to the Gärtnerplatz, and stood obediently in line there for the garden theater, where for the 275th time the Dreimäderlhaus was playing at discount prices. (Eva never wanted to see it because of \?{the mess they made of Schubert}{das Schubert-Verhunzung} -- I was drawn to it.) But right in front of me everything was sold out; so I went home, had some coffee made and set to work intensively. \missing

In the morning I again spent a good hour at the \textit{old Pinakothek}. \WTF{There are new guys there, though Rubens was not in the sexual mkrass}{Das sind doch andere Kerle. Rubens zwar nicht in sexuellem Fett}. I cannot pick out the vast majority of the figures \WTF{in the two hells}{in den beiden Höllenstürzen} from one another. Saw Dürer and Van Dyck again. The fine dogs. Now Honthorst discovered: the lost son. How the fat carefre blue-shirted 

uth sprawled out in the picture and stretches out his legs literally under their nose! How all other people, the sweethearts of the lost at their cheeks and the two couples and the back and front of the table, have directed their glances to the lost! The youth is however not menacing, only carnally satisfied, probably cannibalistic...finally, a few small French pictures: the fancy naked girl on her belly by Boucher, the beautiful head by Greuze. Now I imagine that this is more elegant, stylish, delicate than Italian and French paintings, \WTF{or do I even know that}{oder weiß ich das eben}? -- 
Professor visits, which are limited to leaving cards, conclude the morning: Borinski, Wolters. Bissing must have changed his address. \missing
 %
 