\header{Friday night, after 12 o'clock 11/July 19.}

Good news from Eva from Wednesday evening out of Frankfurt. The capo had assigned her a first-class coupé, she will continue to Driburg on Tgursday morning.

Unfortunately I was in bad health whole day. The heart, the nerves. In the morning, found no peace and quiet to work at the university library, came home ravenously hungry and shattered, read Zola and \textit{Vossler}'s research report in which he treated my Montsequieu as totally and honestly worthy. But in the evening Lerch recounted that V had flat-out told him on Tuesday that my Montsequieu was actually only "\?{interpretive}{darstellerisch}", not scientific work, that I should sometime write something totally factual, without \?{any interpretations}{alle Darstellung}. I fear that I have nearly played out my university role...After eating at Hans M's for a cup of coffee. Afterwards he came to my place for a little while. Later I finally got to work. \missing -- I was invited to Jordan's (July 3rd) and Lerch telephoned me, whereupon I picked up the married couple. Beforehand I wrote to Eva and ate here in the evening. Then I was at Jordan's from 9-11:30. A lovely elegant home filled with books on Hiltenspergerstrasse.

Jordan, mid-forties, a \WTF{clean-shaven beardless}{zerhauenes bartloses} face, thin, gray-blue eyes, pince-nez, a too-loud laugh, too-frequent emphasis: we are in Schwabing -- otherwise however an admirable host. There was a younger priest there, and an oldish rd-haired typical Frenchwoman, wife of an Argentine, Martinez, speaking broken (but not badly) German. There were rolls with anchovy butter, beer and good cigars. The conversation was light gossip with all kinds of jokes, but yet strongly philologically-tinted. Jordan was born in Paris and went to school there up until he was 12 years old, he seemed to also speak the argot fluently. Here he is a branch- or main-office director of the business school. He speaks of Neubert as his student, of Becker as a disagreeable drunkard, the Meyer-Lubkes as his benefactors, has been as it were driven out of Vienna with anti-semitic agitation, since only girls and Jews were seen in M-L's class, and since Jewosh people (Herzog and Spitzer) had habilitated with him. I recalled too late that \?{at some point Becker had thrashed Jordan}{Becker Jordanum irgendwann vermöbelt hat}...Once J's bitterness came through. He was proposed for the first position somewhere and was then not named, since collegues in Munich had \?{called his knowledge of French into question with mischievous anecdotes}{mit tückischen Anekdoten seine französischen Kentnisse verdächtigt hätten}...but otherwise the evening went on with harmkess gossip. Only meanwhile my heart was heavy, and on the way back we spoke again about my case. Vossler 