\header{Tuesday morning, towards 10. 7 January 19}

It's bad that I write at 10 o'clock in the "morning" and still haven't had breakfast. The time slips by and my preparations are not going forwards. I must just make it "intuitive". Like my inaugural lecture.

Eva was still suffering a lot on Sunday. It was lucky that we were at Scherner's in the afternoon. There she had every possible medication -- aspirin, pyramidon, trigemin, bromides -- at her disposal, and on top of that liqueur and other alcohol, and on top of that distraction, conversation, and music. \missing. But even today she is still quite weak, and is having trouble chewing. She had to cancel -- for the first time! -- her organ lesson. \missing. In the afternoon Kopke was here and remained for a modest supper, which we had at home for a change, then we sat a little while in the Merkur, \?{where there was a special edition by the new Berlin Spartakist putschists}{wo ein Extrablatt vom neuen Berliner Spartakistputsch lag} -- on the 6th of January, the "High New Year", no newspapers appeared in Saxony --, finally we went to see Harms, first sat for a long time alone with his wife, then until 12:30 with him, who came late from the editorial office. He very often told of his frightful first marriage and divorce (\?{he seems to have fallen in love with someone who was very nearly a prostitute as a younger man}{er scheint als junger Mensch einer fast richtigen Dirne verfallen zu sein}), also of their past life; she is a craftsman's daughter, and was employed in the commercial and newspaper business. Harms himself then reported out of Berlin. It still isn't clear. Chaos and looming civil war reign. If the government should not succeed in taking drastic measures -- Noske is a dictator -- then I believe that Germany is finally lost. Then we will get occupation by the Entente and total collapse of the Reich.

\missing

I checked yesterday once more that we were both registered to vote; Eva's name was added. The lists are now in a lovely long narrow white hall with a surrounding gallery, very many people pushing in and out; nevertheless it went peacefully. How long now?

%oftene v disorwärts!