\header{Monday afternoon 1 o'clock. 27/January 19.}

\missing

Today, I have returned all of the books to the university library, taken 700M out of the bank, and wrote the rest over on account to Munich. In the afternoon I will make a goodbye visit to Becker and ask him to let me take the Lotheiss materials with me to Munich for a month. Today or tomorrow I will also start writing the first lecture. I would have been to start it already, but I have been going over a little speech that I will perhaps give this evening at Scherners. We will eat there for the last time, and later Harms and Kopfe will come. I want to thank, I want to emphasize, how we have mutually supported eachother spiritually in these times, and \WTF{have in our minds risen above the food troubles}{in Gedanken über das Fraßelend erhoben haben}, and at the close I will speak about our working together in the rebuilding of Germany, \?{I will make all of that warmer}{ich will das alles wärmer machen} like Harms did on New Year's Eve. Whether I \?{that}{das ausführe} however I do not know. It depends on the situation. --

The Munich academic Hilfsbund has asked me to do my lectures at a different time than Jordan's. Indeed that has already happened. Signed: \textit{Dr. Mahrholz}. Since his wife conducted herself like an oie plumée in Italy, we have (without rancor) \?{gone our separate ways}{auseinandergekommen}. He played a certain role in publicity and student politics. I used the occasion to \?{put myself in his good graces}{mich mit ihm ins Einvernehmen zu setzen} and to write a few hopeful lines...\textit{Lerch} has an articoe in the "Glocke", in which he explains that the educated would have to vote for the Social Democrats (a few short months ago however L was still very right-wing!) That is wrong and dumb. I am bourgeois, individualistic, and ambitious. \?{I am very optimistic for}{Ich sehe bewußt auf} the bourgeois program, (1) since I am sympathetic to it, and (2) since the future belongs to them.

In the morning I upset Eva again \?{by getting upset by a word from her, that her organ problems \textit{seemed} to be put before my career problems}{indem ich mich über ein Wort von ihr, das ihre Orgelschwierogkeoten meinen beruflichen voranzusetzen schien, kränkte}. I am so over-exerted that I am hateful. If we were only beyond the first Munich difficulties!

Munich

\header{1.II Saturday evening towards 10. Pension Michel, Bayerstr 57}

I cannot get the idea of being at home here in Municn into my head. I felt much more at home in Leipzig; here it is a bohemian temporary measure.

\textit{Tuesday the 28th of January} in Leipzig, I had a lot of running around and stress, saying goodbye in the cafe, no notable adventures.

\textit{Wednesday, the 30th} I got up at 4 o'clock, \?{got to Berlon only one hour late}{fuhr mit nur eine Stunde Verspätung nach Berlin} and was there around 12 hours with Meyerhof, Sussman's mother, Georg and Felix.

Wednesday night and \textit{Thursday (the 30th)} I was sitting on trains a total of 21 hours (boarded $1\frac{1}{2}$ hours before departure, in order to get a seat, and a $6\frac{1}{2}$-hour delay!) We then found accomodations here, were with Meyerhof, at Ethos, Akropolis and Stephanie, our old usual Munich \?{haunts}{Sitzpunkten}.

\textit{Friday the 31st} we slept until 11 o'clock and only went outside at 1. \?{Dire news about housing}{Aussichtlose Wohnungsauskünfte}. In the barracks. Went for coffee and \?{tp an evening gathering}{Abendgesellschaft} with Hans M, for Friday tea with Muncker.

\textit{Sunday 1/II} the whole morning in the barracks. Finally released. Coffee with Hans, visit with Vossler. Proceeded with Eva's enrollment to the academy. Ethos, and a short while in the Cafe National. Now up here with heat and electrical light, \?{the only advantage to being in Munich}{die einzigen Münchener Vorzügen}.

In the morning, honest work on the lectures shall begin. For that, a visit to the philosophical faculty for Vossler's advice. So I don't know when I'll manage to come up with the more detailed report of the experiences outlined here.

I am now stoic, now despairing; we live in financially-unfavorable circumstances, and so anxiously and so uncomfortably that I don't know how I will succeed in concentrating on work, and how I am to get by with our money for long. I will not be able to be journalitsically \textit{and} scientifically active at the same time. The fantastical revolutionary clamor around Hans [Meyerhof] repels me; I don't know if I am able to patiently wait around for recognition in the peaceful scientific circles.
%} delay! Hannity has read a lot about EMP