\header{Saturday 25 January 19. Toward 1/2 3.}

The Neuberts have a four-room apartment on Fockstrasse in Connewitz. Only one room is heated, one servant girl is missing, they complain about the rise in prices. But the apartment is solidly, elegantly furnished, and the entire young household makes a \?{good impression}{bestfundierten Eindruck} and fills me with envy. Certainly at the moment we may spend more than the Neuberts; but we are desperately poor, and they are in secure circumstances. The wife, young, blond, Saxon, has a fine and natural spirit, one feels good around her.  He himself is pale, apparently bad heart trouble (since he remained the whole war \WTF{d.u.}{d.u.}), of a lively, fresh, amiable type, I like him more every time we are together. There is a lovely tea-table, electrically-lit, at the warm oven we almost finished off the heavy homemade torte, it went off very nicely and cheerfully. We talked shop gossipped a bit -- \?{the severe poverty of the Beckers has struck the Neuberts as sad as well}{auch Neuberts ist die schwere Armut Beckers traurig aufgefallen}, otherwise he told about Jordan, whose wife had become emotionally disturbed and was in a sanatorium, of the tribulation of his lecture before seven listeners on the Provençal, of books, of Paris, etc. We were both animated and satisfied when we left at 7. -- \missing

A remarkable fluke: the nameplate next to the Neuberts reads \textit{F. Mack}. The editorial editor at the N.N. who \?{was laid up sick in the summer}{der im Sommer aufgegeben krank lag}, now healthy, but has gone entirely gray (is the same age as me), 2 friendly children and a rather meretricious wife, former soubrette...this morning I spoke with him, introduced by Harms, about the N.N. Even Kopke, who I never trust much, was there. I have brought back quite a big impression. I have become less free with respect to all these people since I want something from them. Perhaps I am too sensitive. But I sense, at least with Kopke, uneasiness, \WTF{???}{Wegbeigelüste} a priori. Harms says: send us political and editorial reports. Kopke: we have two correspondents in Munich, one political and one non-political, and \WTF{as soon as they get too verbose, the wastebin looms}{sobald sie ausführlich werden, droht der Papierkorb}. I likewise had the feeling: if only you would go there! I arranged with the hopeful Mack that I would write him occasionally about topics other than the theater and visual arts, he would instruct their theater correspondents, in their absence, to rely on me, he will send me books to discuss. (As if I could find the time for that!) I went home with a quite bjtter aftertaste. --

\missing

% aber Kritiker sagen