\header{Sunday evening towards 7:30, January 18th 19.}

Yesterday for tea with Scherner, went there and back. Harms also came. The Neuesten Nachrichten suffered from yesterday's attack; yet Harms praised the fact that the big machines were left undamaged. The German workers still have respect for that. But pictures were smashed, a chair slashed up, scattered typefaces -- \?{it had been professionally led}. --

Today a strike in Leipzig, a procession of teenagers, they evem searched for officers' epaulettes in the Merkur -- all in honor of Liebknecht...another topic of conversation yesterday evening was the scientific critique of the old testament. Harms, a dillettant in the field, stated that the Jews were descended from Bedouins, \?{the patriarchs their household gods}{die Patriarchen ihre Hausgötter}. \?{Isaak would mean "he laughed"}{Isaak heiße "er lacht"}, and must have been a gruesome god. The whole morning it was going through my head, I said to myself, counting backwards from father to grandfather etc etc, there could hardly be 200 people separating me from 5000 BC. I would like to have this company from Bedouins through the ghetto Jews up to the present day lined up before me! What an image -- if only I had made a verse or ome other sketch out of it earlier!

On the way home I said to Harms: "Was it your honest belief that I was under consideration for a Parisian newspaper post?" He: "Certainly -- it just comes down to your personal connections. Perhaps through your brother? Or through the Munich Neuesten?" I said simply that we would see and changed the subject. Hope was finally buried.

\missing

% skampranov
