\header{Wednesday morning 1/2 8 May 7th 19.}

The first thing one hears in the morning: whether the electricity will be on. Today finally yes again, after so many days of strikes and unrest. Mail service to Northern Germany is still completely lacking...Yesterday afternoon, went to see the deputy dean Rehm. Freiher von Bissing is in hiding, since he has already been a hostage once. I put in my request for the one-time \?{war bonus}{Kriegszulage} which the Quaestor discussed with me. Rehm said that the semester would start on June 15th at the earliest, probably entirely cancelled. The students are being recruited desperately. Even with the preparatory courses there will not be very many, since the Hoffmann ministry is allowing anyone who joins the Freikorps to take the matura. The consequences for me: financial bitterness; even our Summer travel plans (Tubingen) are probably thrown out. And then I lose the stimulation of teaching, and the title of professor might again be delayed...I immediately dropped Biré and took up \textit{Article Genève von Dor. Neumann}, which I am to speak about. -- Faculty meeting tomorrow afternoon, reflection on the situation. --

In the city, recruiting and display of military might. Troops with music, yesterday Bavarian riders through the Victory Gate, bands on horses. The mood of the people seems to have already swung around. Gruesome Prussians and reactionaries... Landauer is actually dead. It is said that he wanted to give a speech at his arrest and was beaten with rifle-butts. Hans M and Weckerle still have not been arrested. --

% promised me.  gomer