\header{Wednesday evening towards 11 o'clock 28/May.}

In the morning, with Eva at the old Pinakothek. Saw \textit{Die Trionfi der Schule by Mantegna}. Five small oil paintings: Triumph of death, of love, of time, of eternity, of purity. In each, the triumphal chariot in the center, for death a coffin-like box pulled by oxen over bodies, a skeleton on it, otherwise with those round towers which in Leipzig carry the flowercarts on broad planters at funerals. Roses or elephants or angels or unicorns in front of them, upon them and at their sides allegorical forms, an apparently ancient Christian assortment, not clear to me in all points, behind them wide landscapes, rocks, hills. Eva suggested Ruhm for the purpose of my lit. hist., since he was the most colorful and characteristic for the renaissance. As for its content, just this image is indecipherable. The clearest was death, with the bodies smashed under the heavy cart. Peculiarly, the blood-red angels' bodies, forming tiers over one another on both sides of the white-bearded God the Father, \WTF{pulling the angel in the triumph beatitude}{den Engel im Triumph der Seligkeit ziehen}. \WTF{I get much more from that when I see so few details in the Pinakothek}{Ich habe viel sehr mehr davon, wenn ich so ganz wenige Einzelheiten...sehe} than when I search through all the halls. But I would need hours in order to take in this Triumph. --

On the way back we saw in the courtyard of the Turkish Barracks the volunteer lecturers practicing. Rehm, the Ordinarius and dean, in a common jacket with a gun, Hellmann, the gray-bearded professor, a wingman at attention...In the city, Eva reported, barbed wire, barricades and cars with machineguns are popping up; it seems that a 
ttle is again imminent. The university, Dr Janetzki told me, is supposed to have a sign up accoring to which students serving with Epps only \WTF{have to attend lectures}{gelesen werden dürfe} weekly from Monday until noon Thursday. That would mean a disruption of the whole program, a collision of many lectures and the ruin of the semester, which is already in trouble without this.

I tormented myself the whole day in the reading room with the French university lecture. \WTF{The best material that I once again got hold of, so-to-say instrumental works, which I should have already known for a long time and was not very far away}{Das Beste dabei, daß ich dadurch wieder einmal Material zur Hand bekomme, Instrumentwerke sozusagen, die ich längst kennen sollte und nicht entfernt kenne}. Haas's "Frankreich Land und Staat", the Minerva handbook, the pedagogical lexicon by Roloff was at Herder, Freiburg. I have taken a lot home, \WTF{since tomorrow is Assumption}{da morgen Himmelfahrt}. Also, a book from the University of Paris and a lovely piece of propaganda from this university in 1918. I learned all kinds of things today.

\missing
% forcibly catheterized