\header{Tuesday afternoon May 13th.}

Yesterday morning to the dentist with Eva, great suffering for her, for me none at all. But in the evening began the pain which made me quite miserable today. I am just now coming from Stûttgeh; he helped me a little with an expansion of my root-canal. As soon as the inflammation is done, this root is to be removed, along with one other from the interrupted front-teeth as well. --

Because of the delays with the dentist, and since the recension became longer than I had thought, I have only readied the Lafontaine report this morning and have now sent it out, together with the Genève article, to Neumann. At the dentist, I started Burckhardt's lecture "Culture of the Renaissance". It seems to me like one of the books that one knows without having to read, since it has passed into the public domain and is used by everybody. It shall serve as the prelude of my study of the history of Romance literature...Today I will also be done with the reading aloud of the horrible "Terre". That is no longer realism, it is an exaggerated horror story. --

Letter from Harms. On May 9th he had received all of my registered letters, the whole revolution diary; he will have it copied and give me back the original. Perhaps a part of it can be published later. Anyhow, I am satisfied that the manuscripts aren't lost. Hans included with them a series of his own editorials on the cause of the war and the current situation. He is \?{a believer in power politics}{Machtpolitiker}, without being asocial, reactionary, anti-semitic; conservative-social, All-German democratic. I was glad to read yesterday that Leipzig had been taken by surprise by government troops before the Räterepublik could be proclaimed. -- From mother, a card from May 10th; things seem to be going well for her.

\missing

% burgerlich