\header{May 6 Tuesday morning}

I am tired since we sat until 12:30 with Reyersbach, who again showed off drawings, and Heilbronn. Beforehand, Frau Dr Sobat sang. Ritter is very seriously sick. At 11, a short violent hand-grenade and gun battle somewhere in the immediate vicinity; I looked out the window -- a bullet whizzed by terribly close. \WTF{Like in Aubers at the observatory}{Wie in Aubers am Scherenfernrohr}. -- The Deutsche Bank was still not open; I must try again today, in order to mat Frau Berg. A strange procession through the Ludwigstrasse. Between big luggage cars, small \?{hand-carts}{Kinderhandwagen}, machine guns on them packed between knapsacks. All decked out in flags. One even sees Black-White-Red...an automobile with cool soldiers sitting on it, guns on their knees. Others laying on top of it on their stomachs, revolvers at the ready...A truck pulling a piece of artillery behind it...wagons with machine guns...All that at all hours on all streets. --

In the library's reading room I furtively read an essay by Hofmannsthal about Hugo in the collection "The Poetry". It didn't give me anything new. I went further into Biré. \WTF{I still don't have the whole story}{Die ganze Geschichte will mir noch nicht flutschen}. Also, I do not know at all whether this semester will come off. Contradictory rumors are going around, and there is again heavy recruiting for the Freikorps. -- Read more of the frightful "Terre". -- A registered letter to Harms and Kuchler was accepted at the post office. I myself have received no news at all; even the newspapers here have become almost entirely local stories. -- Landauer is said to have been shot "while attempting to flee
, \WTF{one should otherwise proceed very carefully}{man soll auch sonst sehr schroff vorgehen}. I saw none of the Meyerhofs yesterday. We sat with Pontius in the afternoon at Stephanie, where we have become regulars.
%  Frankly Ted