\header{Sunday night towards 12 o'clock. 24 May.}

\missing

Today was doubly encouraging. In the morning I spoke with Muncker. "You will not sit for long in Munich." In the evening for the first time in weeks, \textit{Vossler}. Stimukating and encouraging as ever. I should constrain myself to my big literary history, and not split myself; there will very soon be a small university free for me, since in the upper regions strings are being pulled and there is not an abundance of new blood. His own plan of work: how the language of philosophy (G. Bruno), how religion (\WTF{am Vulgärlatein zu erweisen}) moves forward. Deepest romantic. I said that language was the only place where the peoples' mind, the peoples' soul is found and can be grasped. "\WTF{Which you use to write verse and to think}{Die für Dich dichtet und denkt}" -- but Schiller did not foresee how deeply romantic truth was given with it...Strange, how Vossler lives on a single idea and \WTF{increasingly spins out from it}{immer mehr aus dem einen herausspinnt}. \WTF{Language, the spirit of a people, nourishing the individuals, fed from the spirit of all}{Sprache, das Geistige eines Volkes, den Einzelnen speisend, vom Geist aller gespeist}.

In the morning (when I spoke to Muncker) a recruiting meeting for lecturers. Rector Mueller and Lt Col Herrgott, a nutcracker face in a field-gray uniform with red stripes and a revolver. Dashing and militaristically humorous. How infinitely much has the military tone changed! We are implored: come! We are thanked for the honor of being able to speak with us. Every consideration is promised for age, social position, professional work. Every individual is courted, every individual is complimented. Up to this meeting there had been some 60 lecturers and assistants enrolled for the three-week training course, some 40 (among them, me) in the emergency reserve, as habing been under fire. After the meeting, another dozen might be added to that. The participation is not large. Herrgott humorously excused himelf, he didn't have a special dressing room for Herren in the barracks. I got a "\WTF{recruiting pass}{Werbeschein}". At some point I will be summoned to training.

Georg wrote. He again urges me to renew relations with Berthold. -- Teubner wrote: He finally rejected the Corneille. He proposed a booklet: French drama from the beginnings to the present. I also accepted that. -- Meyerhofs came to see us on Thursday evening. There was music. Ritter, Gehmacher, Sobat were there: Elena heard nothing at all, and was afterwards very unhappy about it. Today Hans gave me a lovely 7-volume set of Montesquieu's output of the 1800s, which he had seen at an antiquarian's for 5M. -- Vossler brought the painting of the Triumph of Petrarca which is hanging in the old Pinakothek, and which has come into consideration fof the \WTF{cover picture}{Farbentafeln} of my literary history. I will see it in the morning.

The semester is now supposed to start on 6/16, and so I will go to the readings on Tuesday. At the dentist recently I read with much satisfaction the Légende des Siècles. Incidentally the tooth has been rather tormenting me again, and I am di nuovo swollen.

% zonk