\header{Sunday morning 10/May.}

\missing On Thursday, a meeting of the wider philosophical faculty, section 1. This time it began reasonably: Rehm (Bisisng, as dean, kept nervously holding himself back) gave an overview of the situation: the essential thing, and the most awkward for me, is that the semester begins on the 16th of June and will last until the end of August. There is to be a student assembly in the auditorium maximum at 9 o'clock to decide about that. \WTF{I am goinf there}{Ich gehe hin}. Then he told how the revolutionary college council behaved, how is arrest had been debated in the senate, how the judicial authorities had differing opinions about it...I described that in an article for the LNN...Thereupon followed more speechifying from he professors, that the people arrested, that publications would have to be made, although this was already regulated and our faculty was not especially concerned, that I fled in disgust after 5:30, although the actual agend had not been toched on at all. A heap of unbearable chatterers and blockheads. One, who especially wanted to be heard and took himself especially seriously is the \WTF{old, bent-over}{altersgebeugte} steely-gray Grauert with the squirrel head. This time he chattered before the beginning of the meeting: whether, since out meeting was reported to the high command, we could be arrested under military law and be shot by \WTF{fantastic}{tollen} soldiers, like the poor 21 Catholic fellpws were recently. It must first be made clear to the chatterers that we, as the faculty, sit together in an official capacity. --

\?{We now only receive sparse long-overdue reports}{Es kommen jetzt erste spärliche lang abgelagerte Nachrichten}. \WTF{My and Eva's mothers sent cards}{Meine und Evas Mutter schicken Karten}, dated the 15th of April. Courtesy copy of the LNN with the article from the 8th of April, which I just read here in the university. -- \textit{Kaeser} was with me and said that \?{the Velhagen and Klasing edition of Lettres Persanes}{die Lettres Persanes Ausgabe bei Velhagen & Klasing} was out of print. I have now written to Weidmann. I have had nothing from him, so I must probably give up the lecture. \?{Moving into France is now too expensive}{Denn aus Frankreich zu beziehen ist jetzt zu teuer}. For the copy of the LP, which cost 1.50 francs, Kaeser had to pay 8.50M (Correspondingly, the lucky Stefl obtained 500-1000M royalty for a \WTF{special issue}{Stiftersausgabe} at a Swiss publisher, who had promised him 400 Francs). With \textit{Seebass}, finally discussed a little Montesquieu volume for the fruit salad. I am to get 600M for it, also the publisher will pay for the Histoire véritable, which I ordered the day before yesterday, and which now will probably cost 50-70M. (Seebass was here the day before yesterday.) --

Yesterday evening, when Eva became so suddenly sick, Stefl, \textit{O. Crusius} (who had completed his state exam in order to follow his inner urge and to write a paper on the relationship between science and art, since he is enticed by pure aesthetics and philosphy) came by and, in his thoughtful way, played a bit of Bach while Eva laid on the sofa, then Reyersbach and Heilbronn, who is idealistically socially-minded, and with whom I spoke much about thr insane conditions of peace, and Dr Ritter and Frau Sobat. This one, 50 years old with gray hairs and false lighter streaks in between, kind and good-natured, recently told us with naive humor about their destiny. How she was taken in at 18 by an illiterate sculptor, with whom she had a male son; how she was divorced after 5 years, wandered throug sanatoria, \WTF{in White Hirsch}{im weißen Hirsch} met a Serbian lawyer Šobat, married him despite warnings, was caught in the treacherous situation in the Balkans, was divorced again after 5 years, and has now had enough. -- Today I will write about the student assembly for the LNN. After that I will get into the Cordemann dissertation on La Fontaine. Then perhaps read from Burckhardt's Culture of the Renaissance, before I get back to preparing for class again. I am quite unsettled by the change in the semester; I would have liked to have had \?{concurrent months off}{zusammenhängende Ferienmonate}. --

%Velhagen un