\header{Monday morning towards 7 o'clock 26/May 19.}

The whole morning, before supper, before going to sleep -- I spend every free minute concentrating on Burckhardt. I finally wrote the last lines at 11 o'clock. Almost 24 pages excerpt. I have been focused working on it since May 13th. Only as I went through the work with pen in hand did I find behind its cultural-historical \?{details}{Einzelnotizen} (in which the \WTF{initial condition}{Urauflage} is poorer than Geiger's \?{extension}{Erweiterung}) the overflowing spirit, \WTF{judgment}{Urteil} synthesis. The book has a whole literary epoch \?{on its conscience}{auf dem Gewissen}. It gave me the foundarion for my great work.

\textit{Vossler} told how Geiger asked him to contribute to the \WTF{tenth edition}{10. Auflage}. Vossler declined: the book emerged out if a series of cultural-historical research reports, was now an artistic work whose first edition was now increasing in value. Geiger \?{printed this letter in the foreword to the 10th edition}{druckte diesen Brief in seiner 10 Auflage, Vorwort, ab} and repudiated it; Vossler expounded in his essay on logic. (I have Geiger's 9th edition here. He watered down and smothered the thing by a hodgepodge addition of \?{notes}{Notizenmaterial}).

Vossler stressed to me many times: hatch \textit{one} book a year, not many little ones. The stupidest collegues always note whether something is honestly worked on or was winged; Spitzer's and Kuchler's split was not important. (I am gradually learning names and places and \WTF{types of hungry novelists}{Art der mithungrigen romanischen Mäuler}. There aren't too many, but there are also few posts)...How even V has difficulties in bringing out his books: this Winter he is readying his Lafontaine for the presses, is going without royalties...He told of Wolfflin: as Burger, who fell in the Verdun, went into battle with Kutscher, W said: "Herr colleague, these are both coming again!" After Burger's death he told the students that this was a great loss for science, since it could not be guaged how and in which direction he would have acted. (\WTF{???}{Obwohl doch schon vieles von B vorlag!}) --

\missing

\textit{Evening, after 11 o'clock}. The walk to the dentist through the Hofgarten, twice a week in the morning, is actually the only way we have been able to enjoy Spring. Lovely are the Italian Colonnades in the park, the old gun barrels in the grass right in front of the Army Museum, the modern field-gray bustle of the crew ther with machineguns and automobiles, the creek further behind. -- \missing

I wrote to Berthold, rather coolly, only outlubed my situation here, pessimistic... Then a letter to \textit{Pontius}, who is leading the most joyful mercenary's life in the Freikorps Wolf. On a picture postcard from Augsburg -- he was meanwhile in Lindau and elsewher -- he wrote: I bought myself a Baedecker.

\missing



%d this  david limbaugh lips