\header{Sunday morning 17/May 19.}

Yesterday was our official anniversary, and, as a pre-celebration for June 29th, we \?{enjoyed it in style}{ganz hübsch zugebracht}. Eva got some flowers, an orange (now a delicacy for 95Pf!), and a few music-science books. In the afternoon we went from Stephanie to Grosshesselohe and went down to Hellabrun and back. The Spring day (with the Alps visible and lots pf water in the Isar) wa already quite lovely, but the trip was too long and we yet again bemoaned our misfortune at being tied to the always-unsympathetic Munich. Especially \WTF{since Eva lost her Piano}{seit Eva die Orgel so sehr vermißt} we have been depressed. After eating very tired, once more to the cafe, and then to Meyerhof's for a bit. -- On Thursday morning, I proved able to be of service to him. An older detective and a younger, very forceful one came to see us while we were eating breakfast, \WTF{and showed themselves around}{ließen sich gleich herumführen}, but they were very kind. I said: You are certainly here for the Meyerhof affair and immediately began to explain. About my conservative reports for Leipzig, of my conversations with Landauer, of Hans's political un-interesting-ness: he was harmless, adventurous, he had consorted with people of all political policies, he wanted to go back to Palmero as a merchant, and would have to be instructed about German movements. \?{The great enmity for Levien that drove, also Landauer and Weckerle}{Die große Levien-Feindschaft der bei ihm Verkehrenden, auch Landauers, Weckerles}. So all these people stood in the light of his enthusiasm and violent opposition to Levien. That is certainly completely true. However: I could have colored my statements much more distressingly with just as much right at least against Weckerle!... \missing Yesterday morning, even before breakfast, with \textit{Rothenbücher}, who received meas a friend and \WTF{introduced me around in his matter-of-fact way}{in seiner sachlichen Art orientierte}. The Volks-lectures are stillnot yet fixed: in this semester there are only a couple of evening lectures on finance, natural sciences, medicine. There are imminent plans for, in addition to the university, technical school and the business school a proper Volkshochschule with readings, \?{work-courses}{Arbeitscursen}, more general seminars. Very possible that I will get, in one form or another, a teaching position or lecturership there. The path is certainly not closed to me. \missing

The political situation is totally murky, from inside and out. What shame here! First it was threatened that all weapons must be turned over very soon; now a reward is offered: for one hand grenade or 100 bullets, 1M, for a gun 5M, for a machinegun (!!!) 25M. And the baiting of "Prussians" goes further, and people might enter into the \?{militias}{Einwohnerwehr} who formerly belongedto the red army. O Hoffmann Ministry! On the other side, again into antisemitism...Yesterday a note from the rector, \?{Docents could, in order to set an example, join up with Epp}. The Lieutenant Colonel Herrgott wanted to personally speak with them and direct them to posts \?{as had been promised to them}{wie sie ihnen zusagten}! Eva said very calmly: compare this request to the appeals before the revolution. -- What shall become of the peace, I cannot picture at all. Thus I live, expectant, surprised by nothing. Very characteristic here was a recent ad for Prussians, it asked them to not send donations in edibles, they would be supplied. --

I still have much correspondence today. A telegram from Scherners arrived after 4 weeks: "very worried!"  The dispatch went on 4/22 to Frankfurt, and it remained there, then was briefly sent here, then a letter from the old Meyerhofs: Erich, with his whole family from Shanghai, is with them. He was probably there for 12 years without a break, while we lived in Oranienburg his wife visited us; he now has three children and hopes to soon go back to China...I must also write to Harms. \missing
%e\?{militias}reatnth kannst du ziehst much wo die Pampers ist?