\header{Monday morning 1/2 8 May 5 19.}

Yesterday at noon I was visited by Behle, the graying, quiet politicall-bourgeois friend of the Meyerhofs, a Wurtembergish bookseller from Palmero: Elena had just been arrested by soldiers with pistols drawn, but otherwise polite. Luckily he, Behle, shortly before (against H's will) had taken away a half-dozen revolvers and destroyed some papers, political as well as black-market related. The arresting officers had a list which \WTF{had people associated with H}{der bei H. verkehrenden Leute gehabt}, which also included my name...So now I reckon on my own arrest, imagine explaining myself as a correspondent for the LNN, and informed Ritter as well (whose blood poisoning of the hand has worsened and has already required a third procedure). After some advice, chatouillé par l'aventure et flairant des matières nouvelles, I went out with Behle to see Hans M at the hospital, \?{out in Bavaria}{draußen an der Bavaria}. On the way we spoke a lot about Hans, how he had gone rather bad here, and how the fanatical Weckerle, who incidentally is said to be wanted, was a bad political influence. I have painted a picture of the street in my revolution diary which is essentially correct. Only some cannoneers were added to the cannons on Goetheplatz, and I added some detachments of troops -- if I had changed nothing, there would only be infantry and artillery onnthe Goetheplatz. But as I said: overall everything is absolutely correct and not exaggerated...the Israel Hospital, looking like a villa, is small but elegant. Everywhere in the staircases, plaques for founders with stars of David (Jewish?). Hans is in a small room, which contained only 2 beds and one patient. Very pale with a very red beard, but already recuperated. At his bedside, like an evil demon, Weckerle. \WTF{Most unfortunate band of soldiers}{Elendest Soldateska}, mismanagement, general-staff ofdicers, capitalism, etc...Immune to reason, dangerous. Hans was agitated and \?{forced himself to be calm}{gezwungen ruhig} when he heard about the arrest, he handed over his Spartakus membership card to Behle, which he staashed in the closet. Weckerle went right out onto the street "in order to not be arrested here". Then later he wanted to go home. Hans spoke with his people mostly in Italian; I could understand everything, but German is more familiar. -- At 8 Behle came to us with Elena: she had been freed after much not-impolite questioning. There was a denunciation, they had threatened "to shoot down the Whites down to the last bullet". Hans was incriminated. Good at least that Behle had turned over his weapons. -- I was home again at 5. Then at 6 went for a long walk with Eva down to Stachus, showing her everything. There were shots again somewhere, and someone brought wounded out of a house into an ambulance. -- In the evening, Pontius arrived as well. He has joined the Freikorps Wolf and travels to Augsburg today. He had met Frau Eisner in front of Meyerhof's place, who was first arrested, then set free.

Read a lot of La Terre aloud. Frightfully raw and plodding and one-sided. However, still always brilliant scenes. Read very little \textit{Biré}. Wrote in the revolution diary.
