\header{Sunday morning 7:30. 15.III.19.}

Things are going better for Eva insofar as she is fever-free for the third day, and as the gland-abcess is localized in the neck. But she still lays down for the vast majority of the day, wears bandages, has pains, is hindered in her motion and \?{has bad nerves}{mit den Nerven herunter}. \missing -- \textit{Dr Ritter} has treated us well and in a friendly manner. Through him I obtained a view into Catholic circles, who are not fanatical, rather very secularly and economically oriented, but who nonetheless hold firmly onto Catholocism and the church with hearty conviction and \?{self-evidence}{Selbstverständlichkeit}. Yesterday he spoke very calmly of the "\?{Path of sisterhood}{Schwesternweg}", \?{to obtain a little hospital}{ein Krankhäuschen zu erlangen}. The operations sister looks into the matter; if she finds the doctor to be suitable, she speaks with the mother superior; now his character is being observed, and if he is accepted, he will become the leader. Naturally he would not object if the sick receive communion...at the same time he spoke enthusiastically of the devotion of the Catholic sisters. But then he adds very matter-of-factly: one must watch out, lest these sisters intentionally over-exert themselves (mass after the night-duty) in order to quickly get into heaven, and their strength is needed on earth.

After 12 days of general strike, since Tuesday the Leipziger NN is appearing again: with the exceptipn of the article that I wrote on the day of Eisner's murder and a postscript to it, everything is lost or outdated. A shame, especially about the "Dear Pharmacist"; it had \?{bite}{Schwung}.

Every possibility of doing my own work, with the exception of putting together the lectures, is taken from me. Winter sent me two powerful volumes by Korff: Voltaire in Germany, which I want to show to Behrens; I still haven't \?{opened}{aufgeschnitten} it. I finished reading Daudet's "King in Exile" aloud and began "Fromont jr and Risler sr". Both unfortunately German. I took a page of notes on it.

\missing

%