\header{Thursday towards evening 20/March 19.}

Eva was aleady at Stephanie 2x, \?{of course still sneaking around}{freilich noch schleichend} I have also already once again sat in the work room -- but now E complains again of pains in the joints of her feet, and thus worries are returning. -- I have now pushed onward to the middle of Molière in the lectures. \WTF{I drag myself further in the courses}{In der Cursen schleppe ich mich weiter}. If only I knew more of French grammar. -- On Tuesday evening, went with Lerch to see Vossler, who now, naturally, has a more intimate relationship to L than to me. He was recently like a master among his students: I announced the dedication of my literary history, and Lerch \?{presented him with a typewritten column}{überreichte ihm maschinenschriftlich ein Feuilleton} that he had written about V. I know too little: the whole Vosslerian language-philosophy and -theory is foreign to me (with the exception of his history of the French language, which I reported on without having entirely understood it).

Yesterday evening a bad clash at dinner. A newly-added \?{medical representative}{Sanitätsrat}, fresh smug Jewish actor's face, fat fifty-something, publisher of some medical paper \WTF{here with Lehmann}{dahier bei Lehmann}, spoke in a wild manner about the German shame. Nothing had been achieved in the war, the Germans were all dishonorable, servile, etc. I came at him frightfully hard, and finally left, slamming the door. He then asked for a different place at the table other than directly across from me. It was especially hateful that Pontius appeared to approve of the revolting fellow, and Klein, the dainty, correct, quiet lieutenant and student at the polytechnic, also found no word of reply. Dr Ritter, who would have certainly intervened -- the guy said that all German businesspeople were dishonorable, and Ritter's father is a merchant -- was absent,