\header{Sunday evening towards 10 o'clock. 1/III 19}

\missing I held my reading at 3 o'clock in the afternoon: Corneille's comedy. (Eva scolded me that it was \?{too broad}{zu breit}). Then furtively prepared for the German preparatory course in the working room, since the university was suddenly closed at 6 o'clock. There had been a putsch in the city. Arrest of Levien by soldiers on the instructions of the Majority Socialists, afterwards released. \WTF{A low-flying craft}{ein tieffahrender Flieger} scattered fliers against the Spartakists over the streets. At home Eva said that Stephanie had been suddenly closed... but after eating we went out again with Pontius, \?{Stephanie was indeed closed}{da war zwar Stephanie zu}, but across from it Glasl was open. \missing

In the morning to the bank, also 65 M from the mail, the first payment from the Leipziger NN. In Leipzig, incidentally, a total strike, also counterstrike of the bourgeois. Everything is crumbling, god knows what will become of my articles...then the work room. Afternoon Hans M, Stephanie, finally once again 2 hours of the German preparatory course.

--Walzel wrote me, I might sit down with \textit{Lommatzsch} and \textit{Heyss}, who could \WTF{discuss Latin with me}{mir die Romania behandeln}, L the older, H the modern. From Lerch I know that L is the inheritor and publisher of the \WTF{50,000 pages of Tobler}{50000 Toblerzettel} and that Heyss was transferred to the Dresden Hochschule because of a modern book, I believe one from Balzac. I wrote to both. Wrote extensively to Georg. --