\header{Friday evening after 8 o'clock. 28/III 19.}

The classes cost me most of my time; but I have brought the 17th century (and only that!) to a good conclusion. I now have the \WTF{list of writers}{Liste der Inskribenten}; it has become 41. The day started with reading the paper, I took a break, \WTF{asked that the paper to be taken away --  it was done under the stomping in the auditorium}{bat das Blatt wegzustecken -- es geschah unter Trampeln des Auditoriums}; Vossler had been in an entirely similar situation in 1912 or 13...the young Spartakist in the preparatory German course came to me after class today e si spiegava. 20 years old, Austrian officer, purest idealist. I only held that against him: he wanted to spread freedom with despotic means. He said that was only a transitory state and it wouldn't stop at Bolshevism.

The Athenaion published wants to finalize the contract on Monday or Tuesday. -- \textit{Seebass}, who has now turned up here, was with us in the afternoon; he brought out a \?{fruit bowl}{Sammlung "Fruchtschale} and wanted me to take over a volume on Montsequieu. Translation and essay. That is however still far away and murky. --

\textit{11:30}. 6 classes that Lerch gave up at a private girls' school here were offered to me, since he is writing a literary history for Goschen this summer and got the Samson prize for his work on the future tense. Starvation wages, 75M a month. Borcherdt gives 20 classes a week at this school! If it had been only French courses, I would have accepted; but it came out that they were 3 French and 3 English. I have turned it down. Constantly oppressed by the close intimacy and shared opinions between Vossler and Lerch. Even in literature, where both judge things purely aesthetically...Yesterday I heard Vossler's second Lafontaine lecture. Today I told 

 students: I depended on this lecture in many ways, but also judged it differently, not onky aesthetically, but also humanly. -- Yesterday in the French prep course, where I still only have 3 students, an enthusiastic jurist and 2 neo-philologists, the young philologists asked me who they should hear in the next semester. I praised Vossler, praised Lerch as a \WTF{syntactic master}{Syntaktiker}, discouraged his summer courses (overview of the whole French literary history, for Goschen), since it could only \?{contain particulars}{nur Daten enthalten könne}, shrugged my shoulders about Jordan...Today a young officer turned up, who listened to me attentatively, 29 years old, was before the war doing doctoral work on medieval music, can no longer play with a smashed arm and has now become a novelist. I took him to Eva in the Stephanie; he will come to our musical evening on Wednesday. -- Lerch paid me a visit at 8:30; later I went to pick Eva up from the Ansorge concert; we sat there for a long time today and chatted with Dr Ritter and the harmlesw Austrian Fraulein Gemacher. -- Pontius has the whole table photographed together and gave everyone a print. We are gruesomely distorted...We frequently obtain provisions from the peculiar Frau Dr Sobat, mostly eggs, recently also oil and butter. It is appalling how much money we spend in this way. Frau Berg has increased our rate to 600M.
 
\missing% siwnce i cunce