\header{Sunday morning 23/II.}

We were shut in again in the evening. Before going to sleep we heard the crack of two hand grenades and several shots. The morning papers are still not back, the post arrived. Outside it is calm, the people \WTF{proceed}{urscheln} to the Ludwig church. It was strange how between them drove a truck with red flags, soldiers and armed civillians on it, casually urging \?{them to ready their rifles}{die zgewehre schußbereit}. --

Winter has declined my request regarding the editorship of the philological newspaper; he has already negotiated something else. The whole morning I read some of Lanson's Corneille monograph; it encouraged me, but quickly tired me. --

Yesterday evening the dinner group came here; the young Rhinish Dr Ritter, the two Bulgarian nurses, one of them \?{fine}{fein} with the loveliest dark eyes, the lively national economist from Nuremberg, the unlovely but jolly student of the \?{commercial school Centa Weiss}{Handelsschule Centa Weiß}. A bit of plucking of the guitar and singing, the doctor attempted an earnest \WTF{Wolfflied}{???} to Eva's accompaniment, the lovely Bulgarian sang the Heideroslein with a \?{soft, fine, high, tremolo}{leiser, schwirrender, hoher und feiner} soprano in a mellow foreign-sounding German with strong gutturals -- but on the ground the young people sat flirting together on the sofa, Eva sat at the piano, and I was alone. Young people are often awkward company for me. I feel that I no longer belong among them. It happened that one of them was honestly interested in conversing with me, until a second youngster came along; that same instant I was alone. \?{The girls were giddy about a party that brought them into our living room, the most splendid part of the flat}{Die Mädeln schwärmten von einem Fest, das sie in unserem Wohnzimmer, dem Prunkort der Pension gegeben}; the "red drapes", the intimate "\WTF{viscious corners}{lasterhaften Ecke}" were so atmospheric. Young people are happy to communicate among themselves like two-year-old children. The child plays with any object while it is new to him; \?{young people draw on every stimulus, since everything is related to their sexuality}{junge Leute ziehen aus allem Anregung, weil ihnen alles in ihrer Sexualität in Beziehung tritt}.

I have such a heavy heart: I am no longer young, I must somehow find firm soil under my feet. Philology does not give it to me, journalism either. I am alone, too old for the young, too \?{unarrived}{unarriviert} for the old.

% 