\header{Sunday evening towards 7 o'clock 9/February Berg Pension, Schellingstrasse 1}                                                                    

A large, elegant living room, actual dining room with a buffet, table, sofa, divan (but without a writing desk), heavy high plush chairs, thick curtains, carpet, electrical light, big tiled stove (which of course has not yet entirely warmed up against the momentarily-strong frost); a little bedroom, without a heater, thr beds not next to eachother, but otherwise friendly. The landlady is passable, the food is good so far, the little community is apparently nice. The whole thing will cost about 600M a month, I have to add about 300M to that for miscellaneous expenses. But yesterday there was a most pleasant about-face in my finances (see below: "Lectureship"!), and so I look towards the future more calmly, and feel safe and sound for a few months. A pause in our gypsy lifestyle. And since Eva is also settling in here, i.e. seems to have found her musical opportunity, and since I had already given up a few days ago the self-chastisement which finally led to almost complete impotence, the future looks better. And I can work again, and \?{the lectures are going well, and bring me to another time}{die Vorlesungen glücken und lassen mir auch zu Sonstigem Zeit}. It seems as if a time of deepest bitterness, \?{loafing around}{Leerlaufens}, the feelings of envy against Eva, the mental barreness, the financial want, is now basically over.

Yesterday morning in the \?{hall}{Aula} a celebration for the returning veterans. I met Vossler in magnificent robes before the senate room, he invited me in, \?{I "belonged there"}{ich "gehörte dazu"}. I was only in a jacket, \?{and beneath wore the misera plebs of the non-Ordinairus frock and medals}{drinnen trug die misera plebs der Nichtordinarien mindestens Gehrock und Orden}; nevertheless I went in and afterwards went with them in a solemn procession to the \?{semicircle of professors}{Halbrund der Professoren}; at my feet stood the standardbearer in regalia. The celebration itself \?{and Baumckers}{und Bäumckers} was not bad, but the speech was much too long -- I described it in the afternoon in a witty article for Mack, together with the Liebknecht celebration. \?{I was half-disgusted, half-envious}{Mir war halb übel, halb neidisch zu Mut}. The rector's golden chain and the fiery red of the judicial robes \?{glimmered}{funkelte anspornend}. Next to me sat Lerch, also in a jacket. He told me of a lectureship which Rehm gave to him. 4 hours French for the veterans who still haven't received their Matura. After eating -- Old Pinakothek, Hans M -- I went to Rehm, who lives in a villa on Montsalvatstrasse, by the Schwabinger hospital. Deep snow. I met him going out, we went together into the city. Friendly forty-something, little grayed-blonde goatee, Latin scholar, dean during my Genter Affaire. Very interested in me, and since he had heard of my \?{Germanistentum}{??}, he promised me, besides French lectureship, also a German lectureship. That will bring in at least 1000M, perhaps 4000M. \missing -- Late to sleep, late up. Worked a little on the lecture. D'Urfé is ready, and will probably be covered Monday and Tuesday. At 1 o'clock, community lunch. Then through driving snow to the Old Pinakothek, to the \textit{Isenheimer Altar}. We must still see it many times. Grandiosity of the bloody \?{decaying}{verwesende} Christ on the cross, the twisted, swollen feet, the \?{twisted wood of the cross}{gebogene Kreuzholz}, the blue-green lips. The Madonna in the rosebush did less for me. The mythical creatures of hell \?{were fantastic}{Toll die ...}. What a mixture of fantasy and realism! Magnificent heads in Isenmann's passion scene, Jewish types -- childish, stiff movements. \?{We wanted to go back there more frequently, like we did in Leipzig}{Wir wollen, wie in Leipzig, öfter auf kurze Zeit hin}. To coffee with Meyerhof. Unpleasant. Political differences. Above all, however, Elena's envy of Eva. We want to see them less.
