\header{Tuesday evening towards 11 o'clock. 4/II. 19}

This morning wrote a \?{quick article}{raschem Schwung Artikel} for Harms: "Munich Riddle". Half-political, what I saw and experienced with Hans M: on communism, on Levien, of Weckerle and the Italian journalist. Theme: The Bohemian politics here. -- Afternoon got the D'Aubigné lecture ready and began D'Urfé. -- After supper we wantes to go to see Harms and heard that Weckerle was with him. \?{So, I didn't go}{Da mochte ich nicht hinein}.  Cafe Stephanie, met the librarian Steffl, who is still not a doctor, \?{though a solid character}{dabei ein grundgelehrtes Haus ist}. 

\?{This morning a student Stossl enrolled with me}{Vormittags ließ sich bei mir ein Student Stößl melden} and politely asked me for advice -about re-starting his studies. \?{"They asked me in the Summer of 1915 how to prepare; you enlisted exactly when I, along with mybrother, went into combat"}{"Sie fragtem mich im Sommer 1915, wie man aufprotze; Sie traten gerade ein, mit meinem Bruder zusammen, als ich ins Feld ging."} Both Stossls are lieutenants. 

\missing

\?{The saddest memory of Berlin (to catch up a little bit) is mother's eyes}{Die traurigste Erinnerung an Berlin (um tropfenweise nachzuholen) sind Mutters Augen}. Lightless, \?{withered}{vertrocknete Kerne}, blood-red and with no eyelashes. Yet they still seem to have a shimmer, and also seem to feel reasonably well. I was received rather cooly at Sussman's, I also had a rather cool encounter with Georg, and with Felix it bugs me with that he rushed to a reconciliation with Berthold. \WTF{It was striking that Georg quickly and strongly came into my mind, to become a journalist, a Parisian reporter}{Auffallend war, daß Georg auf meinen Gedanken, Journalist, Pariser Berichterstatter zu werden, rasch und lebhaft einging}. Conceptions of honor and financial circumstances have rather changed. He spoke democratically in favor of a president, and Felix came out as a socialist. How different from earlier years!

% MOG