\header{July 19th 1924}

Today it is a year since Richard's misfortine in Schliersee. The day announced itself with thunder and lightning. Thought for a long time about whether he had not probably \?{chosen the better part}{den besseren Teil erwählt}. All that we have have aufferes in the last year in inner torment and national distress! And yet he had prepared a kingly end to his miserable earthly existence. Mea culpa were his last words. \?{My fault, all my fault}{Durch meine Schuld, durch meine große Schuld}. Is it not our greatest torment, that we bear blame, and to old inherited blame add new blame of our own? Do we not suffer for the sins of others, and sin further for coming generations? Where is the sense in these things? Where are you, dear departed? Why do you not give me a sign as to where we must go and what we must do to save ourselves? Have you gone into nothingness? Or are you preparing yourself for a higher existence? Or do you have to strain and suffer like us? Meaning in the meaningless? The solution of the puzzle? The oldest, never solved question. Richard, my good friend, source of my strength, help me further! Be a further sign and symbol for me. Do not let me despair! Lectures: "Discussions with Frederick the Great, diaries of the Herrn de Catt 1758-1760". A probably very witty man at the time is "\?{summoned}{befohlen}" by the king every evening. Conversations about the world, life, art, philosophy and poetry. Many \?{dull}{fades} talks on the French. Then the wonderful words of the king seep through. \WTF{They come through as humane}{Tritt einem menschlich nahe}. One sees him suffer and die. This greatest man fights his enormous battles during the day and converses by night with his friend on the immortality of thr soul, about god, about duty and the arts and sciences. The highest point of the Hohenzollern line. "Life becomes a disgrace and death a duty", he said with respect to a battle which is irretrievably lost. What a \WTF{fanfare word}{Fanfarenwort} into the ears of his unworthy descendents. Yes, a monarchy under the old Fritz, that would be the best form of state. But it is just an illusion. \WTF{Where is our great Fritz}{Woher den großen Fritz nehmen}? Such a man only appears once every 100 years in the history of the world. The \?{forms}{Format} of our present great Herren are drawves against his. "Life becomes a disgrace and death a duty!" Thunderous words of a giant! The booklet provides a deep, uplifting and shocking view into the workshop of a giant. This greatest warrior calls war only "drudgery". His ideal is \WTF{Sanssouci}{???} and a philosophical round table and and[!] flute concerts. He lead the war only from a sense of duty and as a service to his people. Great men make great times -- but not great times great men. \?{Ours belongs to the latter}{Die unsere gehört zu den letzten}. But the time only becomes great through the man. Alexander, Caesar, Barbarossa, Napolean, Frederick, Bismarck. How pitiful their times \?{if one were to imagine them away}{, wollte man sie hinwegdenken}. In the first place, time and man have an organic connection. If a great man is missing, then the time is not ripe. We look over the thing and perhaps call "great" what is wide without depth. It is not the extend of the sides, but rather the extent from top to bottom that is decisive. When our time is ripe, a great man will be brought. If we, in our ignominy, cannot reach your spirit, then indeed, "then life is a disgrace and death a duty". Yesterday afternoon prepared for a tryst with Else. Then Willy Kamerbeek came -- and remained until evening. One must still be friendly and give thanks for the visit. Why do we not speak the truth to people? Completely blessed hours in the evening. \WTF{The deepest human desir was tasted}{Man kostet das Letzte an tiefster menschlicher Lust}. One wants to shout, to celebrate, to sing, -- it is a desire to feel life. Tension, everything awaits in us the great hour. Every nerve burns. Blood throbs in the veins, thumps in head and heart. A mysterious power draws the loving bodies together and into one another. World and pain are forgotten. Instantaneous total forgetting. One rushes througs eternity. Heat, jubilation, madness. And then a silent hour, sated happiness. Nothing more is needed. Resting in the lap of eternity. \WTF{Life is still only an example}{Das Leben ist nur noch ein Beispiel}. Still and wise. And so one sits, arm in arm and cheek to cheek, long, long and waits for a sign from god. Your soul is as silent as the calm sea. Only here and there a light wind ruffles the smooth water. Then the desire will again sprout up in your blood. And then again the great stillness comes over you and you \?{tastet}{grope}[!] from step to step up to the throne of god. (4) The hour / Of great happiness / Is now past. / Still as the calm sea / at ebb tide / is your soul. / A light breeze/Only ruffles/the smooth water./Blood sings in veins,/You live, you live./And then again/The great stillness comes over you./And your soul/gropes/from step/to step up to/up to the throne of god.

% lol