\header{July 11th 1924}

I read Bebel's memoids partly with interest and joy, partly with an awkward feeling of \?{a lack of}{mangelnden} satisfaction. Its \?{untamed nature}{Durchgängernatur}, its courage and its steadfastness bring me joy. Its personal recollections are awkward. It sounds so high and self-satisfied and is in actuality so hollow and meaningless. Nor is there any pleasure in following his toxic effusions about Schweitzer. That is yet a bit plebeian. But that seems to be the way of social-democratic functionaries. (see Noske.) I am still constantly pondering the plan for a weekly paper in Elberfeld. In theory, everything works. We are only lacking 2000M in initial capital. But the Praxis, the damned Praxis. Beautiful Summer day! Heat like in Africa. If only I could get out of here, to the sea or the mountains. The sea would be best. The day's politics are a mix of \?{convulsions and piss}{Krampf und Seich}. France and England have united, naturally at the expense of Germany. Herriot is an underhanded rogue. I prefer Poincaré. MacDonald, the English premier -- aha -- an apostle of peace with an olive branch, English piety, man of \WTF{cants}{???}, in Germany we don't like that, mein Herr. I wait -- I know not what for. For something uncertain, but what? We always wait, we people. Until death ends out waiting. What courage I take from the smallest things. Things must already be totally bent if I lose the last bit of courage. There are people who are so mendacious that one can take away 90\% of their speech as untrue. One part of these people are pathological braggarts (Nölles, Herbert -- perhaps I as well), one part are mendacious liars (Paul Erich Hind..., who by the way is also a swindler and a rogue). What the people consider to be \?{culture}{Bildung} today! He can eat with a knife and fork, not belch in the presence of other people (when he is alone, he can do what he wants), makes a \?{cheeky}{chiki[!]} bow on entering: a nice, cultured man. The bourgeoisie is rotten and eaten away to the very marrow. The nobility could never fall this low. Civic awareness of the masses: don't exploit them so, and they will learn to love their fatherland again. I play a lot with little Elsbeth in the yard. A child is a wonder of god, that lets us forget all the pain and torment of the earth for a few hours. What deep wisdom: "unless you change and become like little children." We learn to cry and laugh again like the children! But children can sometimes be frightfully gruesome. Especially physical weakness and \WTF{unevenness}{Unebenheiten} with respect to other children. I know a little song about it. \?{But these are the childrens' natural drives}{Aber das sind die Kinder aus Naturtrieb}. Is nature not also frightfully gruesome? Is not the struggle for existence -- between man and man, state and state, race and race, continent and continent -- the most gruesome process that the world knows? The right of might -- we must once again see this natural law clearer, then we will lose all fantasies of pacifism and eternal peace. What pacifism you speak about today! You want the peace of the cemetary? The present world-peace is at Germany's expense. Could you speak of world peace when 60 million live in bondage? Will these 60 million not break their yoke as soon as they feel strong enough to do so? Why then do you speak of pacifism! Do we not want to return to nature? Is she not always our great wise teacher? Go and speak of pacifism among lions and tigers! Pacifism is always the \WTF{oil of meekness}{Öl der Sanftmut} of the victorious over the defeated. If I speak of eternal peace and rob you of everything but your shirt -- \WTF{God, there still those who believe my words}{Gott, es gibt immer noch welche, die meinen Worten glauben}. \WTF{Our reasoning sometimes goes down strange tracks}. But the heart still remains at bottom bound to the eternal mother nature. If I am stronger than you, what can I do? Go complain to your god! Or better still, seek friends to help you to break my advantage over you. One must above all simply think, otherwise whe will be led astray. There are eternal laws. There are not eternal laws. But eternal laws. Those are the laws of nature.

%.u