\header{Wednesday morning March 26 19}

I have no lectures on Wednesday, since one French class has been moved from Wednesday to Monday. That mesns I get a breather. Incidentally the French class is a double problem child for me: (1) it causes me grammatical difficulties and (2) I only have 3 students left, and courses with udner 5 participants are to be dissolved. I can probably still obfuscate the situation, since the numer of students is always fluid, and since the course conclides on April 12th. In any case, it is awkward. -- Even in the one German course there is some awkwardness. In order to explain Götz and Räuber, I said: this is the danger of the idea of freedom that does not coincide with \?{law and order}{Gesetzmäßigkeit}, that its purest proponents would find impure followers: Goetz in the Peasants' Revolt, Karl Moor his his robbers, -- the Spartakusbund. Then, as I passed out \?{notes}{Vorträge} for a future lecture, someone stood up: he had \WTF{accepted Goethe's Jugend}{Goethes Jugend übernommen}; but he was a member pf the Spartakusbund -- aslwd whether he might talk instead of about Goethe about the Spartakusbund...My generally strongly anti-revolutionary auditorium stirred; they stomped their feet heavily when I of course declined to change the topic. I did have to add one earnest request, to refrain from the political \?{rallying}{Kundgebungen}. \?{Then I felt in my soul that I presented the essay them "Freiheit, die ich meine"}{Dabei fiel mir dann auf die Seele, daß ich das Aufsatzthema "Freiheit, die ich meine" gestellt}. Of course, the Sturm und Drang lecture justified the choice of topic. Nonetheless...I would like to continue this German lower-level course over the Summer; thus all the awkwardness must be avoided here. -- In my lectures I am rather certain to not get to the year 1700.

On Monday \textit{Vossler} began a six-hour (Monday and Thursday) cycle on \textit{Lafontaine} in the Handelsschule on Herrenstrasse, for the Volkshochschule. As his student and junior I must sit through these lectures, evenings 8:30-9:30, although they will \WTF{presumably}{dem ersten nach zu urteilen} do nothing for me. Up to now \?{V has repeated to the point of redundancy}{wiederholt V bis zur Wortwörtlichkeit} what he said in that Winter lecture in 1912/1913, which I am not using so much, but which I also have problems with. It always comes back to the theory of the \WTF{courtly social coolness}{höfisch gesellschaftlichen Kühle}, the classical lack of feeling, against which I put the question about where then these cool normal people were in the 17th century, outside of Boileau.

\textit{Teubner} has answered my inquiry with much interest. In "\?{From Nature and the Spiritual World}{Aus Nature und Geisteswelt}" is organizing a series of famous authors, 2 or 3 each, but who would have to represent different cultures. Corneille and Racine ar eboth of the Louis XIV century, he wanted one of them and something besides. I will try to make the distinction between C and R clear to him and will propose a double-volume: Corneille-Racine-Calderon. (Along with that a little volume: D'Urfé-Lesage.) I need to add a Spaniard to my literary history anyway. Otherwise I am gradually becoming nervous that the Athenaion publisher \WTF{cannot see}{sich nicht sehen läßt}; \?{he wrote me on March 8}{er schrieb mir unter dem 8/III} that he wanted to personally conclude a contract within 14 days. Yesterday a friendly letter from \textit{Becker} in Leipzig, he has also been asked (after Vossler) to take part, \?{he declined because of "the hunt"}{er habe der "Hetze" wegen abgelehnt}. For me it went otherwise: if I was young, I would have \?{profitted from it}{aus der Durchackerung Gewinn} for the rest of my life, he also believed that the work "\?{depends on}{liege}" me. If the hours between work on the courses, \textit{Korff}. Lecture reading: \textit{Margueritte "Weltkinder"}.

Eva is still not \?{totally recovered}{hergestellt}; the rheumatic pains in her legs prevent her from moving and so naturally from going to her musical course.

I am not happy with my little success. With respect to Lerch and Vossler I always feel like the outsider, the unscientific, like I a
have become foreign, I always believe that I'll never be granted a professorship. --

My journalistic activity is completely asleep. The topic isn't on the streets anymore, and I need every last minute for my work. --

Eva's mother wrote a letter from which it emerged that he has completely succumbed to religious madness: fixed trust in god, revelations of the bible and the gospel of John, Kabbala. Anno 1919 and not born with a sick head, but \?{rather it is planted in a group}{sondern in ihn gepflanzt durch eine Gruppe} of faithful adventists!