\header{Wednesday evening after 11 o'clock 19/II 19.}

Early today -- Vossler told me months ago, I had long given up all hope, Walzel had inquired whether I wanted to undertake a a volume of 20 (encyclopedia) \?{pages}{Druckbogen} in the handbook of literary history, which is to be organized in many volumes by epoch and philosophical viewpoint: \textit{Latin literature from the renaissance through the French revolution}. I have agreed and am very elated...this afternoon the author's copy of my article for the Leipziger NN on the Bohemian politics of Munich arrived, under the heading "Politics and Bohemianism from our \WTF{A.B.}{??} colleague in Munich" two columns long, on the front page above the fold. \?{That also has me very pleased}{Auch das hat mir sehr wohlgetan}. My first political article. I have just spilled out my heart to Harms in a long thank-you letter. That two people live in me, homo politicus and homo doctus. They might send me to Paris for the L.N.N., so both would be satisfied. -- This afternoon at Hans M's I met \textit{Frau and Fraulein Eisner}. The girl is robust and red-haired, from his first marriage. The wife delicate, young. Both simple and unassuming. The wife spoke only rapturoudly of Eisner. Whoever listens to him is won over after three minutes, no one can resist him, farmers in the land and strikers had wept at his speeches!

-- As I came to supper, I heard that in the afternoon there was a putsch and shooting here. With a bad conscience (since I brought her into danger) after 8 o'clock I drove with Eva and Pontius to the station. It was blocked off by \?{guards}{Postenkette}, one could see two fires and (I believe at least) a piece of artillery in front of it. The track must continue without stopping until Stachus. There individual groups of men stood together, in the middle of which ther were always two people conversing or arguing, while the others stood around without knowing why. Only the street leading to the station was packed full. in the rest of the city, silence. We went to Stephanie. -- \missing