\header{Tuesday evening after 7 o'clock 18/March 19.}

Eva is constantly getting better. She usually eats at the table, \?{always has to be up}{darf...ständig auf sein} at noon and evening, but is still wearing bandages. We have celebrated her recovery con tanto amore. Nonetheless, I am still very much tied to the house, hurry to ready my lectures, and aside from that read aloud (Daudet). Sunday I allowed myself the first chapter of Korff's Voltaire in Germany. When Eva is again fully \?{back to normal}{in Gang ist}, i.e. has gone back to her studies in the academy, I will plunge into my non-lecture works: the Corneille study, Voltaire recension, which are moving in a similar direction, perhaps a chapter: Corneille and Lessing. For the time being, that has not happened, I only just get my lectures together.

I am in perpetual worry about my French course: there are only ever 4-5 people there and \WTF{and the little course is dissolving}{die kleine Curse [above, Kurs] löst man auf}; \WTF{so Lerch's German one must remain there}{so mußte Lerchs deutscher daran glauben}. Recently, in a survey, \WTF{I put forward an older attendance list and specified eight students who I haven't had for a long time}{legte ich eine ältere Bestandsaufnahme zu Grunde und gab acht Hörer an, die ich längst nicht mehr habe}. Today I saw Rehm, the organizor of the whole affair, in his philology seminar and asked him to let me run a lower-level French course in the summer. Only the lower-level courses -- thus my German one 

 run through July; the others conclude on Easter. \?{We will see that it is taken care of}{Er wirs sehen, es einzurichten}. Lerch had askes him \?{for the same thing}{um Gleiches}; for this purpose, a few \?{middle-school teachers}{Mittelschullehrer} must be pushed aside. We also spoke of the \?{incoming courses}{eingehenden Cursen}. He said that the government did not want to spend too much, courses with under 5, perhaps under 6 people would be cancelled. I lied: I had on average 8 atudents in the upper-level French coursd, naturally it changes fluctuates. It came out later that there had been fewer and fewer people. And the misery will no longer last forever. Until April 12th. --
 
Yesterday evening, Lerch and Rabinowitsch were here. He is always dissatisfied, always occupied by the demands of "the minimum for existence". Later Dr Ritter came to change the bandages. A religious conversation with him. He contrives to be a doctor and a Catholic. It does not hinder him in his medical duties. God is behind the cells. And why should he not worship him in the form that his fathers and forefathers held sacred? Did he have to believe the bible literally? -- No, but \?{miracles}{das Wunder}, the immaculate conception, the resurrection, all of that - yes! It was not difficult for him, it had comforted him in field. He spoke with quiet contempt of the \?{evangelicals}{evangelischen Geistlichen} who only ever brought "provisions" to comfort the wounded. He could not conceive how I could live entirely without the church. It was awkward to have to admit to being a protestant. Otherwise he would not have understood me at all.

This evening I want to go with Lerch for a while to Vossler's: my first trip out in weeks.

An \WTF{uncomfortably Jewish intimate letter}{unangenehm jüdisch intimer Brief} from Block, the comrade from Wilna. How distant! -- A friendly letter from Frau Harms, confirmed that everything of mine that is left from before the strike is outdated. --

%exld. pletive