\header{Thursday evening, 10 o'clock 27/II.}

In the morning a letter came from Frau Harms anf Kopke, in which the imprint of a new article is apparent (which I then saw in the newspaper room of the university: the first Eisner article had been merged with the first \?{supplement}{Nachtrag}, one word that I had sent to Harms \?{as a transition, "bei derer Gaudi", was inexplicably included}{als Überleitung mitdrucken, "bei derer Gaudi" sende man aufs Geratewohl}). That excited me so much that I \?{went right}{mit gutem Schwung...losließ} into a pointed new letter "My dear pharmacist", particularly directed against postal censorship. That took me until almost noon. I the prepared for my lecture, and held it at 3 after a one-week pause, \?{rather overlong}{etwas allzubreit}. In the university there is only one \?{gate open}{Spalt im Gitter offen}, there were two servants there controlling all entry. In the evening it closed already at 5:45; excuse: the trams stop soon. However there seems to be a fear of general mischief today, a placard indicates particularly strongly an implementation of a 7 o'clock curfew. It seems as if a feud between the Majority Socialists and the Spartakus is brewing. But it seems doubtful to me that everywhere in the reich communist revolts and strikes have broken out... \missing

I expectantly await Walzel's final answer. --

\WTF{The caretaker brought me 100M}{Der Pedell brachte mir 100M}. The first lecture money from the council, the first money earned at a German university.

% strenth