\header{Sunday evening towards 10:30. February 2 19 Munich.}

Today for the first time earnestly wrote the first lecture, 10-2 in the morning and 5-7 in the afternoon: \textit{Introduction and D'Aubigné}. I skipped lunch, met Eva at M's for coffee. Hans's friend \textit{Weckerle}, Spartakist, chair of the Soldiers' Council, writes in "Freiheit" and "Rote Fahne". Dictatorship of the proletariat. I am to dumb to understand it. Whoever votes for the bourgeois without being a capitalist, who doesn't feel like he is a proletarian, is an imbecile. Hans agrees. It repulsed me. \?{We want to distance ourselves from M}{Wir wollen uns von M's zurückziehen}. Then an Italian journalist came, who is here on an information-gathering trip. Weckerle, formerly a merchant in Palmero, explained himself fluently. He is not dumb, not uneducated, but fanatical, ideological, and absolutely self-confident and arrogant...my Italian is rusty; but I was still able to get out a smattering and understood everything...then a walk through snow-covered streets in the Hiltenspergerstrasse to Jordan. Nobody at home. Back to our hotel room. It is warm and well-lit. But otherwise unsatisfactory. Be both feel totally alone and impoverished in Munich, \?{we have longing in our hearts}{sehnen uns von Herzen fort}, we have no happy hours here. Tomorrow Eva is to play before the organist Becht i the academy. Whether she will find any possibilities of playing here depends on that, and \?{our lives here depends much on that}{dacon wieder wird viel für unser beider Sicheinoeben abhängen}. The collision with the bureuacracy when Eva enrolled there yesterday was tragicomic. Certifications of vaccination and good conduct were demanded, organ practice would be \?{about 4x a week, an hour each time, free}{etwa 4x wöchentlich je eine Stunde frei sein}. In truth, that is perhaps not so bad. Bavarian bureaucracy, miderates by Bavarian "friendliness", which is de facto \?{slipperiness}{Glitschigkeit}, unreliability...

A good supper in the "Old Pinakothek", a hearty brew, if not quite coffee, in the Cafe Glasl (\WTF{Stephanie was no good}{Stephanie taugt gar zu wenig}) raised our deeply-sunken mood. Over all, up to now we have been caught up in the most expensive, most uncomfortable \WTF{pumlichsten}{???} temporary situation.

Uncertain when I will find time to fill in the outline from January 28 to February 1. It's a shame, since there are all kinds of intersting details in it.

% freiheit, gleichheit, aller seelen!