\header{Thursday evening 10:30. 6/II 19.}

In order put a provisional end to the terrible hotel situation, today I have rented two rooms with full board on Schellingstrasse 1, after much negotiations, for about 600M a month, heating, light, maid included (550 fixed, 30 for heating on average, misc expenses). In the long-run that is too expensive, since additional expenses are added to it, cafe, laundry, Eva's studies, etc etc, and so if we remain like we have up to now at 900-1000M monthly income, then we must constantly consume the Sebba-reserve. Anyhow, that goes until the Spring, and until then we can probably find some cheaper accomodations...what else are we to do? We lived \textit{just} as expensively, and totally impossibly -- the hotel room is far outside of our part of the city, constantly in transit. Eva's nerves have died down, meanwhile mine have been shattered for the longest time. --

Today a lot of running around with the searching and renting, to see Hans, to the state library, to the cafe. In the morning I wanted to introduce myself to Matt, \?{who once promised me the title of professor}{der mir damals den Profesortitel zusagte}, and did not meet him, but met Vossler on the steps of the ministry. We walked a while together. He said that I would get the title of professor in the course of a year. He praised Lerch's syntactical ability, his work on \?{the future tense}{das Futurum}, strongly rebuked his journalism. Against that Lerch out in that he had to make a living. I myself want to write "\WTF{clamheimlich}{???}". This evening I was at a Liebknecht celebration at Odeon's hall. Gustav Landauer spoke, the \?{advertised music was cancelled}{die angekündigte fiel aus}. That, along with a celebration for veterans which takes place at the university on Saturday, should be enough for an article for Mack.  Landauer was a small, thin, \WTF{schwarzberocktes}{???} little man, black mane, blacker beard. \?{Preacher}{Predigtton} + Berlin jargon. Religious sounds + soviet radicalism. Religious \?{whimsy}{verstiegen}: immortality of the creating spirit within us. The godliness in men. Liebknecht was a role model. -- I got no work done at all today in the working room. The Friday lecture and only a part of the Monday lecture is prepared. I got all of the parts of the Astrée from the state library and schlepped them back to the working room. Incidentally the university also has the whole Astrée. I \?{won't take the lectures too seriously}{will die Vkrlesungen nicht tragisch nehmen}, hope to soon have the \?{tricks of the trade}{Handwerkstrick} worked out and so then find time for other work. --

In Berlin I championed Hansen's and Elena's cause before the now-aged Henri Meyerhof and before the unchanged Lissy, and believe that the ladies have gained from it. Later I met Berthold Meyerhof at the Potsdamer Platz, and he accompanied me along the Lutzowufer down to Beyreuthstrasse. He still wore a uniform, had long, sharp American features, an energetic American chin, has become manly and skeptical, very skeptical with respect to his oldest brother, very mistrustful of Elena. He said to me: "You regard the case too literarily!" I was almost a bit afraid of this secure 27-year-old, who I had known as a soft knave.

\missing
% flinty resolve, leaden blood