\header{Saturday towards 7 o'clock in the evening 22.II.19.}

On Thursday evening, after I spent the whole day sitting in the workroom and standing at the lectern (readings and two hours of Misanthrope), Lerch and his sister-in-law came to see us the evening. Sonja has arisen from the grave, only with her hysteria oriented to the right side. Anti-feminist, anti-revolutionary. Incidentally had started medical studies in Switzerland, now studies philosophy and music theory, besides that rhythmic gymnastics, has already (as she herself has said) tried out 50 occupations, spoke in strong jargon, has, like her sister, a tiny, so to say \?{twisted}{unentwirrbare} figure. I strongly suspect Lerch has turned to her for consolation. He himself grates heavily on my nerves with his perpetual proofs that I couldn't obtain any professorship, that I must be a proper learned linguist and that my literary history is only subjective dilettantism. He was also here depressingly long this morning and belabored the same theme, not without much spirit and rubbing my face in my ignorance. Incidentally all in good friendship. --

Yesterday morning I worked on my lectures in the work room, i.e. I cannibalized Vossler's lecture. (Began Corneille). Around 11 the servant came and said that Eisner had been murdered. (\WTF{Of his wife I want to mske sure that she can maintain a bit of dignity and aloofness}{Von dessen Frau ich doch nochholen will, daß sie ein wenig doch wohl Würde und Unnahbarkeit zu markieren versuchte}). Then around 12 a librarian shouted into the room that the university was to be immediately closed. I then went home and didn't meet Eva, and wanted to pick her up at the academy -- she is now enrolled in the composition class and is Klose's student. A long procession of w skerstrectched over Odeonsplatz

 with occasional cries for revenge; I dared not pass through them and reproached myself for my cowardice. On the other hand it was around 1, and Eva was probably not in the academy any longer. I went back and ran into her right at the house. In any case, it was a shameful memory to not be able to force my way through to her conservatory. After eating, we went with Pontius to Hans M's. Later I went with Pontius, Hans and his friend Behle to Theresienwiese and all over the city. Towards evening I met Eva in Stephanie; after 7 o'clock one could no longer go out onto the streets, we chatted at length over supper, where a young consertatively-oriented doctor and Rheinlander returning from thr field turned up, and then went to sleep soon after. This morning -- \?{I am indeed having a "celebration"}{Ich habe ja nun "Ferien"}, I have been spared from all 4 classes by the closure of the university! I wrote - as far as I was not taken up by Lerch's mentioned visit - a report for the Leipziget NN, which generalizes or overstates a bit what I actually saw. At most I pluralized the weapons I saw loaded on the automobile, while I only once saw the act of loading. After eating to M's again. Hans's completely proletarian, one-sided view of the situation repels me. Wekerle, all-around gaunt and careworn, "haggard", expressed himself very fanatically. "Hostages!" On the way we again, as yesterday as well, met the "Mental workers' council" Ballabene, an insignificant and ignorant forty-something, \WTF{who struck Eva as incredibly important}{der sich ungemein wichtig vorkommt [getroffen?] Eva} and I then went to the station, to send the letter to Harms. Crowds, barricades. Someone let us pass. I asked at the platform when a train was going to Berlin. "\WTF{Dös wisse man net bei derer Gaudi}{???}", yesterday's had not gone. As I again passed the guardposts, which all demanded identification, but which were all very polite, I misplaced a packet, it contained bacon which we had just bought from M's for 30M. I, rather hopeless, went in yet again. The packet, inconspicuous in newspaper, lay there on the empty counter where I had licked the stamps. What joy. Then a little while in the overflowing Stephanie, which was closed in the morning and had to close again at 7 because of the state of siege. Read the newspapers, the Central Council would publish in the stead of the suppressed bourgeois sheets, back home and again wrote a report to Harms, in which I cited as coming from three workers' councillors what I learned from Ballabene, Weckerle and Hans, but otherwise everything according to what really happened. Thus I have given the whole Friday afternoon and all of Saturday to politics. Am I playing a double game? I put on no hateful words against Eisner or Weckerle; but if these people knew that I was reporting to the LNN, they would be closed off to me. And I fear, since \WTF{I focus on the language}{sehr mit der Sprach herausgehe} and since my reports are emphasized in the LNN, my incognito will soon disappear. With the fanaticism that reigns here, I could even undergo "preventative detention", if not worse. Yet I dare say that it will get me into political journalism and pave my way to Paris.
 
What can the university do for me economically in the long run? It has even become questionable whether the government -- which? -- will pay us the fee for the preparatory courses. It is very amusing how socialist economics is \?{gaining popularity}{sich Bahn macht} the circle of lecturers. (Lerch as the driving force). It has recently been considered that the preparatory courses be immediately cancelled if the government does not start to pay the promised 250M per class. Prof Kieckers wanted to speak with Matt on this matter. Kieckers is a sturdy full-blooded man of about 40 years. He does countless lectures, German, old German, Latin, etc etc, is habilitated in comparative linguistics. --


 
 