\header{Wednesday morning 9 o'clock. 12/II 19. Day of father's death.}

\missing Yesterday went especially badly. To be able to speak with ease about D'Urfé, with all the complex themes, is taking great effort. Also, at the end I made a little mistake, incidentally for the second time already: \?{I had reached the end of a section just as the clock hit 4:00}{ich war an einen Abschnitt angelangt, als die Saaluhr genau auf 4 Uhr stand}. So I stopped there. But the bell can just a minute later, and so everyone looked with wonder at the clock when I finished. From now on I will speak until the bell, even if I only just begin some new section. -- \missing

In the morning we had the \?{inaugural professor's meeting}{Professoren-Antrittsvisiten}. \WTF{Handed over the card to Baumcker, accepted in style, living very elegantly and at the same time intimately in Ainmillerstr}{Bei Bäumcker Karte abgegeben, bei Schick, sehr elegant und zugleich intim Ainmillerstr wohnend, aufgenommen}. I.e. by his wife, he himself was laid up sick. Old stately lady in hat and veil, through which poked the white beard and moustache. Total Englishwoman, speaking German well, but with a broken accent, though she has lived in Germany for at least 30 years. She was in England at the start of the war, her husband was a German officer. She was very glad that we expressed a conciliatory view towards England and Italy. She held Eva's hand in hers at the end of a quite emotional speech. \?{Apply your knowledge to conciliation}{Wenden Sie Ihr Wissen im Sinn der Versöhnung an}. It is my nature to join in love, not hate! Eva found that typically English (and rightly so). But now: her third word was, in England no one wanted the war, only the Northcliffe -- e cioè the Jewish press! -- pursued it. The Jews were to blame for the war! The Jews, \?{with their international ties}{die international versippten}, who do their business in peace, are to blame for the war! What a gift to Europe these Jews are. For war and peace, for wining, for losing, for every problem they are to blame! We listened in silence. --

When father died, there was a coat that mother \?{had fitted for me against my will}{gegen meinen Willen für mich umfitten ließ}. At the time, February 1912, she paid 100M for it. I never wore it. Since it was too heavy for me, and Eva had no coat. We fetched it today, all crumpled up but well-preserved, from a box at Wetsch's. Also a winter coat which finally rescued me from thr too-light summer coat. I decided to sell \?{it}{des Stückes}. Hans M claimed 5-700M could be gotten for it. I am skeptical...We wanted to go for coffee with Hans yestersay, met him in front of his place; his wife was under the weather, exhausted from too many \?{accounting books}{Geschäftsbücher}, needed rest. In the evening Hans came here for a while, after that we sat with him in Stephanie. He is completely \?{behind}{im Schlepptau} Weckerle's fanatical and mendacious opinions. The un-socialist bloody government of Ebert, the coming true revolution, the \?{common wage}{Einheitslohn} for all workers, even the "mental" ones, the poor unemployed...

 % h