Yesterday morning: Discussions with Goering and Lippert: Lippert has apparently been very clumsy. Hitler raged about it. Very furious about my ultimatum. Played The Duce for Lippert, wild threats spat out against Strasser, portrayed me as a little Gauleiter, complained that he had not gone to Berlin but to Berchtesgaden on Saturday, then again praised my abilities before Goering, brief and good, the chief, when he is \missing and too unpleasant but essential business will press on. I proudly love the Spaniard. Handshake and more promises.
Amann is said to have pounded the KV daily paper into dust in the VB, Hitler said to have distributed a circular letter against the Strasser paper around the Gau, I am to be the propaganda head -- for the second time? -- and Strasser gets an ultimatum: out of the newspaper, or give up the org division. If only all of that is true. I don't believe it until I see it. I remain totally calm about it. Can wait! Hitler rejects that though however; is is jealous. Afternoon work. I met Erika in the city assembly. The good dear thing! Red house. Old muck! One is only a puppet there. Bach Hall film festival. This time I am in form while speaking, and the whole thing has style and momentum. Together with Charlotte until late into the night. She loves me hotly and as a most special woman. Still, \?{I can't make sense of her}{bin ich nicht klug aus ihr geworden}. The political situation is desperate. The cabinet is at death's door. Tomorrow the Reichstag meets. \?{A funeral viewing?}{Zur Trauersitzung?} The KPD plans another revolution for tomorrow? \WTF{Tollhausk}...Our time is near. If we only had a purposeful, strict leadership! But? Poor Hitler!
