Just back from Nuremberg. Hitler and Streicher pick me up right at the station. Hitler is running over with kindness. A sign that he has a bad conscience. The newspaper affair is just as incredible as a few weeks ago. Telephone conversation with Esser in Berlin: the KV is a thoroughly bankrupt undertaking. The party publisher must raise 100000M \?{to bail him out}{ihn zu regenerieren}. Amann can't do that, and he doesn't want to either. Hitler was very despondent with the report. That is good for me, with that I'll get even more chances for an Angriff daily. Let the two fight each other, I am the laughing third. Hitler was again \WTF{totally in the party conference}, which is to be in Nuremberg again this year. Streicher was not all too enthusiastic about that. He is wholly with me and hates the Strassers. He is in the first place not as \missing as is generally assumed. Only his Jew-mania. Hitler gives me many worries, he promises much and delivers little. Mass assembly. Over-overflowing. A blow-out success. I speak well. The Nurembergers are enthusiastic. Then a little time together with Hitler. He is back on top. Carries on mightily about Feder, who causes him and the movement many problems. I do not like this puffed-up peacock. Hitler is still very endearing. Full of charm. A Herrenmensch! He likes me very much. Osaf is also there. As always. Smiling mockingly. He has style. Bouhler -- a zero, -- Hallermann -- speaks much. Home on the night train. Hitler accompanies me to the station and promises me mountains of gold. I laugh. Short night. Berlin!

