Sunday: to Potsdam. Spoke before 15000 in the airship yard. Icy cold. But good mood. Before me Kunr held a field, forest and meadow speech. I was in good form. Midday with the fuehrer. He has received Phipps, who implored him to dispatch him to London. \WTF{Fuehrer no longer makes any distinction. We do not want to end up accused. London admits that.} But we must go there, otherwise we can no longer easily communicate. Probably Ribbentrop. Two conditions: that we will be equals and that we are "promptly" advised about our proposals. Neurath tells London so on the fuehrer's instructions. Phipps was very small. Also on the other side are only \WTF{people}. One must only have a strong heart. Our ambassador in London has unfortunately not had that. Fuehrer will clean up there when this story is finished. I back him up in his decision to remain strong. If we keep our nerve now, then everything is won. Much work at home. Neurath's answer to London has gone out. In the evening the fuehrer is our guest. He is very cheerful. Big group. Frl Hamsun also there. A remarkable kind of person. With so many character traits of the poet father. An American thriller film "Captain Blood". Good, and grandiose. But otherwise a tall tale. We stay up for a long time and talk. With Magda discussed purchasing the house in Cladow. The fuehrer wants to help us.
Monday: our answer has satisfied few in London. Above all, the French are already threatening departure.  But the English and the Belgians are more reasonable. The fuehrer's answer to Phipps and his cold decisiveness work wonders. They demand a humbling "gesture" from us in view of the fuehrer's offer. Long conversation with Funk. Greiner tries to get sway over the leadership of the ministry and then to bureaucratize it. I shut it down. The bureaucracy is not suited to active work! The propaganda goes blisteringly forward! It is a joy to work together here!
With the fuehrer: 2 of his assemblies must be postponed. That causes me much trouble and concern. In London still nothing new. The council meets today. We must now wait and learn! To not waste the future because of a momentary weakness. Fuehrer flies to Frankfurt. I work until the evening at home. An American film shown: "Broadway[!] Melodies". Lively and fast-paced. The Americans can do that. The content is rubbish, but the way they handle it, that is skill. In the evening I hear the fuehrer's speech from Frankfurt. An enchanting performance. I believe that it will \WTF{give a good choice}. Results from London: our equality announced. But no right to vote, like France and Belgium. Our proposals only negotiated in the Locarno council. That will be represented by Reuter as a rejection. \WTF{But no one is comfortable with it.} Now we must be very careful. Played at length with Helga. The children are releived of all worries. Early to bed. Slept well. Since today I have a difficult day. Must speak six times. That will cost effort and sweat. But also stay young and fresh.


