Tuesday: a fantastic, wild day. My essay against the English moral hypocrisy hits like a bomb. The whole German press takes the same line. England will be smothered. That is a true \WTF{Halberfeldtreiben}. Moreover the fuehrer can still declare that if London continues this way, the naval treaty can be called into question. And now John Bull will be tamed. London has visibly drawn back. That was the purpose of the exercise. But we must keep hold of the reins and stay on the enemy. I give the press the task of exposing the whole English colonial history. That is uncomfortable to the English. Moreover I am now letting our radio stations run in English. That will do it! Demandowski explains his production program to me. He has a whole series of good material. I give him advice for casting and direction. He has already proven himself. With the fuehrer midday. The Memel question has become acute. Ribbentrop has presented the fuehrer's demand for the return of the Memel Territory to the Lithuanian foreign minister in the form of an ultimatum. Now they are negotiating in Kowno. Results can no longer be in doubt. I talk through the Ribbentrop question with Hess. Ribbentrop makes himself quite unpopular everywhere. He has Bohle totally up against the wall. He wants to govern alone and form a state within a state. But he no longer gets in my way. Koehn gives me a report on Spain. The offensive is to begin in Madrid. Franco hopes to have the final victory in his hands in two months. He has spoken out sharply against the monarchy. Afterwards, our Condor legion is to be \?{revealed}{enttarnt}. After the Spanish war I want to call Koehn to Beelin to be Hasenöhrl's successor. I discuss the future work of the foreign divisions with him. They must be more energetic and more handsomely-equipped. Dr Brauer lays out his production program for Terra to me. Not as good as Tobis's, but sill very acceptable. Unfortunately the firms care about everything except the people. I will change that. Evening with the fuehrer. The Memel question is at the critical high point. That means that it is time to watch out again. With the fuehrer in the theater in the Behrenstrasse. \WTF{Zum Tarnen.} A harmless but very amusing tale by RA Roberts "Hau -- Rock". We have to laugh a little at least. Meanwhile there is a heated struggle in Kowno. In the Reich chancellery. Still no result from Kowno. I can meanwhile discuss some questions with the fuehrer. The theater in Vienna will be excised from my budget. Vienna can't do it alone. We don't know however who should manage them. We leave the Czech culture to the Czechs themselves. We only care about German culture. I should buy up the film studio and perhaps a Prague newspaper. Neurath will soon be moved to Prague. If they behave loyally, we will give the Czechs wide berth. They must always have something more to lose. A communique comes from Kowno. Which is unusable. We completely rewrite it. But still no satisfactory decision. Meanwhile Kowno publishes their communique, and then the minister there goes to sleep. \WTF{But now it's 13}. Out envoy will be entrusted with fetching them out of bed and putting the pistol in their chest. Either - or. This little crook from Versailles must now hand over the loot. Otherwise we let him have it! Then we wait and wait. The fuehrer develops his future foreign policy. He now wants to bring some calm, in order to earn some trust again. And then the colonial question comes up again. The one always follows the other. At 3 in the morning comes the announcement that everything was accepted. Only the communique is still missing. We get a couple hours of sleep.
Wednesday: I am drummed out of bed at 7. The communique is there: Lithuania cedes the Memel region. A Lithuanian delegation comes immediately to Berlin to determine the conditions. \WTF{Na, also!} A little pressure, and it's already done. Unfortunately I cannot give the announcement immediately over the radio, since the apparatus is not functioning. In Memel and in the whole Reich the flags fly high. Our Volk is bubbling over with joy and filled with a glorious pride. And there is a reason for it. Only there is the danger that the bourgeoisie beloeve that it will go on like that forever. There are many fantastic ideas about the next plans for the German foreign policy. I will also polemicize against it. Discussed open questions with Hanke and discussed personal details with Dr Mueller. Midday with the fuehrer. In the Reich chancellery a vain joy reigns. The fuehrer is totally happy. The Grand Fascist Council has in a solemn resolution renewed its adherence to the Axis. It was time for that. In Paris and London they are already speculating about a break. The fuehrer now also approves my trip abroad after the finalization of our actions. I fly to Budapest, Athens and Rhodes. How I enjoy it! Next week that starts. The fuehrer drives to Swinemuende, in order to go with the Panzer-ship "Deutschland" to Memel. That will be a joy. \missing

