Yesterday: after a long sleep chatted with the children. They become sweeter and more enchanting from day to day.  Holde is now having her turn. The arrival of the fuehrer in Berlin is fixed for 19:30 Sunday. We prepare for a totally huge reception. My appeal is passed out in 1 million copies. In Birmingham Chamberlain gives a rather rotten speech. This "good old man" is impudent, just as the English are impudent. Blathers on the breaking of promises etc, Daladier demands half-dictatorial powers in the chamber. The Bohemia and Moravia are for London and Paris only a pretext for intensifying rearmament. But we do things with a splash, and we are on guard. Caution is here the mother of wisdom. I allow sharp polemics against Chamberlain in the press. In the afternoon a sharp official declaration comes from London. The Munich Agreement has been broken. England does not recognize the new order in Bohemia and Moravia. But that is probably only theatrics. What these democrats want then is still just to protest. That is only hysterical shrieking post festum, which leaves us entirely cold. The German press will also treat that \WTF{so von obenher}. Contempt is suitable here. Paris also joins in the London protest. We now go into the sharpest polemics against them. My essay in the VB also attacks along this line. Neurath named as the Reichsprotektor for Bohemia and Moravia. That is an extraordinary solution. Neurath is clever, if essentially hard, diplomatically trained and when necessary very friendly. He has a difficult task, but will undoubtedly master it.