Yesterday: my article against the political humorists with my corresponding decree hits like a bomb. Now the intellectual cowards quake and are afraid. Straight away I dictate a new article against the \WTF{cafe snakes}{Kaffeeschlangen} who are a consequence of our momentary coffee shortage and arouse general outrage. I will now strike back against this bad behavior with verve. Otherwise all kinds of work.
With torturous words, Roosevelt withdrew his speech that America's border is on the Rhine. Question is whether the American films are to be withdrawn. I am still not very clear on it. Midday and afternoon, work. Harald sits for his Abitur. The Stojandovic government has stepped down. They have apparently driven the election swindle too far. And then the opposition was still too strong. It is still Balkan. For us, I believe, not a happy development. \WTF{Since Stojandovic can be dealt with}}{Denn mit Stojandovic liess sich umgehen}. Afternoon film review. "Bel ami" a new Willi Forstproduktion. With him himself, Riemann, Dohm and numerous beautiful women. A cheeky film, perhaps a bit too cheeky, but totally magnificently made. The tendency is at the moment rather frivolous, then at the end better. Perhaps some cuts then release it. It will be a big hit. In the evening Leni Riefenstahl reports to me on her trip to America. She gives me an exhaustive picture, which is anything but pleasing. We have no influence there. The Jews reign with terror and boycott.  But how long yet? Late and tired to bed.