Yesterday: the worldwide agitation against us is again in full swing. Above all in London. There my essay against the English for the VB has come exactly true. Incidentally I started a very strong counter-campaign in the German press. Principal: Attack is the best parade! An ultimatum is dictated to us on Romania. That will be denied by Bucharest. Against that I now \WTF{lasse ich loswettern}. The Lithuanian foreign minister is in Berlin. Lithuania seems to want to voluntarily give up Memel. Wait! In London, they are insanely angry at us. Because of our diplomatic success. That is understandable. Discussed press questions for Prague with Amann. We sell only papers written by Germans. The Czechs will be taken further under control. We only want to control, not bully or lead. The Czechs are to do that themselves. With Ley, the "8th Chamber" of the Reich Culture Chamber becomes perfect. Now all that is missing is the acknowledgment from Hess. The \missing success of the German film has gone well so far. We secure an atelier in Prague, since our atelier space is too small in order to be able to publish enough films. With an order I somewhat halted the excesses of modern ballroom dancing. That is necessary. Midday with the fuehrer. He is totally cool with respect to the swelling agitation abroad. It doesn't affect him at all. He views the situation completely calmly, yes, he even gives me leave to make my trip overseas. However I don't know whether I will make use of it. The fuehrer is wonderful is his sovereign calm. \missing
