\header{Friday evening 11 o'clock 25/4.}

Government troops are said to be very nearby, we expect the attack and liberation hourly. Today fliers were scattered, that one shoukd remain at home from 6 o'clock. In the evening, at most a couple shots, occasional sounding of alarms, otherwise everything was calm. -- At Hans M's (who is today having a fracture ooerated on) the day before yesterday, ran into Landauer and the widow Eisner. He now rejects entering into the Levien government. Fantastic confusion is said to reign. Hans showed me a paper with his photograph: "Comrade Meyerhof belongs to the Committee for Combatting the Counter-Revolution. He may carry weapons and carry out arrests." Hans said that he had been forced to take the paper, he could provide me with the same. Landauer advised: arrest Levien...this calm in the city, this being cut-off, the typical shots in the evening, the waiting on help...a evry strange situation.

\missing

Yesterday afternoon a visit with \textit{Professor Lehmann}. They have a tiny quite simple 4th-floor flat on Trautenwolfstrasse; a little flaxen-blonde girl \?{tends to them}{erfüllt sie} with tremendous noise. Today for a long tea (terribly "German") at Muncker's. The gray old professor Borinski and his much younger wife, who was rather talkative with me. He was already 58 and still an Extraordinairus, unsalaried, thanks to the ancien regime. He was too proud to complain. She would rather teach and earn 300M monthly with that, she had been a teacher at the Russian court, she was also a peasant's daughter from Lower Bavaria, and thus always had lard and eggs etc etc. It all sounded rather miserable. Muncker himself seemed to have become rather old.

Music in the evening accodding to custom, but not very thrilling.

% 