\header{Easter Sunday 20/4 19. Morning}

Yesterday started writing the Corneille study, began reading Zola's "La tierre" aloud. In the evening, at Vossler's together with Lehmann, the Braunschweigers, somehow related to the Baltic v.d. Recke, told of the frightful affair with the Bolshevic business. (\WTF{Who sunk bourgeois and nobility with weights, which the diver found upright on the beach}{Die mit Gewichten versenkten Bourgeois und Adligen, die der Taucher aufrecht am Meeresgrund fand}.) Lehmann is a middle-Latin scholar; I saw him collapse with a heart attack in the work room in 1914; he has a blonde, slight wife. Vossler wrote to Kuchler for me, in whose paper my Corneille study is going to appear...at 10:30, while we were sitting up there, shots from the Feilitzschplatz where there were guards stationed, and ringing of bells. Later, it had calmed down, we went straight home, there was only an excited group around an automobile on the Feilitzschplatz. -- The hopeless mood has again whipped around; there was a flyer from Hoffmann, that help was near; there was a rumor that Wurtemberg troops were on the move. I again wrote about all 
f this in a "revolutionary diary". The evening with Vossler yesterday evening was much preferable to us than the one Tuesday with Lerch. \WTF{Where only Lerch received his contract in philology}{Wo doch nur Lerch seine Bedientenaufträge in Filologia ausführlich entgegennimmt}...Lehmen told me that visits with all 70 members of the philology faculty would be essential, but not with all of their wives; \WTF{the whole Summer will certainly be overtime}{auch sei sicherlich den ganzen Sommer über Zeit}. --

The day before yesterday, Weckerle read aloud Landauer's whole extraordinarily phrasemongering writings to his \WTF{team}{Referenten}. Vossler explained how the team mocked him by \WTF{directing two incoming and outgoing washbaskets directly to him}{indem sie zwei Waschkörbe Ein- und Ausgänge direct an ihn geleitet}. He now takes that as the essence of bureaucracy, \WTF{that he would have to decide about a football game in the gymnasium to X itself}{daß er über ein Fußballspiel im Gymnasium zu X selber entscheiden müsse}. Wekerle stressed the abolition of all 

tles: "Teacher at the University of Munich"...Communion and communism. How the people streamed out of the church yesterday. Schellingstrasse was black, in between were scattered the little white candle-bearers (like snowflakes on the black January earth!)% Herzka evempf und Geistkampf -- Geistschlagers, Christschlagers