\header{30/4 19 Wednesday morning}

Finished taking extensive notes on \textit{Bête humaine}, read aloud a few pages from the dragging \textit{Terre}. Hopeless bibliographic preparations for the V Hugo lecture. There is little point; I will go through Mabilleau and Biré and roughly sketch \?{what is worked on from hour to hour}{was von Stunde zu Stunde zu arbeiten ist}. -- It the morning two visits to professors, in both cases only the lady was home. Frau Wilhelm, la femme à Méphisto-Germanistico. Frau Heisenberg, privy councillor, her August (who I do not know) is an Ordinarius for Greek. Both ladies very charming, very interesting, both times Eva had to sit on the sofa right next to the housewife, \WTF{right next to them, that is how it is done}{dicht, das gehört sich}. There is a hierarchy: the Frau Extraordinarius without a lectureship is more intimate, warmer, \WTF{more flexible destiny}{schicksalsverwandter}; the Frau privy councillor is more casual, more affable; \WTF{she answered the door herself, introduced herself}{sie öffnete übrigens selber, stellte sich vor} and had a fresh, un-artificial self-conscious essence. The conversation was always the same: about the present circumstances, about my destiny -- I told of Naples and Gent, of Landauer and Strasser,

In the evening, a loud alarm: bells, a factory horn, cannon shots around 12. Otherwise, silence. Yesterday was the first day since April 13th that the \?{local newspaper}{Staatsztg.} appeared, under censorship of the works council -- again today no trams are running. There is total uncertainty.
%