\documentclass{article}
\usepackage[utf8]{inputenc}

\newcommand{\nf}[2]{
\newcommand{#1}[1]{#2}
}
\newcommand{\nff}[2]{
\newcommand{#1}[2]{#2}
}
\newcommand{\rf}[2]{
\renewcommand{#1}[1]{#2}
}
\newcommand{\rff}[2]{
\renewcommand{#1}[2]{#2}
}

\newcommand{\nc}[2]{
  \newcommand{#1}{#2}
}
\newcommand{\rc}[2]{
  \renewcommand{#1}{#2}
}

\nff{\WTF}{#1 (\textit{#2})}
\nf{\?}{}

\nf{\translator}{\footnote{\textbf{Translator note:}#1}}
\nc{\sic}{{}^\text{(\textit{sic})}}

\nf{\sskip}{...\textit{#1}...}

\title{Klemperer - 1932}

\begin{document}

\date{January 8, 1932}
Friday night, 12:30

Made progress on Corneille up to the end of the comedian chapters.

Much reading aloud. Finished \?{Virey} by Sealsfield. Gordon by Lytton Strachey, now Stevenson "Schatzinsel".

We have gone over to using \textit{Du} with Gusti Wieghardt.

Today from 8:15 to 9:45 my first lecture in the external institute on modern French lit. theory of "\WTF{equalizing}{Ausgleichs}". Preparations exhausting, since the morning was disturbed by Martha Wiechmann. She came from the ministry, where she had protested against her \WTF{reduction}{Abbau}. The lecture itself was also exhausting. In front of about 90 people. Next Friday second and final lecture. On 1/28 the Corneille lecture at the Philology Association.

\date{January 25, 1932}

Always the same with Eva. \WTF{Apathy}{Lebensunlust}. I often believe that only our little Mucius 
keeps her alive. That always lies upon me as a physical pressure --\WTF{it knocks the life out of me}{der Athem bleibt oft aus}. I am so completely tired and hopeless.

In the highschool, a Leipzig docent has been put forward against my will as Bruck's successor. More specifically, Janentzky's treachery is in play. I am totally isolated. Today \textit{Hittmair}, a scientific nobody, received an appointment to T\"ubingen. \?{I will live to see the fourth Anglicist here and probably several more.}

Finishes the Cid chapter in Corneille. Finally \?{agreed on}{verabredet} a Corn. anthology with Hueber. Fee the 365M which I owed H. from the \?{trial}. \?{But I need to write the anthology on the machine}; that will cost me at least 75M. -- Otherwise no income, jobs -- only silence around me.

I held two lectures for the external institute on the latest in French. Large audience, applause, even in the press. But for Hittmair's corresponding lectures, \WTF{put together and written off}{zusammengestellt und abgeschrieben}, the same audience, the same applause, also in the press, and the call to T\"ubingen.

Much reading aloud. Jud S\"uß by Feuchtwanger, now his hateful duchess.

\date{January 29, 1932}

Yesterday my Corneille lecture at the Vitztum gynmasium before the \?{new phililogists}, about a good 100 listeners. Probably good. Previoualy I would have very "\WTF{???}{geschwoin}" \?{about it}. Now? "The witty high school professor." Hittmair among the audience, Ordinairus from T\"ubingen. And Mencke-Gl\"uckert. 
\end{document}
