\letter{94}
\from{Heisenberg}
\date{June 29, 1925}
\location{Goettingen}

Many thanks for your letter, pardon my letter, which was written very late at night and in a not-entirely-\WTF{sane}{zurechnungsfähigem} state. If I actually had written monocrystal, that was of course a print error for crystal lattice (I write this in order to take the blame for this type of rubbish and to not leave it to Herrn Elsasser); however I earnestly hold it to be entirely possible that the Ramsauer experiment, as well as that of Davison and Kunsman, should be explained by the Einstein theory (which was all Elsasser claimed), and ever since studying Einstein's paper I'm actually very excited about it.

As regards the energy \?{calculation} in my quantum mechanical formalism, it is my opinion just as \WTF{unavoidable}{zwangsläufig} as the multiplication of "Fourier"-series. i.e. \textit{if} one believes in the quantum-theoretical change of this multiplication, and \textit{further} in the form for the energy $\frac{p^2}{2m} + \omega^2 q^2$, then one must also admit $W=\left(n+\inv{2}\right)h\nu$. Meanwhile I have made some, but not much, progress, and am again convinced in my heart, that this quantum mechanics is already correct, \?{and for this reason} Kramees accuses me of optimism.

Even S. Eminenz found Einstein's paper to be beautiful, and \?{so with you he must "have more joy about a sinner who does pennance"} etc.

Many greetings,
Your Heisenberg

PS! I am not satisfied with your interpretation that the $\sigma$-components are not circular. One could, following Stern, separate out the atoms with the \textit{magnetic} field, then they are also separate when they are outside of the magnetic field and are only still in the electric field.