\letter{96}
\from{Heisenberg}
\date{July 9, 1925}
\location{G\"ottingen}

Dear Pauli!

If you believe that I had only read your letter with jeers, then you quite decieve yourself; on the contrary, my opinion on mechanics is more radical from day to day since Helgoland, and it is my fixed conviction that the Bohr theory of hydrogen in the present form is no better than the "Land\'e theory of the Zeeman effect". But in many points we are still not of one mind; (your argument against the mechanical orbits in H because of the sum rules was known to me, since we had discussed it with you once in Copenhagen; and ) am in total agreement if you want to \?{exclude} half-integer $m$ from it. Yet I don't know what you think about orbits which \?{fall} in the nucleus. We are nevertheless probably as one in thinking that the kinematics of the quantum theory are already completely different from the classical ($h\nu$-relation!), and for this reason I see absolutely no geometrically-\?{controllable} sense in the statement "falling into the nucleus". It is my conviction that an interpretation of the Rydberg formula in the sense of circular- or elliptical-orbits in \textit{classical} geometry has not the least physical meaning and all my wretched efforts go towards completely doing away with the idea of orbits, which cannot be observed anyway, and to suitably replace them. For this reason I \?{am comfortable with} simply sending you the manuscript of my paper straight away, since I believe that it contains, at least in the critical i.e. negative part, actual physics. Though I have a very bad conscience, since I must beg you to send it back in 2-3 days, since in my lasy days here I would like to either finish it or burn it. My own opinion on the scribblings (about which I am not at all happy), is this: that I am firmly convinced of the negative critical part, but that I hold the positive to be overly formal and meager; but perhaps \?{more able people} could do something reasonable with it. So please mainly read the introduction.

To the close of your letter: I did not mean that the \?{breadth} of the line amounts to $2536\inv{30}$, indeed this has been measured; rather I think that the line $2p_2 - 2s$, which is almost exclusively responsible for the splitting of $2p_2$, if one wants to interpret the Hanle splitting, gives about $\inv{30}$

which does not seem to be in agreement with the spectrum.

Now I beg you for sharp criticism and a soon return of the paper! Many greetings to the whole institute!

\textsc{W. Heisenberg}

%wy  Rydxohere the pampers is