\header{Friday June 13th, 9 o'clock in the morning.}

Worked on the Victor Hugo lecture: "What is Romanticism?" yesterday and already earlier today; it should be ready today. In the Romance language seminar on Montesquieu looked up Hettner, leafed through Vinet -- without new \WTF{lecture}{Belehrung}...Read aloud from Au Bonheur des Dames. In heavy heat, went to the dentist and the Deutscher Bank, in the evening went in vain to M's then to the cafe.

The idea of right and wrong is lost to the people of all parties. A \?{honest}{biedere}, educated, good-natured lady, a Frl Prantl, said at supper with conviction: Graf Arco, Eisner's murderer, must be acquited, he had carried out an act of liberation. Hans M saidnthe murder of the hostages was justified, Frau Dr Sobat defended 
Leviné, even if he instigated the murder of the hostages, he was no murderer; he who only instigates shows that he couldn't himself kill! --

\missing

\textit{12 o'clock at night (13/6)} The introduction to "Romanticism" is almost entirely ready, and is not bad. Not very original, but it is well put-together \WTF{arranged}{fest disponiert}...Towards evening went for "German" tea with Munckers. Usual bore. Few people and nothing of significance there. \WTF{That house has become old and tired}{Das Haus wird altermüde}...After that, for the first time in a long time, singing at our place. Finally towards 11 o'clock with Frau Dr Sobat to Stephanie for a few minutes and drank some beer. Today Eva copied a theoretical musical work. The time when I dictated my affairs to her, when she was totally tied up with my work, is long gone. I have a very egoistical desire for those times. But things went better for me then. But I must constantly remind myself that I must not retard E's own development, that I not exploit her for myself. Of course I have been made bit lonesome by the organ. But then again: \WTF{what would Eva start now without her own occupation, where she has no household}{Was finge Eva jetzt ohne ihren eigenen Beruf an, wo sie keinen Haushalt hat}...