\header{Tuesday June 10th, morning towards 12 o'clock}

\missing

I have been very frustrated with \textit{Teubner} recently. It's been back and forth since almost February. First he got into my Corneille proposal, made all kinds of suggestions. Then he rejected it and asked whether I wanted to undertake two volumes on "Nature and the Mental World", about French dramatists and storytellers; when I accepted he would share the conditions with me. \WTF{I accepted, and today he wrote, but because of the situation he still could confirm, but he hoped to be certain in the course of the year, etc etc}{Ich nahm an, und heute schreibt er, noch könne er sich der Lage halber nicht binden, hoffe aber bestimmt, im Laufe des Jahres...etc etc}.

\textit{Evening, towards 12}. Began Nolhac; his good introduction is totally Burckhardtish, without naming him. In the seminar, read Vossler's little Italian literary history. Before eating, to Hans M's, warned him about Weckerle. Most violent clash: "Your Whites are the murderers; it was right to shoot the hostages!" I threatened to have Weckerle arrested if he turned up again. We parted very agitated. After supper -- I was entirely alone, E was at the theater, everyone else away -- I went to see him again, he had meanwhile (while I was away) phoned: we reconciled -- but the internak situation is unchanged. A woman with him, harmlessly dumb, said that he friend saw Levien every two days! Hans plays with the fire until he gets burned. Weckerke has for the moment a journalistic post in Mannheim, and so Munich is spared. Towards 10 the quiet Behle accompanied me to pick up Eva from the National Theater and sat chatting at Stephanie. -- Started \textit{Au Bonheur des Dames}.