\header{Thursday afternoon 19 June 19}

Yesterday evening, as we came from Meyerhof's -- long discussion in the \?{garden}{Gärtchenlaube} -- there was a telegram from Georg from that very day: "Mother, after a brief sickness, passed gently away". \sic{12th II 1912} - 18/VI 1919. Father was actually cleverer to go before the war. I have long reckoned on this death, but it is surprising nonetheless. I am again just as cold-hearted as with father's death, and actually all the time. Loneliness is all I feel now. Indeed, mother was de facto dead or me for a long time. Blind, shut off from life, closely surrounded by her daughters. But she herself probably still always \WTF{had an awareness of being alive}{noch Lebensgefühl gehabt} in her family circle. She has probably also been lucky. Always lively and fulfilled \?{in her narrow way}{in ihrer Enge}, always cheerful, almost careless -- after father's death \WTF{breathing in a type of feeling of dominion}{aufathmend in einer Art Herrschaftsgefühl}, then being occupied with her daughters (Marta, Grete, Wally in turn) was certainly felt as a stimulation rather than as a disgrace. Certainly without Lear-moods... She had clung to me, and like father, \WTF{she had not imagined that I would succeed at a porr}{hat sie es nicht erlebt, daß ich in eine Hafen gelangt wäre}. I had been quite cold and ungrateful for her real feelings for me, and I am still now.

I have precious little desire to go to the funeral, which is indeed a most empty formality, but I will probably do it anyway. There will be much awkwardness for me there. Berthold, inheritance, which will not make me rich, and will not \WTF{ease my soul}{soulagieren}. Perhaps I will ask the brothers to keep the money for themselves and further \WTF{impoverish}{bealmosen} myself.

Much to do. Yesterday evening I borrowed 200 M from Dr Ritter, since the bank is closed because of Corpus Christi. Today, already at the station twice because of travel papers. They are kosher for tomorrow. But I have also requested a telephone conversation with Georg in order to hear when the funeral will be. I don't know whether Weissensee works on Sunday...At Hans M's, who lent me a black tie and a dark hat, and to 
hom I poured my heart out. He is now my only friend from youth. --

Tuesday I spoke again on Romanticism, yesterday from 3-5 on Montesquieu. I must continue this introduction next Wedneaday, but I want to get to the lecture itself then as well. The Petrarca biography was shoved into the background on these lecture days; today I want to earnestly get into it. --

Answer and ultimatum of the Entente. Miserable, how the same Centrum- and democratic press, who had written in high tones againsf the signing, have now suddenly collapsed: the poor people want peace. Politics is gradually becoming so repulsive to me that I want to turn completely away from i

 --
 %