\header{Berlin trip June 21-23  Mother: 6/18/19}

\textit{Nuremberg, 4 o'clock Monday afternoon 23/June 1919}
In a Nuremberg cafe, \?{first class}{erster Stock}, across from the Lorenz Church. Arrived here at 3:30, sent a telegram to Eva, here with two real coffees and a cookie, sent a registered letter to Berthold; frank explanation that I left the exclusive decision regarding the inheritance to him, since the money was his. But if it should come to me in some form, then I would have to have a formal explanation as to which claims Eva will be able to raise later; brotherly addition: was glad to have been with him, was thankful to him, but could not forgive his unexcusable behavior from 1916.

I departed Munich on Saturday at 7:45. Because of a railworkers' strike in Thuringia, detour from Nuremberg to the East over Hof and Leizig. \WTF{The Leipzig grotesquery at Scherner's}{Die Leipziger Groteske bei Scherners}. Sunday morning trip to Berlin, to Marta, with Jelski and Walter to Weissensee, funeral. Ate with Georg, to Felix's, to Berthold's -- inheritance. At 9:30 on the fast train to Hof; there at 4:10 this morning, left at 5:20, fourth class in the slow train. At ?? in Nuremberg, from which I returned to Munich at 7:30. I haven't been out of my boots for two nights, since early Saturday hurled from impression to impression, nerves badly worn out.

I will write the whole thing in detail, from Munich to the end, but probably only after Wednesday, since the lectures are on my mind. I won't write much more now, so that I could go for a little walk in the most beautiful Nuremberg weather. (When was I here with Eva? Sometime during the war, since on the \?{castle}{Burg} a youth said: "A spy!").

Mother affected me hard emotionally. First I was totally cold, accepting it \WTF{sensationally}{sensationell} and Machiavellianishly. Then, before falling asleep on Saturday evening, I thought honestly about her and regarded my feelinglessness to be a crime. A night full of pain, the trip, the Leipzig celebration, actually a celebration, fully distracted me. I discussed the grotesqueness with Kopke. \WTF{He said, the drunken conclusion was a telegram: "Pick up the corpse!"}{Er sagte, besoffener Schluß sei ein Telegramm: "Bestellen Sie die Leiche ab!"} Now I acted exhausted in Berlin, not because of the enjoyment, but rather, lying, because of the overnight trip. Then, as mother's coffin stood there where father's coffin stood, a few years came down; but I told myself -- because of exhausted nerves. Then new distraction and new pangs of conscience. She deserved better love from me.

At the station already at 6:45 on Sunday morning, although only departed an hour later. Still, only standing room, and always tightly squashed, so that I could hardly move my feet. But, a place to sit from Nuremberg on. The people on the train these days: old good-natured master craftsman, organized cabinet-maker in the middle between the majority socialists and independents; a Saxon jurist my age with an adorable youth and a lovely wife; Insurance-Reichsrat, pianist and Liszt-enthusiast, crippled by a shot to the hand; an independent worker, sworn to the world revolution and the soviet republic, a petite-bourgeois widow full of anxiety about her wealth, etc, politics permeates everything, everyone for peace and more or less convinced of Germany's guilt; more in tune with the socialists than conservatives, most are indifferent to foreign policy.

\textit{Waiting room, 7 o'clock in the evening}

The train is supposed to be delayed by 90 minutes. Hopefully Eva is not at the station...waiting room, beer and the last of the 5 cigarettes from Felix. --

From Nuremberg, the train on Saturday Thuringer was directed East to Hof because of strike. In the area of Marktredwitzer \WTF{wheezing and plodding}{Keuchen und Schleichen} again, two machines in front, two behind. It was 7:30 when we got to Leipzig. I decided to get out, went to a hotel at the station (a monopoly, I believe, a little room for 6M), there I was told that the rooms in Berlin were very expensive and that there was good fast train leaving at 5:45, I rang Scherner's and heard a crazy \WTF{Jubelhallo}{!!} through the apparatus. Went to Manna, which had now set its tables and raised its prices, but still the old nutritous broadbeans and spatzle and the old slow evening waitress, then I ran without a coat -- the raincoat was in the hotel! -- through thunderstorms to the C-station, where one now pays 25pf, and drove through the familiar city to Connewitz. Stormy reception at Scherner's, Buckels, Semmelrath, the little conservatory student and cafe actress, tge Vogels, the rather stiff married teacher couple. I had no suspicion about mama's birthday party, flowers, gifts, the just-finished supper hailing down. Jubilant receptipn, and when a while later Kopke appeared, he shook me on both shoulders so hard that my teeth smashes together. All these people that we brought together, now address eachother informally and are boisterously intimate with one another. They seem to think warmly  of us, and the Scherners in particular took me in with such love that I was completely comfortable and warm. \WTF{In no time Eva and me were in Scherner's "Du" zone}{im Nu hatte ich auch für Eva und mich das Schernersche Du sitzen}, and \WTF{"Hanschen" preferred to use Du with me}{Hans hätte mich am liebsten mit allen verduzt}. I had to drink a lot of fruit wine, also liqueur, also ate strawberries and smoked. We discussed my war diary, of which there was a machine copy at home, and about Harms, who was politically remote from these people (he is in Koesen), and about the necessity of signing (which at this instant is once again in question because of the rejection by all the moderates, while it was certain on Saturday), and Kopke advised me on journalism, said even Harms was against it, and praised my article, and we talked about the old Leipzig days and I expanded on my study on Romanticism, and we acted foolishly and were alsoa bit tipsy and drunk, drunk, and \WTF{was warm and heavy}{mir war warm und schwer} and I was so full of life and I said to Kopke that life was a tragicomedy, and that I was numb and the whole thing was \WTF{grotesque}{eine erlebte Groteske}, and he seconded that conclusion -- \WTF{but I know one better: cry and be ashamed of your tears, since they're not from the heart, rather merely tears of exhaustion and observed and analyzed with new ideas, in the direction of Kleist -- Fatherland -- Romanticism}{ich weiß aber einen besseren: weinen und sich seiner Thränen schämen, weil es nicht einmal besoffene sind, sondern bloß Übermüdungsthränen und beobachtete und analysierte mit Gedankenzusatz, Richtung Kleist -- Vaterland -- Romantik}

Meanwhile it was \WTF{already dawn}{zeitig dämmerig} and clear and on Scherner's balcony there was heavenly rain-fresh morning air and to the left \?{half-veiled}{in halber Verschleierung} was the nearby forest, and on June 29th 1904 I had also gone throug the earliest Summer morning, and in the following days wandered wandered and laid with Eva in nightly in the green forest...We became tired and drank coffee and ate many \?{sandwiches}{Wurstbrod}, and a food packet was prepared for me, and the lighter was filled with benzene, and Scherner lent me black gloves (for Stefl's tophat), and we jointly wrote to Eva ("Du!") and Kopke and Petersen wallowed with their "women on the side" on the Sofa, an Scherner sat them on his belly and bounced them. And finally we all went together through the characteristic pale morning back into the city, Scherner hanging on my arm, the two of us in a serious conversation. He wants to, in addition to his pharmacy job, take 6 semesters of philosophy and a dissertation between philosophy, Catholicism and literature. We also spoke about characters of mutual acquaintance. By the Rossplatz the other people took their leave, but the Scherners brought me to the door of the hotel. We are friends for life...

It was after 4 o'clock, I called the porter, paid, washed up a bit, got dressed (coat, new collar, better boots) and went to the station. Direct trip to Berlin. I probably slept a bit (my bed remained untouched) and, both before and afterwards, hardly got to Petrarka's lecture that I brought along, nor even to the newspapers that I always bought. In Berlin at 8:30 on Sunday, \?{going to Meyerhof's was out of the question}{an Meyerhofs war nicht zu denken}. At the counter I was told, that if I returnes the fo..owimg morning I would be in Munich just as early as if I had used the evening fast train leaving from Hof. But I was feeling restless and adventurous and bought a ticket for Hof anyway. I then got a shave (60pf!), and also had the barber tie my tie and took the underground train to Bay. Platz. Just as I had often to see mother during the war. Meet Marta year-stained and unrested, Julius portly, Walter fat, big, satisfied, very elegant, very modern \WTF{in litteris}{??} and very red in Politicis. Drank a mouthful of tea and had to go. As to mother's death, I gradually learned that she had been sick for just a week, only caught a light cold, almost dying on Sunday from pneumonia, and then survived with her old tenacity, so that she made plans on Tuesday and got heart pills instead of morphine, and went to sleep after eating on Wednesday...\?{Found Marta at the car terminal}{Marta fand an ein Auto Anschluß} (the family doesn't have their own any more), I went on the underground and tram with Jelski and Walter to Weissensee. At Alexenderplatz and later at the castle I saw battle scars similar to those I saw at the Justice Palace at Munich. (Now it is 8 o'clock, at 7 the peace must be signed or the ceasefire will run out. No one here knows. The last report ran: All officers would resign if the cabinet signed...Pur fleet in the English harbor sunk by a German crew!)...In Weissensee everything, really everything was exactly as at father's funeral. The family gathered gradually, Berthold's first word, as at father's death, was a mechanical "\WTF{Stay strong!}{Halt dich stramm!}", \?{with which he seems to give himself composure}{womit er sich selber Haltung zu geben scheint}. Friendly \?{hugs}{Berührung}. Everyone told me that I looked very bad, and I lied about the night-trip and \WTF{enjoyed the financial benefits of my bad looks}{freute mich der finanziellen Wirkung wegen des schlechten Aussehens}. Frank, Olga emaciated and sunken. Lotte Sussmann, grown and strong, Grete Goldschmidt-Rebenwurzel's husband, old and stately, didn't know my name at all, that I existed, was not without comic effect. My sister Grete - absent. Held up by sciatica in Saxony -- naturalmente.

Hedel is said to involved in theater and literature -- \WTF{???}{Violine gelangt sein}? Nobody loves her. No foreigners, the death announcement appeared later. A nice garland, a bigger one from the Reform congregation. At 12 o'clock the quick ceremony. \?{Professional pallbearers}{Gesculte Träger}, black coffin, simple, like father's. Hidden choir, before that few bars from the harmonium. "You are my refuge, my banner" which is sung every week in the community. But father's "God, you see" was lovelier still. None of the words were believed but yet the tears still came -- \WTF{after the wild night and since there was sobbing all around}{nach der durchbummelten Nacht und da ringsum geschluchzt wird}. As contagious as seasickness. The usual unctuous prayer (no sermon, \?{thank god}{G.s.D.}!) thoroughly dried them. "It is determined in god's plan", \WTF{military emblems on one dark man}{militärisches Zeichen des eines schwarzen Mannes}, the others militaristically shouldered the casket, outside he was put into a hearse. Terribke rainstorm, went further. First silence, then, behind at least, very quiet chatting. I asked Lotte about her abitur, about Hedel etc. At father's vault, an open place. 7 years later. Mother had been 76 years old, father only 72. The lowering, the tossing of handfulls of dirt on it, the banging shoveling, the pre-written Hebrew prayer, which no one understood. The trip home in two rented cars. I went with Georg and Sussmann. It is Georg's own car, now sold to his previous chauffeur, he told laughing what Huth earns, calculated the cost of the trip, etc etc. Then had to go to a patient and meanwhile talked with Otto on his \?{physics study}{Physikstudium}. Midday was elegant -- again one servant -- and very meager. Afterwards I poured my heart out about the finances and my future. Georf was very interested in my plans for political journalism and \WTF{encouraged then}{ihnen geneigt}. But I should still hold out for the university professor track. He gave me 300M for the trip, which only cost me 100M, and I will also make more in exchanging it. Berthold telephoned: at five o'clock tea and the testament, but to Felix's beforehand. --

(Munich 24/6) Very friendly reception there. Same financial situation on my part; Felix thought that I looked "undernourished", and I gladly let him have this opinion. I got guest-gifts: cigars, which have eased the trip for me, a leather case for them, cookies, a Summer jacket which Felix had inherited from his wife's father, who had handed over a jacket for me and which has now gone over unchanged to Eva's everyday use...At 5 to Berthold's, a difficult trip. First I was alone with him, neutral hugs; I had to wonder at his powerful youths, Aenny was impeccable and lively as ever. Marta and Wally came, boring tea, at which B's mother in law took part. After that, the inheritance discussion among us siblings. I took exception to the fact that my inheritance \WTF{is returned upon my death}{falle bei meinem Tode zurück}, it is awkward for me that mother had made a later (legally invalid) draft which treated Grete better; half from disgust, half entirely practically, 

to not have myself left out and to rather have Georg's lasting support, I put forward my complete rejection. Even Marta and Wally have different ideas, the whole consultatiob about immediate payout or further \?{investment}{Verwaltung uns Zinsverteilung} breaking down. Incidentally the whole thing, about which father spent so much work and touching concern, is a pittance. About 80,000M which the siblings and I are involved with, and from which some 30,000 consists in \WTF{Reich Bonds}{Reichsanleihen}. Berthold offered Marta and me each 1000M interest to start, the affluent Wally should and would renounce the interest. Fruitless interruptions. Father had intended Grete a sixth, mother a third. There are also rather contentious stipulations about Heinz Macholl in it...Mother left me a silver box. I had also refused it yesterday, since Marta and Walla quarrelled a bit about individual pieces of furniture. Then from Nuremberg on I left everything to Berthold. We took a break, was meanwhile taken out to an over-elegant and over-expensive supper by Anny, and Berthold tormented and sickened me in the old manner since I did not eat enough of it. Finally at 7 o'clock we went our four ways, the siblings said goodbye, I remained a little while more with B and his wife and poured my heart out about the whole hopelessness and \WTF{despair}{Verfehltheit} of my financial and occupational situation. Then I said goodbye and went to the station. The train, since it only went to Hof, was rather empty. I found a good seat went through the night in an unthinking, exhausted, half-sleeping haze. \?{I had plenty of bread from Scherner's}{Belegte Bros hatte ich reichlich von Scherners} and Anny, who also added a piece of chocolate. I hadn't seen chocolate at all for a long time, hadn't eaten any in years. I brought it with me to Eva, but greedily smokes the five expensive cigars which I got from Felix in the course of the day. \missing

(6/25) After two nights of travelling, I had above all to restore myself in Nuremberg, \WTF{also had a good overall memory of the layout lf the city}{hatte auch eine gute Gesammterinnerung an das Stadtbild}. So I sat for an hour in the Cafe Kusch, drank two genuine coffees, wrote to Berthold and then these notes. Finally I mailed the letter and only then, in the late afternoon, did I go out for a little walk. Up to the castle. One could not go inside: in the closed-off courtyard there was artillery pointed at the city, there were sandbags piled up against the entrance, and guards (politely) forbade entry. But above, in the green depth of the trench, civilians shot heavy crossbows at high-up targets, against \WTF{which}{dessen Leinewand} the thick bolts thudded and crashed harmlessly. Medieval and contemporary. \?{From the highest ramparts}{Unterhalb des obersten Nurgplateaus} I has a beautiful view of the city. High gables and pointed steeples and red bricks. Then a little over the bridges the hustle and bustle of the German Middle Ages \WTF{and Venice}{und Venedig} (the decorative windows, \?{everything pressed right up against the water}{das Dicht-ans-Wasser-Gedrängte}, the narrow gables, the tiled roofs). I stopped a minute at the stall of a nearby junkseller. Shoelaces, books, notes, slippers, boots. Overall, Nuremberg was thoroughly familiar to me -- in detail, I knew nothing, it would take years to study, e.g. at the portal of the Lorenz church. -- Now a little supper in a vegetarian restaurant, which are now so common in Germany, and then to the station before 7 o'clock. The train was to depart at 7:24, but a delay of 90 minutes was immediately announced. I set down with a beer and the last cigar in the waiting room and wrote in my journal. Unfortunately only until 8:30. Then as I got to the platform, they gave another 140 minutes, and so I had to wait until almost 10 o'clock. Countless people with me -- I quite feared the moment of the rush. But I squeezed myself in very well, of course in deadeningly stuffy air and close quarters. I slept sitting on my luggage; in Treuchtlingen I even got a place to sit and chatted with a student who wanted to go to Davos to pick up her sister. I took her for a teacher and spoke a few good words about the help that Davos always brings. Then when I heard that the lady had just taken the state medical exam, I was embarassed by my banalities...

Finally in Munich at 2, we got \?{street-pass papers}{Straßenpassoerschein}. I went through the empty city (Stachus, Ludwigstrasse) and was \?{stopped}{controlliert} twice, but very politely. Peculiarly it looked like two guards \?{stopped}{stellten und controlliert} an automobile. Polite hand-motions, but before straightening the weapons in their straps...At 3 o'clock I caught up with Eva. --

\missing


% clean sweep