\header{Friday afternoon 3 o'clock. 20 June}

At 6 I got the "urgent telephone connection" with Berlin that I had requested at 8 o'clock in the morning. Georg said briefly and cooly that mother had died pf pneumonia on Wednesday afternoon and will be buried on Sunday at 12 o'clock. -- "Then I will come." -- "Yes, come, that is nice." He seemed to not have expected that.

...Yesterday I picked Eva up at the Matthaeu church; \WTF{A flattened circle, naked and sober, with a square factory smokestack on it}{ein plattgedrückter Kreis, nackt und nüchtern, mit einem eckigen Fabrikschornstein darauf}. A passable organ. -- Afterwards ate with Eva in the garden of the "new exchange". There they now have very good coffee, admittedly 1.30 for a little cup -- but in Stephanie one can still only get piss. Hans M doesn't like to go there any more, because the barbed wire, barricades and guards in the neighborhood irritate him. --

Again today, from early in the morning, worries: dentist, bank, station. I now leave at 7:45 tomorrow morning -- "You would do welp to be at the station an hour beforehand". I got the travel papers out of pity, though the telegram was not "\?{certified}{beglaubigt}"; after that, a "\?{registration card}{Zulassungskarte}" was still needed, only then could I get a ticket. Anyhow, there is again a daily fast train. And I am to come back on Sunday night. Of course, will all of that work out? In Thuringia there is said to be a rail strike, and perhaps I shall run into trouble, since the Reich cabinet has resigned yesterday, and since the national assembly apparently cannot agree on the acceptance or rejection. Here in Munich a part of the troops are said to belong to the Independents...incidentally I am going to tomorrow's Epp-appeal. -- From \textit{Stefl}, who I met yesterday, I just got a top-hat, since mine is buried at Wetsch's (which I bought for father's funeral and probably wore only that one time). Stefl has a little room in a pension on Jaegerstrasse, which is overflowing (\?{up to the heating vents}{bis in die Ofenöffnungen}) with bibliophiliac for the most part very modern books (Dehmel, Daubler, Trakl). He \WTF{spends}{steckt...herein} his passion and money here, for all of his peacefulness and old-German learnedness, he is very far to the left \?{and at the forefront}{und vorn} in literis et politicis. While I was with him, Seebass arrived, who he is very friendly with. We ourselves, I found, have been \WTF{cut a little bit}{ein bißchen geschnitten} in recent times. He always makes an appointment to play the violin and never comes. -- He told me, most emphatically, that the Montesquieu contract is ready for me, and he also promises me a Petrarca volume for the fruit salad. Incidentally, Inselverlag and Mueller are said to have published lots of German specimens from the Petrarca letters. I am so distrustful: I always fear taking anything scientific from Stefl and Seebass too seriously, I also suspect a bit of anti-Semitism from Seebass.

I have told myself and Eva: perhaps on familial occasions I should remain completely silent about old insults to my sense of honor, and leave Eva herself out of the game. Calmly make my peace and only consider making her and my financial interests as well-off as possible. I am momentarily in greater distress: the 8000M will not suffice if I don't earn something extra. Perhaps I will be helped by my little inheritance, perhaps something will be left to me. All means are valid; it's all about carrying out my work to its goal and also not letting Eva stop halfway. If a peace with Berthold \?{helps that along}{weiterhilft}, so be it. Eva is entirely off to the side, now mother is dead, there is no longer any \?{bond}{Band} from her to my sisters. And I must carry out separate calculations: remember what I owe to myself, \?{smother}{herunterwürgen} what would inflict sickness on me and Eva, try to be as financially protected as possible. It is not pretty -- but it is probably the smartest thing to do.

Hans M says that Pontius gossips a lot about me, I was much too reactionary, and I was a total slave to my wife. Especially this second point sickens me. Semper idem. {...}

It is miserable: \?{out of the inheritance I made some acquisitions}{auf die Erbschaft hin mache ich Anschaffungen}; for 15M I bought the soft hat which Hans had lent me; I had my military boots worked on for 40M. Everything is so unspeakably expensive; food and side-expenses tie up unheard-of money.