\header{Monday adternoon 30/June 19 Munich.}

People were so crowded at the cinema ("The Hounds of Baskerville") that we couldn't get it. So we went to the very much empty \textit{Kammerspiele}. A wretched house on Augustenstrasse, and the theater itself a miserablel pathetic little cinema in it, narrow and not large, \WTF{all the way to the back over the floor in rows}{ganz hinten über dem Parkett im Rang}. Apparently had been a cinema before (with the usual side emergency exits to the street. Seats for 3M in the first balcony row. Much more expensive in the evening). They showed \textit{Mandragola}; I was very interested to become acquainted with the piece. But it left me cold. A lecture on literary history. That there no curtain came down, but instead an actor called "Action!" and then likewise the next act was announced from the \?{prompt box}{Souffleurkasten} (Aktus quartus, quintus!), that it came here from an auditorium, half wearing fool-costumes, that a curtain opened over a church facade in the background every time, and up there the intermission music was sung -- did not make the affair any warmer. \missing

After that to the new market for coffee. In the evening Frau zsobat sang her formal exercises, it was very boring for me. I envy Frau Sobat and Dr Ritter; \?{neither of them has a good voice}{sie haben beide keine Stimmen}, yet they go on in their art and are fulfilled and satisfied by it, especially Dr Ritter, who doesn't doubt himself at all. What luck. --

Spent this morning in the city. Dentist. --