\header{Monday morning 7 o'clock. 2/June 19.}

Still constant work on the university referat. But I want to complete it today and present it to Heilbronn and Reyersbach in the evening. Yesterday afternoon, coffee from 4 until (unfortunately) 7 at Hartmann's on Kaiserplatz, across from the Ursulaturm and Zifferblatt, while a thunderstorm (after the warm weather finally arrived) went on outside. Kind, modest, harmless old people. Coffee and cake. Two old ladies and a young, gigantic, fresh, unaffected girl, transplanted here from Friedenau and the Reinhardt school \WTF{with Hermine Körner at the theater}{mit der Hermine Körner ans Schauspielhaus}, debutante, who has been entrusted with big upcoming roles, Rose Berndt and Penthesilea. Her untheatrically-robust essence particularly pleases me. A Fraulien \textit{Molter}. -- In the evenimg we chatted at length with Dr Ritter, \WTF{the three of us made our own dumplings}{wir hatten uns zu dritt aus Eigenen Mehlklöße machen lassen} and considered his marriage options. We apparently rather liked Frau Gehmacher, but as a married person would not obtained his desired assistant doctor post, would would lead him to a hospital directorship (with the help of the Catholic nuns!). He also fears financial difficulties and is a calmy-reflective mature person...On Sunday evening we sat in on an entirely similar conversation with him and Stefl at the Stephanie. --

Yesterday evening again read aloud a long piece of \textit{L'\OE uvre}.

% untheatralisches robustes Wesen