\header{Tuesday morning 7 o'clock 8/April 19.}

Early yesterday the incredible proclamation of the socialist-communist Raterepublik. A break with Weimar, greetings to the Russian and Hungarian brothers -- "national day of celebration". I went to the university. Gates, one small entrance, a heap of people. I got in, saw a note by the \?{administrator}{Verwalter} a note: the university \?{stands behind the Zentralrat}{unterstehe dem Zeltralrat}; I authorize the Herren...signed \textit{Landauer}.

At home I spoke to some professors; no one knew what had happened. Then a notice outside: I close the university; the senate is dismissed; after the celebration a peoples' school will be opened. -- \textit{Strasser}. This Strasser is the same young man and Austrian lieutenant who recently wanted to talk to be about Spartakus instead of the young Goethe, behaves then in private juts as he does in class. A somewhat \?{older}{reifer} student, Terkel I believe, gave a very excited, imploring speech. "We are the \?{works committee}{Beteiebsrat} -- third revolution, revolutionary tribunal -- in an hour the machine guns could be here -- \?{we will pay with our heads for what happens}{wir haften mit unsern Köpfen, die fallen können} -- no unrest, go home..."

Just then at midday before the university I received a serious a

 really undeserved personal injury. I met "the Lerches", I have been extremely friendly to the tiny Rabinowitsch. I requested the people to come over to us; the Frau said very loudly, in the middle of the crowd: "I do not consort with converted Jews." I let it stand, I confronted Lerch later. He gave no explanation, rather \WTF{ran off with his second wife}{zog bekniffen mit seinem zweite Weibe ab}. How can one, and how can this person reproach me for what I do in private? What do I have to do with the ghetto? The day disturbed me and still disturbs me now.
 
 After eating in Stephanie, then to the Meyerhofs', who were alone with the tranquil Behle, went for a walk with them down the Ludwigstrase then again to Stephanie...\textit{A telegraph 
 om Harms, he asked to to telephone an article. How and from where?} In the city I saw a sharply anti-semitic and anti-soviet scene. (see the to-be-written article.) Hans advised immediatelt taking all money from the Deutschen Bank. At home, I read aloud the Voltaite book (to its end) and Zola.
 
...Towards evening notice at the university: lectures will be held from 2 o'clock Tuesday until Friday April 12th. I telephoned Vossler about it. "Then I am still not entirely fired." There is supposed to be a student assembly in the max. auditorium at 9. -- How do I attend that, write the article, and hold my still-not-ready lecture? And how and from where do I telephone?? I already spoke to Dr Ritter about it.
 % scurpulous