\header{Saturday morning 12 April 19}

The last two lectures cost me almost all of my work-time. Yesterday I finished with the 33rd; Bousset formed a good conclusion. The 12-15 people who were still present stomped me a little parting-ovation, a so-to-say curtain call...In the French upper-level course no one has shown up since Tuesday; there were still 4 pepple sitting in the last German course (Strasser's). I asked whether we should work or go. "Talk with us a bit." First we spoke of the school reform, Strasser, the Raterepublik, and everyone was very democratic; \?{then I had them tell me about themselves}{dann ließ ich mir Persönliches erzählen}. One is 39 years old, Auslanddeutscher, came from his post in India, in the 6th semester studied national economy and is now taking his Notabitur. Another, 20 years old, at 16 he entered the army on the second day of mobilaztion, and ended leading a company. --

Lerch came to see me at the university; he wanted to visit me here to talk. He reported that his sister-in-law (soon his second wife) had recently attacked me at Vossler's, \WTF{I would have done anything for material reasons}{Ich täte alles aus materiellen Gründen}; he had gone up against her. Incidentally, "converted Jew" was no insult, that must be discussed, I would have to teach Rabinovitch better. I gruffly rejected it. If a man abused me, I could slap him or spit in his face, against a woman I am defenseless, but she no longer exists for me. I would only give someone the honor of a debate who I deemed worthy; a vulgar person, a base fanatic, no...I was irritated, and he could not give up his sister-in-law for my sake. Certainly all evil comes from the fanatics, but also all good. He was so un-fanatical that he understood every standpoint. So then he now lovesthe second Rabinowitsch. I said: if I encountered him in the university or elsewhere or if he came to me, I would be friendly -- I ruled everything else out...He could not force his wife into anything! "If you let her insult your friends without demanding a retraction..." It is an affair that always turns my stomach. --

The situation here is ever-escalating and cannot last. There already seems to be great concern in the new government. \?{The more violent their actions}{Um so heftiger ihr Vorgehen}. Today: "disarming the bourgeoisie". A totally idealistic article by Landauer in the NN, who has completely taken over the Zentralrat. They speak lyrically of freedom, and become ever more tyrannical. Even Landauer flatters the Bavarian hate of Prussia.

% i can tell you