\header{Thursday morning before 7 o'clock. 10 April 19.}

On Tuesday aftenoon, the most-chaotic student assembly in the auditorium maximum. (Schmidt-Nörr) After eating, very badly prepared before my half-auditorium lecture. No one shows up any longer for the French course. In the evening, at Vossler's with Eva. Despite announcing our appearance to Lerch, he was there with his sister-in-law. We paid them no attention and that worked out very well. We left around 9:30 in order to catch the last tram. \?{I knew that after I left Frau Rabinowitsch would make her excuses}{Ich wußte, daß Frau Rabinowitsch hinter mir her ihre Erklärungen abgeben werde}. Already the next morning I had the opportunity to talk with Vossler. He said that she was completely fanatical, considered me a traitor to her people, had written a fanatical article in the Bavarian Kurier, according to which the Germans weren't antisemitic enough. We are supposed to go to Vossler's on Sunday evening, we won't see the Lerches then. Lerch's sister-in-law will likewise establish her helplessness. I also said that as regards science, he over-exalts himself, one Vosslerian idea occurs to him every six months, which he then carries through in a Toblerian manner. Vossler agrees with me; \?{after a while it adds up}{nach einer Weile setzte er dann hinzu}: But nevertheless he has a scientific character. Beforehand he said: "I need him -- I can't do it myself." --

This discussion took place yesterday ta 11 in the auditorium maximum. At 10 o'clock the caretaker brought an invitation to the assembly of the entire teaching staff taking place just afterwards, until the direction of the prorector Frau vom Muller, the medic who swore me in after 1915. Baumcker declared himself ill. It came to a declaration of solidarity. If the Zentralrat fired some lecturers, then none would remain. But no one resigned. Everyone just feels robbed. The assembly was interesting enough. Excited interruption by the old Brentano, who I had heard in the first semester of 1902, some words from Kesch, who looked like a character-actor playing Napolean, with close-cropped gray hair and a totally bald head, am agreement from Jaffe, the finance minister of the "old government", a fine delicate gray-haired little man. A national economist (among other titles), Sinzheimer, made himself repulsively notable and tiresome through chattering and quarreling, and obtained more opposition than one would have expected, but a very excited assembly to be capable of just that. At the end spokespeople for the student body appeared, among them Mahrholz. It was a boon to my vanity to sit before him on the professors' bench. (Among them, \textit{one} woman, a doctor.) A revolutionary student wanted to give an explanation for everything, \WTF{but his his words were chopped up}{aber ein zerhauener das Wort}, said that he spoke for all groups except for the radicals and explained: the student body goes with the professors through thick and thin! Stormy applause. Then he added: "We expect, however, that the proposed reforms in the senate will be taken up immediately." This was promised to him. -- The sitting finished at 1. No one can say whether he is still a lecturer. \WTF{But will read until morning}{Aber gelesen wird bis morgen}.

I have now extensively described all of this politica in an article for the LNN up to the here-mentioned details. Hopefully it is not lost again, like several were during the second revolution. I sat working until the evening and then brought it to the station. Then by foot through the city at 7. Automobiles threw out fliers for the Raterepublik. I have the impression that the ground is shaking sub pedibus. Again there was a flyer from Bamberg. A flyer from the Association of Jewish Citizens entreated moderately against the Jew-baiting. Early today, manifesto from the revolutionary tribunal. Monsterous. Discretionary punishment for any infringement of revolutionary principles. 6 party members (Independents and Communists \?{outnumbering}{Unabh. und Communisten, die Mehrheitssoc überwiegend} the Majority Socialists) decide without appeal. A lawyer had an advisory voice. It is time that Munich is recaptured. But today Braunschweig is is also declared as a Raterepublik. I am sometimes shaken in my beliefs. Hans M is smilinglynand unshakeably convinced in the durability and the "justice" of the new situation. --

A student came to me and laid down a scholarship exam; i.e. I had to test and confirm what he had learned in my course. He told me that he did not go to Vossler because one couldn't get the first note there. \?{He knew his information so well}{Er wßte aber so glänzend} that I couldn't give him anything other than the sought-after 0.5-note.

Incidentally, Vossler told me later that this \textit{Schneider} was known to him as particularly hard-working. -- \missing

%ataidtentionmumm beloved aunt