\header{Wednesday evening 7 o'clock. 2/April 19.}

Constant snow, half-melting; \?{my boots are unable to keep up}{mein Stiefelzeug ist dem nicht gewachsen}. I wanted to have a cobbler work on my brand-new too-large military boots -- he demanded 60M for it. The man lives in Hans M's house, who I took this opportunity to see again, and who prophesizes the Räterepublik in the next weks, and from which the atrocities of the \textit{"Noske-guards"} in Berlin were fulfilled.

Wednesday is my day without any lectures; I used it as a chance for the Voltaire book. Only leafed through some chapters, carefully read others. I hope to be able to write on Sunday. I become tired so agonizingly easily with \WTF{earnest}{ernster} lectures.

I was again deeply depressed today by a visit from \textit{Vossler} last night. The constant dialogue between Vossler and Lerch on linguistic things, conjunctives, etymologies -- Lerch uses the library and Vossler's experiences. And I sit there just as dumb and unimportant as Frau Vossler and a young son. If I say something about literary history, then I am immediately cut down by Vossler and Lerch: they stand pondering from pure aesthetical heights...on Monday Vossler spoke of Lafontaine's "Humor", on Tuesday afternoon I \?{attacked}{bestritten} this humor in my lecture -- there are only \WTF{Rococo games}{Rokokospielerei}. I asserted just the same thing yesterday evening. But most of the time, I was silent. Lerch said of Vossler and himself: "We linguists" -- "WTF{You must despise it, since you indeed did not ascribe fundamental value to the form of the poetry}{Sie müssen das verachten, weil Sie ja nicht der Form der Dichtung Hauptwert beilegen}." -- I said to Vossler: \?{I am on the market and am old and know that not much is throught of my ideas}{Ich stehe am Markt und bin alt und weiß, man schätzt nicht, was ich gebe}. It is unphilological. And yet Vossler only half-comforted me: certainly, only on old texts; anyhow... I am on the market and remain dependent. Today Georg gave me another 2000M -- \?{it seems a lot to him}{ihm scheint es viel}, but it wouldn't be enough for me without additional income. And it is so bitter to take it. He is pressing for a reconciliation with Berthold, he didn't find the insult inflicted on me so bad. -- \missing



% d